### 2014-04-14 documentation/spa.tex
Update documentation

% Created 2014-04-14 Mon 14:38
\documentclass[runningheads,a4paper]{llncs}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{makeidx}
\usepackage{epstopdf}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{times}
\usepackage{listings}
\institute{University of Groningen \and Kings College London \and Brown University}
\hypersetup{plainpages=false}
\newcommand{\highlight}[1]{\colorbox{yellow}{#1}}
\usepackage{natbib}
\input{revision}
\author{Kuiper, J \inst{1}. \and Marshall, I.J. \inst{2} \and Wallace, B.C. \inst{3} \and Swertz, M.A. \inst{1}}
\date{\today}
\title{Spá: a web-based viewer for text mining in Evidence Based Medicine}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.4.50.1 (Org mode 8.2.5h)}}
\begin{document}

\maketitle
\begin{abstract}
When doing sentence extraction or document level predictions on unstructured text the results of trained models are often hard to interpret within their context.
Furthermore presenting results to end users can be a considerable user interface challenge.
This problem is especially prevalent in Evidence Based Medicine, where most of the research findings are only published as unstructured PDF documents.
To this end we present \textbf{Spá}\cite{kuiper2014} \footnote{freely available under GPLv3 at \url{https://github.com/joelkuiper/spa}}, a generic web-based visualizer for sentence and document level classifiers on PDFs.
Spá allows the results of sentence extractions to be visualized within the PDF document itself, and allows other results to be presented alongside it.
\\
\\
\texttt{revision: \revision, date: \revisiondate}
\end{abstract}

\section{Introduction}
\label{sec-1}
\begin{figure}[htb]
\centering
\includegraphics[width=.9\linewidth]{./screenshot.png}
\caption{Screenshot of Spá}
\end{figure}

Finding sentences or words with particular characteristics within a larger document is an important task in natural language processing and machine learning.
For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match a certain ontology to impose structure.

Dealing with unstructured text is of particular importance in research areas where most findings are only published in that form.
In evidence based medicine, for example, the results of clinical trials, which assess the safety and efficacy of treatments, are often only published as PDF documents.

Furthermore to arrive at informed decisions about a specific clinical question, many clinical trials need to be pooled and summarized.
The process of pooling and summarizing clinical trials is called \emph{systematic reviewing}, and forms the corner-stone of current evidence based medical practice.
Systematic reviewing consists of specifying an inclusion criteria (i.e., the criteria studies must satisfy to be included in the review), searching the literature, screening the retrieved citations to identify eligible studies and, finally, summarizing the relevant evidence.
But achieving this aim is complicated by the massive numbers of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials as having been conducted in the last decade \cite{valkenhoef2012}.
While publishing standards are improving and novel tools for systematic reviewing are being created to address this problem, a lot of legacy publications still only exist as PDF documents.
This raises questions about the sustainability of systematic reviews in its current form.

Thus to aid the process of systematic reviewing we created a generic web-based tool that allows the visualization of annotations within a PDF documents, or meta-information alongside it.
The aim is to have a pluggable system to allow for semi-automated (machine assisted) screening, data extraction and data summarization.
\section{Architecture}
\label{sec-2}

\begin{figure}[htb]
\centering
\includegraphics[width=.9\linewidth]{sequence_diagram.eps}
\caption{\label{fig:sequence}Sequence diagram of a typical request-response}
\end{figure}

Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js/}} for visualization of the document and text extraction.
The results of the text extraction are processed server-side by a variety of (pluggable) pipelines, as outlined in figure \ref{fig:sequence}.
Results from these pipelines, which could be complicated machine learning systems, are communicated back to the browser and displayed.
For each of the annotations the relevant nodes in the document are highlighted and a minimap, inspired by \href{http://substance.io/}{substance.io}, is projected to show where it resides within the document.
The user can then interactively activate and inspect the specific type of results.
\highlight{TODO?}
\section{Case Study}
\label{sec-3}
As a case study we evaluate the automatic assessment of Risk of Bias in clinical trial publications.
\highlight{TODO}
\section{Conclusion \& Future work}
\label{sec-4}
We present a web-based tool for interactive visualization of annotations and metadata on PDF documents.
This allows users to see the results from machine learning systems within the context of a specific document.
Moreover, we present a case study for Evidence Based Medicine by automatically extracting potential Risks of Bias, with supporting sentences.

However, we believe the tool to be useful for a much wider range of text mining and machine learning applications.
To increase the generality of the tool work is being done to support a consumer/producer pattern for the pipelines, allowing developers to quickly plug-in new systems.

\bibliographystyle{splncs}
\bibliography{references}
% Emacs 24.4.50.1 (Org mode 8.2.5h)
\end{document}

### 2014-04-14 documentation/spa.tex
Minor documentation changes

@@
-% Created 2014-04-14 Mon 14:38
+% Created 2014-04-14 Mon 15:43
 \documentclass[runningheads,a4paper]{llncs}
@@
 \tolerance=1000
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage[protrusion=true,expansion=true]{microtype}
 \usepackage{makeidx}
 \usepackage{epstopdf}
-\usepackage[usenames,dvipsnames]{xcolor}
-\usepackage[protrusion=true,expansion=true]{microtype}
 \usepackage{times}
@@
 \hypersetup{plainpages=false}
+\setcounter{tocdepth}{3}
 \newcommand{\highlight}[1]{\colorbox{yellow}{#1}}
-\usepackage{natbib}
 \input{revision}
-\author{Kuiper, J \inst{1}. \and Marshall, I.J. \inst{2} \and Wallace, B.C. \inst{3} \and Swertz, M.A. \inst{1}}
+\author{Kuiper, J\inst{1}. \and Marshall, I.J.\inst{2} \and Wallace, B.C.\inst{3} \and Swertz, M.A.\inst{1}}
 \date{\today}
@@
 Furthermore presenting results to end users can be a considerable user interface challenge.
-This problem is especially prevalent in Evidence Based Medicine, where most of the research findings are only published as unstructured PDF documents.
-To this end we present \textbf{Spá}\cite{kuiper2014} \footnote{freely available under GPLv3 at \url{https://github.com/joelkuiper/spa}}, a generic web-based visualizer for sentence and document level classifiers on PDFs.
+These challenges are of key interest in research areas where most findings are only published as unstructured PDF documents, such as evidence based medicine.
+To this end we present \textbf{Spá} \footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa}} \cite{kuiper2014}, a generic web-based visualizer for sentence and document level classifiers on PDFs.
 Spá allows the results of sentence extractions to be visualized within the PDF document itself, and allows other results to be presented alongside it.
@@
 Finding sentences or words with particular characteristics within a larger document is an important task in natural language processing and machine learning.
-For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match a certain ontology to impose structure.
+For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match a certain ontology to impose a certain structure.
 
@@
 But achieving this aim is complicated by the massive numbers of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials as having been conducted in the last decade \cite{valkenhoef2012}.
-While publishing standards are improving and novel tools for systematic reviewing are being created to address this problem, a lot of legacy publications still only exist as PDF documents.
+While publishing standards are improving and novel tools for systematic reviewing are being created to address this problem \highlight{citation needed}, a lot of legacy publications still only exist as PDF documents.
 This raises questions about the sustainability of systematic reviews in its current form.
 
-Thus to aid the process of systematic reviewing we created a generic web-based tool that allows the visualization of annotations within a PDF documents, or meta-information alongside it.
+To aid the process of systematic reviewing we made a generic web-based tool that allows the visualization of annotations within a PDF documents, or meta-information alongside it.
 The aim is to have a pluggable system to allow for semi-automated (machine assisted) screening, data extraction and data summarization.
@@
 
-Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js/}} for visualization of the document and text extraction.
+Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
 The results of the text extraction are processed server-side by a variety of (pluggable) pipelines, as outlined in figure \ref{fig:sequence}.
 Results from these pipelines, which could be complicated machine learning systems, are communicated back to the browser and displayed.
-For each of the annotations the relevant nodes in the document are highlighted and a minimap, inspired by \href{http://substance.io/}{substance.io}, is projected to show where it resides within the document.
+For each of the annotations the relevant nodes in the document are highlighted and a custom scrollbar, inspired by \href{http://substance.io/}{substance.io}, that acts as a mini-map is projected to show where it resides within the document.
 The user can then interactively activate and inspect the specific type of results.
-\highlight{TODO?}
+\highlight{todo?}
 \section{Case Study}
@@
 As a case study we evaluate the automatic assessment of Risk of Bias in clinical trial publications.
-\highlight{TODO}
+\highlight{todo}
 \section{Conclusion \& Future work}
@@
 However, we believe the tool to be useful for a much wider range of text mining and machine learning applications.
-To increase the generality of the tool work is being done to support a consumer/producer pattern for the pipelines, allowing developers to quickly plug-in new systems.
+To increase the generality of the tool work is being done to support a consumer/producer protocol for the pipelines, allowing developers to quickly plug in new systems.
+Furthermore, work is being done on allowing users to save selected annotations for sharing and off-line, possibly embedded within the document itself.
 

### 2014-04-14 documentation/spa.tex
Add header to documentation

@@
-% Created 2014-04-14 Mon 15:43
+% Created 2014-04-14 Mon 17:44
 \documentclass[runningheads,a4paper]{llncs}
@@
 \usepackage{listings}
-\institute{University of Groningen \and Kings College London \and Brown University}
+\urldef{\mailsa}\path|{joel.kuiper, m.a.swertz}@rug.nl|
+\urldef{\mailsb}\path|iain.marshall@kcl.ac.uk|
+\urldef{\mailsc}\path|byron_wallace@brown.edu|
+\institute{University of Groningen P.O. Box 30001, 9700 RB Groningen \\ \mailsa \and King's College London, London SE1 3QD, UK \\ \mailsb \and Brown University, Providence, RI 02906, USA \\ \mailsc}
 \hypersetup{plainpages=false}
@@
 \date{\today}
-\title{Spá: a web-based viewer for text mining in Evidence Based Medicine}
+\title{Spá: a web-based viewer for text mining in evidence based medicine}
 \hypersetup{
@@
 These challenges are of key interest in research areas where most findings are only published as unstructured PDF documents, such as evidence based medicine.
-To this end we present \textbf{Spá} \footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa}} \cite{kuiper2014}, a generic web-based visualizer for sentence and document level classifiers on PDFs.
+To this end we present Spá\footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa}} \cite{kuiper2014}, a generic web-based visualizer for sentence and document level classifiers on PDFs.
 Spá allows the results of sentence extractions to be visualized within the PDF document itself, and allows other results to be presented alongside it.
@@
 Finding sentences or words with particular characteristics within a larger document is an important task in natural language processing and machine learning.
-For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match a certain ontology to impose a certain structure.
+For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match an ontology to impose a certain structure.
 
@@
 While publishing standards are improving and novel tools for systematic reviewing are being created to address this problem \highlight{citation needed}, a lot of legacy publications still only exist as PDF documents.
-This raises questions about the sustainability of systematic reviews in its current form.
+This raises the questions about the sustainability of systematic reviews in its current form.
 
-To aid the process of systematic reviewing we made a generic web-based tool that allows the visualization of annotations within a PDF documents, or meta-information alongside it.
+To aid the process of systematic reviewing we made a generic web-based tool that allows the visualization of annotations within the document, and meta-information alongside it.
 The aim is to have a pluggable system to allow for semi-automated (machine assisted) screening, data extraction and data summarization.
@@
 Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
-The results of the text extraction are processed server-side by a variety of (pluggable) pipelines, as outlined in figure \ref{fig:sequence}.
-Results from these pipelines, which could be complicated machine learning systems, are communicated back to the browser and displayed.
+The results of the text extraction are processed by the Python server-side by a variety of (pluggable) pipelines, as outlined in figure \ref{fig:sequence}.
+Results from these pipelines, which could be complicated machine learning systems, are communicated back to the browser and displayed using React components \footnote{\url{http://facebook.github.io/react/}}.
 For each of the annotations the relevant nodes in the document are highlighted and a custom scrollbar, inspired by \href{http://substance.io/}{substance.io}, that acts as a mini-map is projected to show where it resides within the document.
-The user can then interactively activate and inspect the specific type of results.
-\highlight{todo?}
+The user can interactively activate and inspect specific results.
 \section{Case Study}
 \label{sec-3}
-As a case study we evaluate the automatic assessment of Risk of Bias in clinical trial publications.
+As a case study we implemented automatic assessment of Risk of Bias in clinical trial publications.
 \highlight{todo}
@@
 To increase the generality of the tool work is being done to support a consumer/producer protocol for the pipelines, allowing developers to quickly plug in new systems.
-Furthermore, work is being done on allowing users to save selected annotations for sharing and off-line, possibly embedded within the document itself.
+Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
 

### 2014-04-14 documentation/paper.tex
Switch org to TeX

--- 2014-04-14 documentation/spa.tex
@@
-% Created 2014-04-14 Mon 17:44
+% Created 2014-04-14 Mon 18:10
 \documentclass[runningheads,a4paper]{llncs}
@@
 \usepackage{rotating}
-\usepackage[normalem]{ulem}
 \usepackage{amsmath}
@@
 \usepackage[usenames,dvipsnames]{xcolor}
-\usepackage[protrusion=true,expansion=true]{microtype}
 \usepackage{makeidx}
 \usepackage{epstopdf}
-\usepackage{times}
 \usepackage{listings}
+
 \urldef{\mailsa}\path|{joel.kuiper, m.a.swertz}@rug.nl|
@@
 \institute{University of Groningen P.O. Box 30001, 9700 RB Groningen \\ \mailsa \and King's College London, London SE1 3QD, UK \\ \mailsb \and Brown University, Providence, RI 02906, USA \\ \mailsc}
-\hypersetup{plainpages=false}
+
 \setcounter{tocdepth}{3}
 \newcommand{\highlight}[1]{\colorbox{yellow}{#1}}
+
 \input{revision}
@@
 \title{Spá: a web-based viewer for text mining in evidence based medicine}
-\hypersetup{
-  pdfkeywords={},
-  pdfsubject={},
-  pdfcreator={Emacs 24.4.50.1 (Org mode 8.2.5h)}}
+
 \begin{document}
@@
 \centering
-\includegraphics[width=.9\linewidth]{./screenshot.png}
+\includegraphics[width=.9\linewidth]{./images/screenshot.png}
 \caption{Screenshot of Spá}
@@
 \label{sec-2}
-
 \begin{figure}[htb]
 \centering
-\includegraphics[width=.9\linewidth]{sequence_diagram.eps}
+\includegraphics[width=.9\linewidth]{./diagrams//sequence.eps}
 \caption{\label{fig:sequence}Sequence diagram of a typical request-response}
@@
 
+\subsubsection{Acknowledgments}
+\label{sec-4-0-1}
+Part of this research was funded from the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement n° 261433 (Biobank Standardisation and Harmonisation for Research Excellence in the European Union - BioSHaRE-EU)
+
 \bibliographystyle{splncs}
 \bibliography{references}
-% Emacs 24.4.50.1 (Org mode 8.2.5h)
+
 \end{document}

### 2014-04-14 documentation/spa.tex
Add incantation
a pass on the paper

--- 2014-04-14 documentation/spa.tex
@@
 \date{\today}
-\title{Spá: a web-based viewer for text mining in Evidence Based Medicine}
+%\title{Sp{\' a}: a web-based viewer for text mining in Evidence Based Medicine}
+\title{Sp{\' a}: Extracting and Displaying Attributes of Interest \\ for Evidence Based Medicine}
 \hypersetup{
@@
 \begin{abstract}
-When doing sentence extraction or document level predictions on unstructured text the results of trained models are often hard to interpret within their context.
-Furthermore presenting results to end users can be a considerable user interface challenge.
-These challenges are of key interest in research areas where most findings are only published as unstructured PDF documents, such as evidence based medicine.
-To this end we present \textbf{Spá} \footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa}} \cite{kuiper2014}, a generic web-based visualizer for sentence and document level classifiers on PDFs.
-Spá allows the results of sentence extractions to be visualized within the PDF document itself, and allows other results to be presented alongside it.
-\\
-\\
+
+%Evidence-based medicine requires 
+In an ideal world, scientific findings would be stored in structured databases so as to be easily accessible.
+In practice, however, unstructured PDF documents remain the main vehicle for dissemination of scientific findings.
+Those interested in gathering and assimilating data must therefore manually peruse published articles and extract from these the elements of interest.
+Evidence based medicine (EBM) provides a compelling illustration of this challenge: many expensive person-hours are spent each year extracting summary information from articles that describe clinical trials.
+Supervised machine learning provides a potential means of mitigating this burden by automating extraction.
+But for automated approaches to be useful to end-users, we need tools that allow domain experts to interact with, and benefit from, model predictions.
+To this end, we present an open-source tool called {Sp\'a}\footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa}} that accepts as input an article describing a clinical trial and provides as output an automatically visually annotated rendering of this article.
+Specifically, we focus on automating \emph{risk of bias} assessments and extracting the clinical trial sample size.
+This tool is thus of immediate use to those who practice evidence based medicine.
+However, more generally, {Sp\'a} provides a framework for visualizing predictions (both at the document and sentence level) for full-text PDFs.
+
+%When doing sentence extraction or document level predictions on unstructured text the results of trained models are often hard to interpret within their context.
+%Furthermore presenting results to end users can be a considerable user interface challenge.
+%These challenges are of key interest in research areas where most findings are only published as unstructured PDF documents, such as evidence based medicine.
+
+%To this end we present \textbf{Spá} \footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa}} \cite{kuiper2014}, a generic web-based visualizer for sentence and document level classifiers on PDFs.
+%Spá allows the results of sentence extractions to be visualized within the PDF document itself, and allows other results to be presented alongside it.
+
 \texttt{revision: \revision, date: \revisiondate}
@@
 \section{Introduction}
-\label{sec-1}
+\label{section:intro}
+
+Identifying and extracting specific elements of interest from the full-texts of published articles is an important practical step for many tasks.
+Consider evidence based medicine (EBM) \cite{sackett1996}, in which the aim is to address a specific clinical question by identifying and synthesizing data from all published relevant articles.
+Thus when undertaking such exercises, one needs, e.g., to extract from the article describing a clinical trial the number of participants that were enrolled (the sample size).
+Another component of EBM is assessing the \emph{risk of bias} for a particular study across different domains.
+For example, one often wants to assess the risk of bias due to improper blinding of participants and personnel.
+For this task, one wants both to make a summary judgement (e.g., low risk of bias) while simulteanously extracting the sentence(s) supporting this assessment.
+%In any case, such decisions may affect one's interpretation of the body of evidence pertaining to a particular question.
+
+%Finding sentences or words with particular characteristics within a larger document is an important task in natural language processing and machine learning.
+For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match a certain ontology to impose a certain structure.
+
+Extracting such information from the free text of articles describing clinical trials is a laborious process.
+Machine learning methods provide the machinery to automate such extractions: these can effectively impose the structure of interest onto PDF's.
+But if such technologies are to be practically useful, we need tools to visualize the predicted annotations.
+Here we describe {Sp\'a} which aspires to realize this aim.
+{Sp\'a} is an open-source, web-based tool that incorporates state-of-the-art machine learning predictors to automatically annotate PDF articles describing clinical trials with risk-of-bias predictions and extracted sample sizes.
+This tool is useful for practitioners of evidence based medicine and other biomedical researchers.
+
 \begin{figure}[htb]
@@
 \includegraphics[width=.9\linewidth]{./screenshot.png}
-\caption{Screenshot of Spá}
+\caption{Screenshot of Sp{\'a}}
 \end{figure}
 
-Finding sentences or words with particular characteristics within a larger document is an important task in natural language processing and machine learning.
-For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match a certain ontology to impose a certain structure.
+While our application of interest is evidence based medicine, we emphasize that the framework can incorporate other types of articles (and the appropriate trained machine learning models).
+Thus the contribution of this work is two-fold, as we present: (1) a practical tool that incorporates cutting edge machine learning to help biomedical researchers rapidly assess published articles describing clinicals, and, (2) a general open-source web framework for visualizing the predictions of trained models from (PDF's of) full-text articles.
+These contributions are described further in Sections \ref{section:EBM-ML} and \ref{section:SPA}, respectively.
 
-Dealing with unstructured text is of particular importance in research areas where most findings are only published in that form.
-In evidence based medicine, for example, the results of clinical trials, which assess the safety and efficacy of treatments, are often only published as PDF documents.
+\section{Automating Evidence-Based Medicine}
+\label{section:EBM-ML}
 
-Furthermore to arrive at informed decisions about a specific clinical question, many clinical trials need to be pooled and summarized.
+%Dealing with unstructured text is of particular importance in research areas where most findings are only published in that form.
+%In evidence based medicine, for example, the results of clinical trials, which assess the safety and efficacy of treatments, are often only published as PDF documents.
+
+%Furthermore to arrive at informed decisions about a specific clinical question, many clinical trials need to be pooled and summarized.
+
+\subsection{Systematic Reviews}
 The process of pooling and summarizing clinical trials is called \emph{systematic reviewing}, and forms the corner-stone of current evidence based medical practice.
 Systematic reviewing consists of specifying an inclusion criteria (i.e., the criteria studies must satisfy to be included in the review), searching the literature, screening the retrieved citations to identify eligible studies and, finally, summarizing the relevant evidence.
-But achieving this aim is complicated by the massive numbers of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials as having been conducted in the last decade \cite{valkenhoef2012}.
-While publishing standards are improving and novel tools for systematic reviewing are being created to address this problem \highlight{citation needed}, a lot of legacy publications still only exist as PDF documents.
-This raises questions about the sustainability of systematic reviews in its current form.
+%But achieving this aim is complicated by the massive numbers of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials as having been conducted in the last decade \cite{valkenhoef2012}.
+%While publishing standards are improving and novel tools for systematic reviewing are being created to address this problem \highlight{citation needed}, a lot of legacy publications still only exist as PDF documents.
+%This raises questions about the sustainability of systematic reviews in its current form.
 
 To aid the process of systematic reviewing we made a generic web-based tool that allows the visualization of annotations within a PDF documents, or meta-information alongside it.
+
 The aim is to have a pluggable system to allow for semi-automated (machine assisted) screening, data extraction and data summarization.
-\section{Architecture}
-\label{sec-2}
+
+\subsection{Machine Learning Strategies}
+
+\begin{itemize}
+\item Basically show that we're using state of the art
+\item Briefly talk about cochrane DB / distant supervision
+\item KDD stuff (briefly)
+\item Multi-task stuff!
+\end{itemize}
+
+\section{Sp{\'a} Architecture}
+\label{section:architecture}
 
@@
 
-Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
+Sp{\'a} relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
 The results of the text extraction are processed server-side by a variety of (pluggable) pipelines, as outlined in figure \ref{fig:sequence}.

### 2014-04-14 documentation/paper.tex
Merging

@@
 \usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{makeidx}
 \usepackage{epstopdf}
@@
 
+\begin{document}
 \setcounter{tocdepth}{3}
@@
 \date{\today}
-\title{Spá: a web-based viewer for text mining in evidence based medicine}
-
-\begin{document}
+\title{Spá: a web-based viewer for text mining in Evidence Based Medicine}
 
@@
 \begin{abstract}
-When doing sentence extraction or document level predictions on unstructured text the results of trained models are often hard to interpret within their context.
-Furthermore presenting results to end users can be a considerable user interface challenge.
-These challenges are of key interest in research areas where most findings are only published as unstructured PDF documents, such as evidence based medicine.
-To this end we present Spá\footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa}} \cite{kuiper2014}, a generic web-based visualizer for sentence and document level classifiers on PDFs.
-Spá allows the results of sentence extractions to be visualized within the PDF document itself, and allows other results to be presented alongside it.
+Unstructured PDF documents remain the main vehicle for dissemination of scientific findings.
+Those interested in gathering and assimilating data must therefore manually peruse published articles and extract from these the elements of interest.
+Evidence based medicine provides a compelling illustration of this challenge: many person-hours are spent each year extracting summary information from articles that describe clinical trials.
+Machine learning provides a potential means of mitigating this burden by automating extraction.
+But, for automated approaches to be useful to end-users, we need tools that allow domain experts to interact with, and benefit from, model predictions.
+To this end, we present an open-source tool called Spá\footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}} that accepts as input an article describing a clinical trial and provides as output an automatically visually annotated rendering of this article.
+More generally, Spá provides a framework for visualizing predictions, both at the document and sentence level, for full-text PDFs.
 \\
@@
 \section{Introduction}
-\label{sec-1}
+\label{section:intro}
+Identifying and extracting specific elements of interest from the full-texts of published articles is an important practical step for many tasks.
+Consider evidence based medicine (EBM) \cite{sackett1996}, in which the aim is to address a specific clinical question by identifying and synthesizing data from all published relevant articles.
+Thus when undertaking such exercises, one needs, e.g., to extract from the article describing a clinical trial the number of participants that were enrolled (the sample size).
+Another component of EBM is assessing the \emph{risk of bias} for a particular study across different domains.
+For example, one often wants to assess the risk of bias due to improper blinding of participants and personnel.
+For this task, one wants both to make a summary judgement (e.g., low risk of bias) while simulteanously extracting the sentences supporting this assessment.
+
+%Finding sentences or words with particular characteristics within a larger document is an important task in natural language processing and machine learning.
+For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match a certain ontology to impose a certain structure.
+
+Extracting such information from the free text of articles describing clinical trials is a laborious process.
+Machine learning methods provide the machinery to automate such extractions: these can effectively impose the structure of interest onto PDF's.
+But if such technologies are to be practically useful, we need tools to visualize the predicted annotations.
+Here we describe Spá which aspires to realize this aim.
+Spá is an open-source, web-based tool that incorporates state-of-the-art machine learning predictors to automatically annotate PDF articles describing clinical trials with risk-of-bias predictions and extracted sample sizes.
+This tool is useful for practitioners of evidence based medicine and other biomedical researchers.
+
 \begin{figure}[htb]
@@
 \includegraphics[width=.9\linewidth]{./images/screenshot.png}
-\caption{Screenshot of Spá}
 \end{figure}
 
-Finding sentences or words with particular characteristics within a larger document is an important task in natural language processing and machine learning.
-For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match an ontology to impose a certain structure.
+While our application of interest is evidence based medicine, we emphasize that the framework can incorporate other types of articles (and the appropriate trained machine learning models).
+Thus the contribution of this work is two-fold, as we present: (1) a practical tool that incorporates cutting edge machine learning to help biomedical researchers rapidly assess published articles describing clinicals, and, (2) a general open-source web framework for visualizing the predictions of trained models from full-text articles.
+These contributions are described further in Sections \ref{section:EBM-ML} and \ref{section:architecture}, respectively.
 
-Dealing with unstructured text is of particular importance in research areas where most findings are only published in that form.
-In evidence based medicine, for example, the results of clinical trials, which assess the safety and efficacy of treatments, are often only published as PDF documents.
+\section{Automating Evidence-Based Medicine}
+\label{section:EBM-ML}
 
-Furthermore to arrive at informed decisions about a specific clinical question, many clinical trials need to be pooled and summarized.
+\subsection{Systematic Reviews}
 The process of pooling and summarizing clinical trials is called \emph{systematic reviewing}, and forms the corner-stone of current evidence based medical practice.
-Systematic reviewing consists of specifying an inclusion criteria (i.e., the criteria studies must satisfy to be included in the review), searching the literature, screening the retrieved citations to identify eligible studies and, finally, summarizing the relevant evidence.
+Systematic reviewing consists of specifying an inclusion criteria, searching the literature, screening the retrieved citations to identify eligible studies and, finally, summarizing the relevant evidence.
 But achieving this aim is complicated by the massive numbers of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials as having been conducted in the last decade \cite{valkenhoef2012}.
-While publishing standards are improving and novel tools for systematic reviewing are being created to address this problem \highlight{citation needed}, a lot of legacy publications still only exist as PDF documents.
-This raises the questions about the sustainability of systematic reviews in its current form.
+While publishing standards are improving and novel tools for systematic reviewing are being created to address this problem \highlight{citation needed}, a lot of legacy publications will remain only as PDF documents.
+This raises questions about the sustainability of systematic reviews in its current form.
 
-To aid the process of systematic reviewing we made a generic web-based tool that allows the visualization of annotations within the document, and meta-information alongside it.
+To aid the process of systematic reviewing we made a generic web-based tool that allows the visualization of annotations within a PDF documents, or meta-information alongside it.
 The aim is to have a pluggable system to allow for semi-automated (machine assisted) screening, data extraction and data summarization.
-\section{Architecture}
-\label{sec-2}
+
+\subsection{Machine Learning Strategies}
+
+\begin{itemize}
+\item Basically show that we're using state of the art
+\item Briefly talk about cochrane DB / distant supervision
+\item KDD stuff (briefly)
+\item Multi-task stuff!
+\end{itemize}
+
+\section{Architecture overview}
+\label{section:architecture}
 \begin{figure}[htb]
@@
 \end{figure}
-
 Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
@@
 Results from these pipelines, which could be complicated machine learning systems, are communicated back to the browser and displayed using React components \footnote{\url{http://facebook.github.io/react/}}.
-For each of the annotations the relevant nodes in the document are highlighted and a custom scrollbar, inspired by \href{http://substance.io/}{substance.io}, that acts as a mini-map is projected to show where it resides within the document.
-The user can interactively activate and inspect specific results.
-\section{Case Study}
-\label{sec-3}
-As a case study we implemented automatic assessment of Risk of Bias in clinical trial publications.
-\highlight{todo}
+
 \section{Conclusion \& Future work}
-\label{sec-4}
 We present a web-based tool for interactive visualization of annotations and metadata on PDF documents.
@@
 \subsubsection{Acknowledgments}
-\label{sec-4-0-1}
 Part of this research was funded from the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement n° 261433 (Biobank Standardisation and Harmonisation for Research Excellence in the European Union - BioSHaRE-EU)

### 2014-04-15 documentation/paper.tex
Minor changes
Do not depend on epstopdf
Clean-up Makefile
Minor documentation changes

@@
 \usepackage{graphicx}
-\usepackage{longtable}
 \usepackage{float}
 \usepackage{wrapfig}
-\usepackage{rotating}
 \usepackage{amsmath}
@@
 \usepackage{hyperref}
+\usepackage{microtype}
+\usepackage{acronym}
 \tolerance=1000
 \usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{epstopdf}
 \usepackage{listings}
@@
 \urldef{\mailsc}\path|byron_wallace@brown.edu|
-\institute{University of Groningen P.O. Box 30001, 9700 RB Groningen \\ \mailsa \and King's College London, London SE1 3QD, UK \\ \mailsb \and Brown University, Providence, RI 02906, USA \\ \mailsc}
+
+\acrodef{ebm}[EBM]{Evidence-based Medicine}
+
+\institute{
+  University of Groningen P.O. Box 30001, 9700 RB Groningen \\ \mailsa
+  \and King's College London, London SE1 3QD, UK \\ \mailsb
+  \and Brown University, Providence, RI 02906, USA \\ \mailsc}
 
@@
 Those interested in gathering and assimilating data must therefore manually peruse published articles and extract from these the elements of interest.
-Evidence based medicine provides a compelling illustration of this challenge: many person-hours are spent each year extracting summary information from articles that describe clinical trials.
+\acl{ebm} provides a compelling illustration of this: many person-hours are spent each year extracting summary information from articles that describe clinical trials.
 Machine learning provides a potential means of mitigating this burden by automating extraction.
 But, for automated approaches to be useful to end-users, we need tools that allow domain experts to interact with, and benefit from, model predictions.
-To this end, we present an open-source tool called Spá\footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}} that accepts as input an article describing a clinical trial and provides as output an automatically visually annotated rendering of this article.
+To this end, we present an web-based tool called Spá\footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}} that accepts as input an article and provides as output an automatically visually annotated rendering of this article.
 More generally, Spá provides a framework for visualizing predictions, both at the document and sentence level, for full-text PDFs.
@@
 
+\acresetall
+
 \section{Introduction}
 \label{section:intro}
-Identifying and extracting specific elements of interest from the full-texts of published articles is an important practical step for many tasks.
-Consider evidence based medicine (EBM) \cite{sackett1996}, in which the aim is to address a specific clinical question by identifying and synthesizing data from all published relevant articles.
-Thus when undertaking such exercises, one needs, e.g., to extract from the article describing a clinical trial the number of participants that were enrolled (the sample size).
-Another component of EBM is assessing the \emph{risk of bias} for a particular study across different domains.
-For example, one often wants to assess the risk of bias due to improper blinding of participants and personnel.
-For this task, one wants both to make a summary judgement (e.g., low risk of bias) while simulteanously extracting the sentences supporting this assessment.
+Finding sentences or words with particular characteristics within a document is an important task in natural language processing and machine learning.
 
-%Finding sentences or words with particular characteristics within a larger document is an important task in natural language processing and machine learning.
-For example, one may wish to identify the most important sentences in a document to automatically generate a summary, or match a certain ontology to impose a certain structure.
+Consider \ac{ebm} \cite{sackett1996}, which addresses clinical questions by identifying and synthesizing data from all relevant published articles.
+When doing this one needs, for example, to assess the \emph{risk of bias} for a particular study across different domains, like bias due to improper blinding of participants and personnel.
+For this task, one wants to make a summary judgement (e.g., low risk of bias) and simultaneously extract the sentences supporting that judgement.
 
-Extracting such information from the free text of articles describing clinical trials is a laborious process.
-Machine learning methods provide the machinery to automate such extractions: these can effectively impose the structure of interest onto PDF's.
-But if such technologies are to be practically useful, we need tools to visualize the predicted annotations.
+Extracting such information from the unstructured text of clinical trial articles is a laborious process.
+Machine learning methods provide the machinery to automate such extractions; as they can effectively impose structures onto PDF's.
+But if such technologies are to be practically useful, we need tools to visualize the predictions.
 Here we describe Spá which aspires to realize this aim.
-Spá is an open-source, web-based tool that incorporates state-of-the-art machine learning predictors to automatically annotate PDF articles describing clinical trials with risk-of-bias predictions and extracted sample sizes.
-This tool is useful for practitioners of evidence based medicine and other biomedical researchers.
+Spá is an open-source, web-based tool that can incorporate state-of-the-art machine learning predictors to automatically annotate PDF articles.
+Furthermore we have created machine learning systems on describing clinical trials with risk of bias predictions and extracted sample sizes.
+This tool is useful for practitioners of \ac{ebm} and other biomedical researchers.
 
@@
 \includegraphics[width=.9\linewidth]{./images/screenshot.png}
+\caption{\label{fig:screensot}Screenshot of a PDF with highlighted risk of bias}
 \end{figure}
 
-While our application of interest is evidence based medicine, we emphasize that the framework can incorporate other types of articles (and the appropriate trained machine learning models).
-Thus the contribution of this work is two-fold, as we present: (1) a practical tool that incorporates cutting edge machine learning to help biomedical researchers rapidly assess published articles describing clinicals, and, (2) a general open-source web framework for visualizing the predictions of trained models from full-text articles.
-These contributions are described further in Sections \ref{section:EBM-ML} and \ref{section:architecture}, respectively.
+While our application of interest is \ac{ebm}, we emphasize that the tool can be used in any domain.
+Thus the contribution of this work is two-fold, as we present:
+(1) a practical tool that incorporates machine learning to help researchers rapidly assess published medical articles, and,
+(2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
+These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}, respectively.
 
-\section{Automating Evidence-Based Medicine}
+\section{Automating \acl{ebm}}
 \label{section:EBM-ML}
@@
 \subsection{Systematic Reviews}
-The process of pooling and summarizing clinical trials is called \emph{systematic reviewing}, and forms the corner-stone of current evidence based medical practice.
+The process of pooling and summarizing clinical trials is called \emph{systematic reviewing}, and forms the corner-stone of current \ac{ebm}.
 Systematic reviewing consists of specifying an inclusion criteria, searching the literature, screening the retrieved citations to identify eligible studies and, finally, summarizing the relevant evidence.
 But achieving this aim is complicated by the massive numbers of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials as having been conducted in the last decade \cite{valkenhoef2012}.
-While publishing standards are improving and novel tools for systematic reviewing are being created to address this problem \highlight{citation needed}, a lot of legacy publications will remain only as PDF documents.
-This raises questions about the sustainability of systematic reviews in its current form.
+While methods and publishing standards are improving, a lot of legacy publications will remain only as PDF documents.
 
-To aid the process of systematic reviewing we made a generic web-based tool that allows the visualization of annotations within a PDF documents, or meta-information alongside it.
-The aim is to have a pluggable system to allow for semi-automated (machine assisted) screening, data extraction and data summarization.
+To aid the process of systematic reviewing we made a web-based tool that allows the visualization of annotations within a PDF documents, and meta-information alongside it.
+The vision is to have a system to allow for semi-automated (machine assisted) screening, data extraction and data summarization.
 
@@
 \centering
-\includegraphics[width=.9\linewidth]{./diagrams//sequence.eps}
+\includegraphics[width=.9\linewidth]{./diagrams/sequence.pdf}
 \caption{\label{fig:sequence}Sequence diagram of a typical request-response}
@@
 Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
-The results of the text extraction are processed by the Python server-side by a variety of (pluggable) pipelines, as outlined in figure \ref{fig:sequence}.
-Results from these pipelines, which could be complicated machine learning systems, are communicated back to the browser and displayed using React components \footnote{\url{http://facebook.github.io/react/}}.
+The results of the text extraction are processed server-side by a variety of pipelines, as outlined in figure \ref{fig:sequence}.
+Results from these pipelines, which could be complicated machine learning systems, are communicated back to the browser and displayed using React components\footnote{\url{http://facebook.github.io/react}}.
+
+For each of the annotations the relevant nodes in the document are highlighted and a custom scrollbar, inspired by \href{http://substance.io/}{substance.io}, that acts as a mini-map is projected to show where it resides within the document.
+The user can interactively activate and inspect specific results.
 
 \section{Conclusion \& Future work}
-We present a web-based tool for interactive visualization of annotations and metadata on PDF documents.
+We present a web-based tool for interactive visualization of annotations and meta-data on PDF documents.
 This allows users to see the results from machine learning systems within the context of a specific document.
-Moreover, we present a case study for Evidence Based Medicine by automatically extracting potential Risks of Bias, with supporting sentences.
+Moreover, we present a case study for \ac{ebm} by automatically extracting potential Risks of Bias, with supporting sentences.
 
@@
 \subsubsection{Acknowledgments}
-Part of this research was funded from the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement n° 261433 (Biobank Standardisation and Harmonisation for Research Excellence in the European Union - BioSHaRE-EU)
+Part of this research was funded by the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement n° 261433
 

### 2014-04-15 documentation/paper.tex
s/pipelines/topologies/

@@
 Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
-The results of the text extraction are processed server-side by a variety of pipelines, as outlined in figure \ref{fig:sequence}.
-Results from these pipelines, which could be complicated machine learning systems, are communicated back to the browser and displayed using React components\footnote{\url{http://facebook.github.io/react}}.
+The results of the text extraction are processed server-side by a variety of processing topologies, as outlined in figure \ref{fig:sequence}.
+Results, which could come from complicated machine learning systems, are communicated back to the browser and displayed using React components\footnote{\url{http://facebook.github.io/react}}.
 
@@
 However, we believe the tool to be useful for a much wider range of text mining and machine learning applications.
-To increase the generality of the tool work is being done to support a consumer/producer protocol for the pipelines, allowing developers to quickly plug in new systems.
+To increase the generality of the tool work is being done to support a pluggable system for processing topologies, allowing developers to quickly plug in new systems.
 Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.

### 2014-04-15 documentation/paper.tex
Documentation fixes

@@
 To aid the process of systematic reviewing we made a web-based tool that allows the visualization of annotations within a PDF documents, and meta-information alongside it.
-The vision is to have a system to allow for semi-automated (machine assisted) screening, data extraction and data summarization.
 
 \subsection{Machine Learning Strategies}
+When doing risk of bias assessment one wishes to \highlight{todo}
 
-\begin{itemize}
-\item Basically show that we're using state of the art
-\item Briefly talk about cochrane DB / distant supervision
-\item KDD stuff (briefly)
-\item Multi-task stuff!
-\end{itemize}
+% \begin{itemize}
+% \item Basically show that we're using state of the art
+% \item Briefly talk about cochrane DB / distant supervision
+% \item KDD stuff (briefly)
+% \item Multi-task stuff!
+% \end{itemize}
 
@@
 Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
+The ultimate vision is to have a extensible system for semi-automated (machine assisted) screening, data extraction and data summarization.
 

### 2014-04-16 documentation/paper.tex
Add link to substance.io beta

@@
 \usepackage[T1]{fontenc}
+\usepackage[protrusion=true,expansion=true]{microtype}
 \usepackage{fixltx2e}
@@
 \author{Kuiper, J\inst{1}. \and Marshall, I.J.\inst{2} \and Wallace, B.C.\inst{3} \and Swertz, M.A.\inst{1}}
-\date{\today}
+\date{\texttt{revision: \revision, date: \revisiondate}}
 \title{Spá: a web-based viewer for text mining in Evidence Based Medicine}
@@
 More generally, Spá provides a framework for visualizing predictions, both at the document and sentence level, for full-text PDFs.
-\\
-\\
-\texttt{revision: \revision, date: \revisiondate}
 \end{abstract}
@@
 
-For each of the annotations the relevant nodes in the document are highlighted and a custom scrollbar, inspired by \href{http://substance.io/}{substance.io}, that acts as a mini-map is projected to show where it resides within the document.
+For each of the annotations the relevant nodes in the document are highlighted and a custom scrollbar, inspired by \href{http://substance.io/}{substance.io}\footnote{\url{http://substance.io/beta/}}, that acts as a mini-map is projected to show where it resides within the document.
 The user can interactively activate and inspect specific results.

### 2014-04-16 static/scripts/helpers/text_layer_builder.js
Stick with 0.8.1 of pdf.js for now
See https://github.com/mozilla/pdf.js/issues/4631

@@ -30,14 +30,6 @@ var TextLayerBuilder = function textLayerBuilder(options) {
   this.layoutDone = false;
   this.divContentDone = false;
 
-  if(typeof PDFFindController === 'undefined') {
-      window.PDFFindController = null;
-  }
-
-  if(typeof this.lastScrollSource === 'undefined') {
-      this.lastScrollSource = null;
-  }
-
   this.beginLayout = function textLayerBuilderBeginLayout() {
     this.textDivs = [];
     this.renderingDone = false;
@@ -57,12 +49,7 @@ var TextLayerBuilder = function textLayerBuilder(options) {
   this.renderLayer = function textLayerBuilderRenderLayer() {
     var textDivs = this.textDivs;
     var canvas = document.createElement('canvas');
-    var ctx = canvas.getContext('2d');
-
-    // No point in rendering so many divs as it'd make the browser unusable
-    // even after the divs are rendered
-    var MAX_TEXT_DIVS_TO_RENDER = 100000;
-    if (textDivs.length > MAX_TEXT_DIVS_TO_RENDER) return;
+    var ctx = canvas.getContext('2d', {alpha: false});
 
     for (var i = 0, ii = textDivs.length; i < ii; i++) {
       var textDiv = textDivs[i];
@@ -72,15 +59,15 @@ var TextLayerBuilder = function textLayerBuilder(options) {
       if (width <= 0) {
         textDiv.isWhitespace = true;
         continue;
+      } else {
+        var textScale = textDiv.canvasWidth / width;
+        var rotation = textDiv.angle;
+        var transform = 'scale(' + textScale + ', 1)';
+        transform = 'rotate(' + rotation + 'deg) ' + transform;
+
+        CustomStyle.setProp('transform', textDiv, transform);
+        CustomStyle.setProp('transformOrigin', textDiv, "0% 0%");
       }
-
-      var textScale = textDiv.canvasWidth / width;
-      var rotation = textDiv.angle;
-      var transform = 'scale(' + textScale + ', 1)';
-      transform = 'rotate(' + rotation + 'deg) ' + transform;
-
-      CustomStyle.setProp('transform', textDiv, transform);
-      CustomStyle.setProp('transformOrigin', textDiv, "0% 0%");
     }
 
     this.renderingDone = true;
@@ -117,8 +104,9 @@ var TextLayerBuilder = function textLayerBuilder(options) {
   this.insertDivContent = function textLayerUpdateTextContent() {
[…]

### 2014-04-16 static/scripts/models/appState.js

@@ -2,7 +2,6 @@
 define(['backbone', 'PDFJS'], function(Backbone, PDFJS) {
   'use strict';
   PDFJS.workerSrc = 'static/scripts/vendor/pdfjs/pdf.worker.js';
-  PDFJS.disableWebGL = false;
 
   var AppState = Backbone.Model.extend({
     initialize: function() {

### 2014-04-16 pipeline.py
Use markdown for the results blocks
Gives the flexibility back to the pipelines

@@ -92,7 +92,10 @@ class SampleSizePipeline(Pipeline):
             matched_span = []
 
 
-        ss_row = {"name": "Sample Size"}
+        ss_row = {
+            "name": "Sample Size",
+            "document": "**Predicted sample size:** %s" % (predicted)
+        }
         ss_row["annotations"] = [{"span": matched_span,  "sentence": predicted, "label": 1}]
 
         return [ss_row]
@@ -173,7 +176,8 @@ class RiskOfBiasPipeline(Pipeline):
 
             # change the -1s to 0s for now (TODO: improve on this)
             # done because the viewer has three classes, and we're only predicting two here
-            domain_row["document"] = 1 if doc_model.predict(X_doc)[0] == 1 else 0
+            document_prediction = "positive" if doc_model.predict(X_doc)[0] == 1 else "unknown"
+            domain_row["document"] = "**Overall risk of bias prediction**: %s <br> **Supporting sentences**: %s" % (document_prediction, len(domain_row["annotations"]) or "*none*")
 
             output.append(domain_row)
 

### 2014-04-16 static/scripts/main.js

@@ -12,6 +12,7 @@ require.config({
     'underscore': 'vendor/underscore',
     'Q': 'vendor/q',
     'react': 'vendor/react',
+    'marked': 'vendor/marked',
     'JSXTransformer': 'vendor/JSXTransformer',
     'backbone': 'vendor/backbone',
     'PDFJS': 'vendor/pdfjs/pdf'

### 2014-04-16 static/scripts/main.js
Actually debounce minimap update
*sheesh*

@@ -74,7 +74,7 @@ define(function (require) {
 
   appState.on("update:minimap", _.debounce(function(e, obj) {
     minimap.forceUpdate();
-  }), 450);
+  }, 50));
 
 
 

### 2014-04-16 static/scripts/main.js
Style tweaks

@@ -74,7 +74,7 @@ define(function (require) {
 
   appState.on("update:minimap", _.debounce(function(e, obj) {
     minimap.forceUpdate();
-  }, 50));
+  }, 50, true));
 
 
 

### 2014-04-16 abstract_pipeline.py
Move to pdf.js 1.0.x
See https://github.com/mozilla/pdf.js/pull/4633

@@ -57,7 +57,7 @@ class Pipeline(object):
 
         for idx, page in enumerate(pages):
             if page is not None:
-                textNodes = [node["str"].encode("utf8") for node in page]
+                textNodes = [node["str"].encode("utf8") for node in page["items"]]
 
                 total = 0
                 ranges = []

### 2014-04-16 pipeline.py

@@ -177,7 +177,8 @@ class RiskOfBiasPipeline(Pipeline):
             # change the -1s to 0s for now (TODO: improve on this)
             # done because the viewer has three classes, and we're only predicting two here
             document_prediction = "positive" if doc_model.predict(X_doc)[0] == 1 else "unknown"
-            domain_row["document"] = "**Overall risk of bias prediction**: %s <br> **Supporting sentences**: %s" % (document_prediction, len(domain_row["annotations"]) or "*none*")
+            template_text = "**Overall risk of bias prediction**: %s <br> **Supporting sentences**: %s"
+            domain_row["document"] = template_text % (document_prediction, len(domain_row["annotations"]) or "*none*")
 
             output.append(domain_row)
 

### 2014-04-16 static/scripts/helpers/text_layer_builder.js

@@ -29,16 +29,10 @@
 var TextLayerBuilder = function textLayerBuilder(options) {
   this.layoutDone = false;
   this.divContentDone = false;
+  this.textDivs = [];
 
-  this.beginLayout = function textLayerBuilderBeginLayout() {
-    this.textDivs = [];
-    this.renderingDone = false;
-  };
-
-  this.endLayout = function textLayerBuilderEndLayout() {
-    this.layoutDone = true;
-    this.insertDivContent();
-  };
+  this.viewport = options.viewport;
+  this.pageIdx = options.pageIndex;
 
   this.setupRenderLayoutTimer = function textLayerSetupRenderLayoutTimer() {
     // Rendering is done in React, so we don't care here.
@@ -53,6 +47,9 @@ var TextLayerBuilder = function textLayerBuilder(options) {
 
     for (var i = 0, ii = textDivs.length; i < ii; i++) {
       var textDiv = textDivs[i];
+      if ('isWhitespace' in textDiv) {
+        continue;
+      }
 
       ctx.font = textDiv.style.fontSize + ' ' + textDiv.style.fontFamily;
       var width = ctx.measureText(textDiv.textContent).width;
@@ -77,66 +74,56 @@ var TextLayerBuilder = function textLayerBuilder(options) {
     return this.textDivs;
   };
 
-  this.appendText = function textLayerBuilderAppendText(geom) {
-    // vScale and hScale already contain the scaling to pixel units
-    var fontHeight = geom.fontSize * Math.abs(geom.vScale);
-    var fontAscent = geom.ascent ? geom.ascent * fontHeight :
-          geom.descent ? (1 + geom.descent) * fontHeight : fontHeight;
+  this.appendText = function textLayerBuilderAppendText(geom, styles) {
+    var style = styles[geom.fontName];
 
-    var style = {
-      fontSize: fontHeight + "px",
-      fontFamily: geom.fontFamily,
-      left:  (geom.x + (fontAscent * Math.sin(geom.angle))) + 'px',
-      top:  (geom.y - (fontAscent * Math.cos(geom.angle))) + 'px'
-    };
-
-    var textElement = {
-      canvasWidth:  geom.canvasWidth * Math.abs(geom.hScale),
-      fontName: geom.fontName,
-      angle:  geom.angle * (180 / Math.PI),
-      style: style
-    };
-
-    // The content of the div is set in the `setTextContent` function.
-    this.textDivs.push(textElement);
-  };
-
[…]

### 2014-04-16 static/scripts/models/appState.js

@@ -2,6 +2,9 @@
 define(['backbone', 'PDFJS'], function(Backbone, PDFJS) {
   'use strict';
   PDFJS.workerSrc = 'static/scripts/vendor/pdfjs/pdf.worker.js';
+  PDFJS.cMapUrl = 'static/scripts/vendor/pdfjs/cmaps/';
+  PDFJS.cMapPacked = true;
+  PDFJS.disableWebGL = false;
 
   var AppState = Backbone.Model.extend({
     initialize: function() {

### 2014-04-16 static/scripts/main.js
Slower debounce for minimap

@@ -74,7 +74,7 @@ define(function (require) {
 
   appState.on("update:minimap", _.debounce(function(e, obj) {
     minimap.forceUpdate();
-  }, 50, true));
+  }, 100));
 
 
 

### 2014-04-16 static/scripts/main.js
Slower debounce for minimap

@@ -74,7 +74,7 @@ define(function (require) {
 
   appState.on("update:minimap", _.debounce(function(e, obj) {
     minimap.forceUpdate();
-  }, 50, true));
+  }, 100, true));
 
 
 

### 2014-04-17 static/scripts/helpers/text_layer_builder.js
[WIP] clean-up text layer rendering

@@ -27,59 +27,13 @@
  * text that is being searched for.
  */
 var TextLayerBuilder = function textLayerBuilder(options) {
-  this.layoutDone = false;
-  this.divContentDone = false;
-  this.textDivs = [];
-
   this.viewport = options.viewport;
-  this.pageIdx = options.pageIndex;
 
-  this.setupRenderLayoutTimer = function textLayerSetupRenderLayoutTimer() {
-    // Rendering is done in React, so we don't care here.
-    // Original implementation delayed painting if the user was scrolling
-    this.renderLayer();
-  };
-
-  this.renderLayer = function textLayerBuilderRenderLayer() {
-    var textDivs = this.textDivs;
-    var canvas = document.createElement('canvas');
-    var ctx = canvas.getContext('2d', {alpha: false});
-
-    for (var i = 0, ii = textDivs.length; i < ii; i++) {
-      var textDiv = textDivs[i];
-      if ('isWhitespace' in textDiv) {
-        continue;
-      }
-
-      ctx.font = textDiv.style.fontSize + ' ' + textDiv.style.fontFamily;
-      var width = ctx.measureText(textDiv.textContent).width;
-      if (width <= 0) {
-        textDiv.isWhitespace = true;
-        continue;
-      } else {
-        var textScale = textDiv.canvasWidth / width;
-        var rotation = textDiv.angle;
-        var transform = 'scale(' + textScale + ', 1)';
-        transform = 'rotate(' + rotation + 'deg) ' + transform;
-
-        CustomStyle.setProp('transform', textDiv, transform);
-        CustomStyle.setProp('transformOrigin', textDiv, "0% 0%");
-      }
-    }
-
-    this.renderingDone = true;
-  };
-
-  this.getRenderedElements = function() {
-    return this.textDivs;
-  };
-
-  this.appendText = function textLayerBuilderAppendText(geom, styles) {
+  this.createElement = function(geom, styles) {
     var style = styles[geom.fontName];
 
     if (!/\S/.test(geom.str)) {
-      this.textDivs.push({isWhitespace: true});
-      return;
+      return {isWhitespace: true};
     }
 
     var tx = PDFJS.Util.transform(this.viewport.transform, geom.transform);
@@ -111,33 +65,36 @@ var TextLayerBuilder = function textLayerBuilder(options) {
       textElement.canvasWidth = geom.width * this.viewport.scale;
     }
 
-    this.textDivs.push(textElement);
+    return textElement;
   };
 
[…]

### 2014-04-17 static/scripts/main.js

@@ -53,6 +53,7 @@ define(function (require) {
 
   appState.on("change:pdf", function(e, pdf) {
     viewer.setProps({pdf: pdf});
+    resultsState.reset();
   });
 
   var Results = require("jsx!components/results");
@@ -74,7 +75,7 @@ define(function (require) {
 
   appState.on("update:minimap", _.debounce(function(e, obj) {
     minimap.forceUpdate();
-  }, 100));
+  }, 150, true));
 
 
 

### 2014-04-22 pipeline.py
s/positive/low for RoB predictions

@@ -176,7 +176,7 @@ class RiskOfBiasPipeline(Pipeline):
 
             # change the -1s to 0s for now (TODO: improve on this)
             # done because the viewer has three classes, and we're only predicting two here
-            document_prediction = "positive" if doc_model.predict(X_doc)[0] == 1 else "unknown"
+            document_prediction = "low" if doc_model.predict(X_doc)[0] == 1 else "unknown"
             template_text = "**Overall risk of bias prediction**: %s <br> **Supporting sentences**: %s"
             domain_row["document"] = template_text % (document_prediction, len(domain_row["annotations"]) or "*none*")
 

### 2014-04-22 documentation/paper.tex
updates to ECML paper

@@
 \usepackage{textcomp}
+\usepackage{wrapfig}
 \usepackage{marvosym}
@@
 \acl{ebm} provides a compelling illustration of this: many person-hours are spent each year extracting summary information from articles that describe clinical trials.
+This represents an enormous burden, especially in light of the expotentially increasing volume of published biomedical articles.
 Machine learning provides a potential means of mitigating this burden by automating extraction.
-But, for automated approaches to be useful to end-users, we need tools that allow domain experts to interact with, and benefit from, model predictions.
-To this end, we present an web-based tool called Spá\footnote{available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}} that accepts as input an article and provides as output an automatically visually annotated rendering of this article.
-More generally, Spá provides a framework for visualizing predictions, both at the document and sentence level, for full-text PDFs.
+But for automated approaches to be useful to end-users, we need tools that allow domain experts to interact with, and benefit from, model predictions.
+To this end, we present a web-based tool called Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}} that accepts as input an article and provides as output an automatically visually annotated rendering of this article.
+More generally, Spá provides a framework for visualizing predicted full-text PDF annotations, both at the document and sentence level.
 \end{abstract}
@@
 \label{section:intro}
-Finding sentences or words with particular characteristics within a document is an important task in natural language processing and machine learning.
 
-Consider \ac{ebm} \cite{sackett1996}, which addresses clinical questions by identifying and synthesizing data from all relevant published articles.
-When doing this one needs, for example, to assess the \emph{risk of bias} for a particular study across different domains, like bias due to improper blinding of participants and personnel.
+%Finding sentences or words with particular characteristics within a document is an important task in natural language processing and machine learning.
+Imposing structure on full-text documents (e.g., identifying specific sentences of interest) is an important, challenging and practical task in natural language processing and machine learning.
+Consider \emph{systematic reviews} -- fundamental tools in \ac{ebm} \cite{sackett1996} -- which aim to address specific clinical questions by identifying and synthesizing data from all relevant published articles.
+When doing this one often needs, for example, to assess the \emph{risk of bias} for a particular study across different domains, such as bias due to improper blinding of participants and personnel.
 For this task, one wants to make a summary judgement (e.g., low risk of bias) and simultaneously extract the sentences supporting that judgement.
@@
 Extracting such information from the unstructured text of clinical trial articles is a laborious process.
-Machine learning methods provide the machinery to automate such extractions; as they can effectively impose structures onto PDF's.
-But if such technologies are to be practically useful, we need tools to visualize the predictions.
-Here we describe Spá which aspires to realize this aim.
+Machine learning methods provide the machinery to automate such extractions; as they can effectively impose the desired structure onto PDFs.
+For example, we can train a classifier to automatically assess the risk of bias across different domains and simulteanously identify the sentences supporting these assessments.
+We may also train a model that extracts the sample size from a paper describing a clinical trial. 
+But if such technologies are to be practically useful, we need tools that visualize these model predictions and annotations.
+Here we describe Spá, which aspires to realize this aim.
 Spá is an open-source, web-based tool that can incorporate state-of-the-art machine learning predictors to automatically annotate PDF articles.
-Furthermore we have created machine learning systems on describing clinical trials with risk of bias predictions and extracted sample sizes.
-This tool is useful for practitioners of \ac{ebm} and other biomedical researchers.
+As a practical (and useful) demonstration of this technology, we have built a machine learning system that automatically annotates PDFs to facilitate \ac{ebm}. 
+Specifically, this system leverages a multi-task model that simulteanously assesses the risk of biases across several domains, and extracts sample sizes from articles.
+%Moreover, we have created machine learning systems on describing clinical trials with risk of bias predictions and extracted sample sizes.
+This tool is unique in that it leverages state-of-the-art ML models applied to full-text articles to assist practitioners of \ac{ebm} (and other biomedical researchers).
 
@@
 \centering
-\includegraphics[width=.9\linewidth]{./images/screenshot.png}
-\caption{\label{fig:screensot}Screenshot of a PDF with highlighted risk of bias}
+\includegraphics[width=.8\linewidth]{./images/screenshot2.png}
+\vspace{-1em}
+\caption{\label{fig:screenshot}Screenshot of a PDF with highlighted risk of bias.
+Here the risk of bias is assess to be low, for example, and one of the supporting sentences for this assessment describes the randomization procedure (highlighted in green).}
+\vspace{-2em}
 \end{figure}
 
-While our application of interest is \ac{ebm}, we emphasize that the tool can be used in any domain.
+While our application of interest is \ac{ebm}, we emphasize that the visualization tool can be used for any domain in which one wants to annotate PDFs. 
 Thus the contribution of this work is two-fold, as we present:
-(1) a practical tool that incorporates machine learning to help researchers rapidly assess published medical articles, and,
+(1) a practical tool (Spá) that incorporates cutting edge machine learning to help researchers rapidly assess the risk of biases (and sample sizes) in published biomedical articles, and,
 (2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
@@
 \subsection{Systematic Reviews}
+%%% sort of redundant with above; may want to re-factor
 The process of pooling and summarizing clinical trials is called \emph{systematic reviewing}, and forms the corner-stone of current \ac{ebm}.
-Systematic reviewing consists of specifying an inclusion criteria, searching the literature, screening the retrieved citations to identify eligible studies and, finally, summarizing the relevant evidence.
-But achieving this aim is complicated by the massive numbers of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials as having been conducted in the last decade \cite{valkenhoef2012}.
-While methods and publishing standards are improving, a lot of legacy publications will remain only as PDF documents.
+Systematic reviewing consists of specifying a precise clinical question and accompanying study inclusion criteria, and then exhaustively searching the literature to identify eligible studies. 
+Identified eligible studies are subsequently analyzed (i.e., synthesized), resulting in a summary of all of the published evidence that pertains to the clinical question of interest.
+Systematic reviews thus represent a rigorous, data-driven approach to answering clinical questions. 
+But conducting systematic reviews is complicated by the massive number of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials that were conducted in the last decade \cite{valkenhoef2012}.
+While methods and publishing standards are improving, many legacy publications will remain available only as PDF documents.
 
-To aid the process of systematic reviewing we made a web-based tool that allows the visualization of annotations within a PDF documents, and meta-information alongside it.
+Extracting information of interest from these PDFs is imperative but laborious. 
+To mitigate this burden, we have constructed machine learning models that automatically extract some characteristics of interest.
+Specifically, our model predicts {\it risk of biases} across different domains as a function of the texts comprising articles. 
+It simultaneously extracts sentences supporting these predictions. 
+We briefly outline our approach to achieving this below. 
+We also note that we have a a separate model that extracts the study sample size from articles. 
+Spá -- our visualization tool -- provides a framework to upload PDFs and then render these predicted annotations. 
+We foresee adding additional predictors to this tool that, for example, may identify different treatment mentions within the text (e.g., drugs).
 
-\subsection{Machine Learning Strategies}
-When doing risk of bias assessment one wishes to \highlight{todo}
+% made a web-based tool that allows the visualization of annotations within a PDF documents, and meta-information alongside it.
+
+\subsection{Machine Learning Approaches}
+
+We briefly describe our model for assessing the study risk of bias (and supporting sentences) across the following domains: random sequence generation, allocation concealment, blinding of participants and personnel, blinding of outcome assessment, incomplete outcome data and selective reporting.
+To train our model, we have leveraged the Cochrane Database of Systematic Reviews (CDSR) in lieu of manually annotated data, which would be expensive to collect. 
+The CDSR contains descriptions and data about clinical trials reported in existing systematic reviews. 
+Briefly, we match (the full-texts of) studies to entries in the CDSR, which contains risk of bias assessments; this provides document level labels. 
+The CDSR also contains sentences that annotators indicated as supporting their assessments. 
+We match these strings to substrings in the PDFs to provide sentence-level supervision. 
+This can thus be viewed as a \emph{distantly supervised} \cite{mintz-09,nguyen-11} approach.
+
+%%%
+% note that this is a little misleading right now -- we don't technically have this multi-task joint extraction thing going yet!!!
+%%%
+Concerning the risk of bias predictions, we have two tasks for a given article: (1) predict the overall risk of bias for each of the domains of interest, and, (2) extract the sentences that support these assessments.
+In both cases we leverage standard bag-of-words text encoding and linear-kernel support vector machines (SVMs). 
+Because the risk of bias predictions are correlated (across domains), we take a \emph{multi-task} \cite{evgeniou2004} approach to classification and jointly learn a model for the domains. 
+We accomplish this by way of a feature space construction that includes both shared and domain-specific terms (similar to the domain adaptation approach in \cite{daume2007}).
+
+With respect to the second task of sentence extraction, we \emph{jointly} assess the risk of bias associated with a given article \emph{and} the sentence(s) that support this judgement. 
+Specifically, we first make sentence level predictions (using one set of trained models), and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier.
+Due to space constraints here, we omit further specifics of our approach, but we provide further details elsewhere \cite{marshall2014}. 
+Figure \ref{fig:screenshot} shows example system output: the overall risk of bias with respect to random sequence generation is judged to be low, and supporting sentence
+%More specifically, the database we leverage contains structured and semi-structured data for each systematic review.
+Internally, the Cochrane Collaboration stores working versions of their reviews as XML.
+Each review contains a wealth of (structured) data about the clinical trials that met the review inclusion criteria.
+There are usually multiple clinical trials described in a single review.
+Cochrane reviews use basic clinical trial identifiers which are unique per review (based on the first author surname and year of publication) throughout these files.
+It is therefore possible to extract structured data, and filtered snippets of full text data which describe a single clinical trial.
+Using these identifiers, we were able to obtain full structured citation data for the primary reference of all included studies across the CDSR.
 
@@
 
-\section{Architecture overview}
+%\vspace{-2em}
+\section{Spá Architecture Overview}
 \label{section:architecture}
-\begin{figure}[htb]
-\centering
-\includegraphics[width=.9\linewidth]{./diagrams/sequence.pdf}
-\caption{\label{fig:sequence}Sequence diagram of a typical request-response}
-\end{figure}
+ \vspace{-1em}
+\begin{wrapfigure}{l}{0.5\textwidth}
+%\centering
+\begin{center}
+\includegraphics[scale=.275]{./diagrams/sequence.pdf}
+\end{center}
+\caption{\label{fig:sequence}Sequence diagram of a typical request-response in Spá.}
+\vspace{-2em}
+\end{wrapfigure}
+
 Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
@@
 The user can interactively activate and inspect specific results.
+\vspace{-1em}
 
-\section{Conclusion \& Future work}
+\section{Future work}
 We present a web-based tool for interactive visualization of annotations and meta-data on PDF documents.
-This allows users to see the results from machine learning systems within the context of a specific document.
-Moreover, we present a case study for \ac{ebm} by automatically extracting potential Risks of Bias, with supporting sentences.
+This allows users to see the results from machine learning predictions for a specific document.
+We have demonstrated the utility of this system within the context of \ac{ebm} by automatically extracting potential risks of bias (and supporting sentences) via state-of-the-art ML methods.
 
-However, we believe the tool to be useful for a much wider range of text mining and machine learning applications.
-To increase the generality of the tool work is being done to support a pluggable system for processing topologies, allowing developers to quickly plug in new systems.
+More generally, we believe the tool to be potentially useful for a much wider range of text mining and machine learning applications.
+To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated PDF annotation.
 Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
-The ultimate vision is to have a extensible system for semi-automated (machine assisted) screening, data extraction and data summarization.
+The ultimate vision is to have a extensible system for semi-automated (machine assisted) screening, data extraction and data summarization for EBM, and to allow rapid development of similar systems for other domains.
 
 \subsubsection{Acknowledgments}
-Part of this research was funded by the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement n° 261433
+Part of this research was funded by the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement n° 261433. % TODO add seed funds ack (BCW)
 

### 2014-04-23 static/scripts/helpers/annotator.js
Do not set color via injected CSS

@@ -1,5 +1,5 @@
 /* -*- tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2; js-indent-level: 2; -*- */
-define(['jQuery','underscore', 'Q', 'jQuery.injectCSS'], function($, _, Q) {
+define(['jQuery','underscore', 'Q'], function($, _, Q) {
   'use strict';
 
   var colors =
@@ -23,19 +23,6 @@ define(['jQuery','underscore', 'Q', 'jQuery.injectCSS'], function($, _, Q) {
     return str ? str.replace(/ /g, "-").toLowerCase() : null;
   };
 
-  function injectStyles(id, color) {
-    var styles = {};
-    var colorStr = color.join(",");
-    styles["." + id + "_header"] = {
-      "background-color": "rgb(" + colorStr + ") !important", // YOLO
-      "color": "white !important"
-    };
-    styles["." + id + "_annotation"] = {
-      "background-color": "rgb(" + colorStr + ")"
-    };
-    $.injectCSS(styles);
-  }
-
   var Annotator = {
     _postProcess: function(data) {
       data = _.clone(data);
@@ -43,7 +30,7 @@ define(['jQuery','underscore', 'Q', 'jQuery.injectCSS'], function($, _, Q) {
         var id = toClassName(result.name);
         result.active = idx == 0 ? true : false;
         result.id = id;
-        injectStyles(id, colors[idx % colors.length]);
+        result.color = colors[idx % colors.length];
       });
       return data;
     },

### 2014-04-23 static/scripts/main.js

@@ -20,7 +20,6 @@ require.config({
   shim: {
     'jQuery': { exports : 'jQuery' },
     'underscore': { exports : '_' },
-    'jQuery.injectCSS': { deps: ['jQuery'] },
     "backbone": {
       deps: ["jQuery", "underscore"],
       exports: "Backbone" },
@@ -70,9 +69,9 @@ define(function (require) {
     document.getElementById("minimap")
   );
 
-  appState.on("update:minimap", _.debounce(function(e, obj) {
+  appState.on("update:textNodes", _.debounce(function(e, obj) {
     minimap.forceUpdate();
-  }, 150, true));
+  }, 100, true));
 
   var $ = require("jQuery");
   appState.on("change:pdf", function(e, pdf) {

### 2014-04-23 static/scripts/models/appState.js

@@ -15,13 +15,13 @@ define(['backbone', 'PDFJS'], function(Backbone, PDFJS) {
     },
     defaults: {
       data: '',
-      minimap: [],
+      textNodes: [],
       pdf: {}
     },
     loadFromData: function(data) {
       var self = this;
       PDFJS.getDocument(data).then(function(pdf) {
-        self.set({pdf: pdf, minimap: []});
+        self.set({pdf: pdf, textNodes: []});
       });
     }
   });

### 2014-04-23 static/scripts/models/results.js

@@ -6,6 +6,7 @@ define(['backbone', 'helpers/annotator'], function(Backbone, Annotator) {
     defaults: {
       id: "",
       document: null,
+      color: null,
       name: "",
       active: false,
       annotations: []

### 2014-04-23 static/scripts/main.js
Minor fixes
- Paving the way for a color picker of sorts

@@ -71,7 +71,7 @@ define(function (require) {
 
   appState.on("update:textNodes", _.debounce(function(e, obj) {
     minimap.forceUpdate();
-  }, 100, true));
+  }, 150, true));
 
   var $ = require("jQuery");
   appState.on("change:pdf", function(e, pdf) {

### 2014-04-24 documentation/paper.tex
iain's partial pass at paper - redone abstract

@@
 \begin{abstract}
-Unstructured PDF documents remain the main vehicle for dissemination of scientific findings.
-Those interested in gathering and assimilating data must therefore manually peruse published articles and extract from these the elements of interest.
-\acl{ebm} provides a compelling illustration of this: many person-hours are spent each year extracting summary information from articles that describe clinical trials.
-This represents an enormous burden, especially in light of the expotentially increasing volume of published biomedical articles.
-Machine learning provides a potential means of mitigating this burden by automating extraction.
-But for automated approaches to be useful to end-users, we need tools that allow domain experts to interact with, and benefit from, model predictions.
-To this end, we present a web-based tool called Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}} that accepts as input an article and provides as output an automatically visually annotated rendering of this article.
-More generally, Spá provides a framework for visualizing predicted full-text PDF annotations, both at the document and sentence level.
+% Unstructured PDF documents remain the main vehicle for dissemination of scientific findings.
+% Those interested in gathering and assimilating data must therefore manually peruse published articles and extract from these the elements of interest.
+% \acl{ebm} provides a compelling illustration of this: many person-hours are spent each year extracting summary information from articles that describe clinical trials.
+% This represents an enormous burden, especially in light of the expotentially increasing volume of published biomedical articles.
+% Machine learning provides a potential means of mitigating this burden by automating extraction.
+% But for automated approaches to be useful to end-users, we need tools that allow domain experts to interact with, and benefit from, model predictions.
+% To this end, we present a web-based tool called Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}} that accepts as input an article and provides as output an automatically visually annotated rendering of this article.
+% More generally, Spá provides a framework for visualizing predicted full-text PDF annotations, both at the document and sentence level.
+
+Summarizing the evidence about medical interventions is an immense undertaking.
+Unstructured PDF documents remain the main vehicle for disseminating the results of clinical trials.
+Expert clinicians and researchers typically manually extract and synthesise information about effectiveness, adverse effects, and trial quality, which are published as \emph{systematic reviews}.
+We introduce Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}}, a web-based PDF viewer which uses machine learning modules to semi-automate the task of PDF annotation and summarisation.
+As an example, we demonstrate the use of Spá to semi-automate the assessment of bias in clinical trials.
+Spá allows the use of hybrid models which simultaneously classify PDF documents (specifically identifying trials at low risk of various biases), and also annotate sentences or words which contribute most to the classification.
+Spá is modular, and new models may be trivially added, thus allowing its use in other domains with a PDF-based literature, including law, physics, and biology.
+
 \end{abstract}
@@
 Imposing structure on full-text documents (e.g., identifying specific sentences of interest) is an important, challenging and practical task in natural language processing and machine learning.
-Consider \emph{systematic reviews} -- fundamental tools in \ac{ebm} \cite{sackett1996} -- which aim to address specific clinical questions by identifying and synthesizing data from all relevant published articles.
-When doing this one often needs, for example, to assess the \emph{risk of bias} for a particular study across different domains, such as bias due to improper blinding of participants and personnel.
-For this task, one wants to make a summary judgement (e.g., low risk of bias) and simultaneously extract the sentences supporting that judgement.
+\emph{Systematic reviews} are fundamental tools in \ac{ebm} \cite{sackett1996}, and aim to answer clinical questions by exhaustively searching the literature for relevant studies.
+Reviewers extract data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases, and synthesise this data to produce a textual and statistical summary.
+As an example, we demonstrate the task of bias assessment.
+Assessing bias is time-consuming.
+Assessing a single trial takes a domain expert around 10 minutes \cite{Hartling2011}.
+A single review may typically include several dozen trials, and due to empirical low rates of reviewer agreement, it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus\cite{Hartling2009}.
 
-Extracting such information from the unstructured text of clinical trial articles is a laborious process.
 Machine learning methods provide the machinery to automate such extractions; as they can effectively impose the desired structure onto PDFs.
@@
 Here we describe Spá, which aspires to realize this aim.
+
 Spá is an open-source, web-based tool that can incorporate state-of-the-art machine learning predictors to automatically annotate PDF articles.
@@
 \begin{figure}[htb]
+	\vspace{-2em}
 \centering
@@
 \caption{\label{fig:screenshot}Screenshot of a PDF with highlighted risk of bias.
-Here the risk of bias is assess to be low, for example, and one of the supporting sentences for this assessment describes the randomization procedure (highlighted in green).}
+Here the risk of bias is assessed to be low, for example, and one of the supporting sentences for this assessment describes the randomization procedure (highlighted in green).}
 \vspace{-2em}
@@
 Thus the contribution of this work is two-fold, as we present:
-(1) a practical tool (Spá) that incorporates cutting edge machine learning to help researchers rapidly assess the risk of biases (and sample sizes) in published biomedical articles, and,
+(1) a practical tool (Spá) that incorporates cutting-edge machine learning to help researchers rapidly assess the risk of biases (and sample sizes) in published biomedical articles, and,
 (2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
@@
 \subsection{Systematic Reviews}
-%%% sort of redundant with above; may want to re-factor
-The process of pooling and summarizing clinical trials is called \emph{systematic reviewing}, and forms the corner-stone of current \ac{ebm}.
-Systematic reviewing consists of specifying a precise clinical question and accompanying study inclusion criteria, and then exhaustively searching the literature to identify eligible studies. 
-Identified eligible studies are subsequently analyzed (i.e., synthesized), resulting in a summary of all of the published evidence that pertains to the clinical question of interest.
-Systematic reviews thus represent a rigorous, data-driven approach to answering clinical questions. 
-But conducting systematic reviews is complicated by the massive number of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials that were conducted in the last decade \cite{valkenhoef2012}.
-While methods and publishing standards are improving, many legacy publications will remain available only as PDF documents.
+% %%% sort of redundant with above; may want to re-factor
+% The process of pooling and summarizing clinical trials is called \emph{systematic reviewing}, and forms the corner-stone of current \ac{ebm}.
+% Systematic reviewing consists of specifying a precise clinical question and accompanying study inclusion criteria, and then exhaustively searching the literature to identify eligible studies. 
+% Identified eligible studies are subsequently analyzed (i.e., synthesized), resulting in a summary of all of the published evidence that pertains to the clinical question of interest.
+% Systematic reviews thus represent a rigorous, data-driven approach to answering clinical questions. 
+% But conducting systematic reviews is complicated by the massive number of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials that were conducted in the last decade \cite{valkenhoef2012}.
+% % While methods and publishing standards are improving, many legacy publications will remain available only as PDF documents.
 
-Extracting information of interest from these PDFs is imperative but laborious. 
-To mitigate this burden, we have constructed machine learning models that automatically extract some characteristics of interest.
-Specifically, our model predicts {\it risk of biases} across different domains as a function of the texts comprising articles. 
-It simultaneously extracts sentences supporting these predictions. 
-We briefly outline our approach to achieving this below. 
-We also note that we have a a separate model that extracts the study sample size from articles. 
-Spá -- our visualization tool -- provides a framework to upload PDFs and then render these predicted annotations. 
-We foresee adding additional predictors to this tool that, for example, may identify different treatment mentions within the text (e.g., drugs).
+% Extracting information of interest from these PDFs is imperative but laborious. 
+% To mitigate this burden, we have constructed machine learning models that automatically extract some characteristics of interest.
+% Specifically, our model predicts {\it risk of biases} across different domains as a function of the texts comprising articles. 
+% It simultaneously extracts sentences supporting these predictions. 
+% We briefly outline our approach to achieving this below. 
+% We also note that we have a a separate model that extracts the study sample size from articles. 
+% Spá -- our visualization tool -- provides a framework to upload PDFs and then render these predicted annotations. 
+% We foresee adding additional predictors to this tool that, for example, may identify different treatment mentions within the text (e.g., drugs).
 
-% made a web-based tool that allows the visualization of annotations within a PDF documents, and meta-information alongside it.
+% % made a web-based tool that allows the visualization of annotations within a PDF documents, and meta-information alongside it.
 

### 2014-04-24 documentation/paper.tex
some updates on the paper

@@
 Summarizing the evidence about medical interventions is an immense undertaking.
-Unstructured PDF documents remain the main vehicle for disseminating the results of clinical trials.
-Expert clinicians and researchers typically manually extract and synthesise information about effectiveness, adverse effects, and trial quality, which are published as \emph{systematic reviews}.
-We introduce Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}}, a web-based PDF viewer which uses machine learning modules to semi-automate the task of PDF annotation and summarisation.
-As an example, we demonstrate the use of Spá to semi-automate the assessment of bias in clinical trials.
-Spá allows the use of hybrid models which simultaneously classify PDF documents (specifically identifying trials at low risk of various biases), and also annotate sentences or words which contribute most to the classification.
-Spá is modular, and new models may be trivially added, thus allowing its use in other domains with a PDF-based literature, including law, physics, and biology.
+In part this is because unstructured PDF documents remain the main vehicle for disseminating the results of clinical trials.
+Clinicians and researchers typically manually extract and synthesise information regarding effectiveness, adverse effects, and trial quality, which are then published as \emph{systematic reviews}.
+We introduce Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}}, a web-based PDF viewer that allows for annotation and summarisation machine learning modules to semi-automate the task of PDF annotation and summarisation.
+To illustrate, we demonstrate the use of Spá to semi-automate the assessment of bias in clinical trials.
+Spá can visualize the output from hybrid models that simultaneously classify PDF documents (e.g., identifying trials as low risk of various biases), and also annotates sentences or words that contribute most to the classification.
+The Spá architecture is modular, and new models may be trivially added, thus the tool made be widely useful in other domains with a PDF-based literature, including law, physics, and biology.
 

### 2014-04-24 documentation/paper.tex
Pass at the paper

@@
 \acrodef{ebm}[EBM]{Evidence-based Medicine}
+\acrodef{ml}[ML]{Machine Learning}
+\acrodef{pdf}[PDF]{Portable Document Format}
+\acrodef{cdsr}[CDSR]{Cochrane Database of Systematic Reviews}
+\acrodef{svm}[SVM]{Support Vector Machine}
 
@@
 \begin{abstract}
-% Unstructured PDF documents remain the main vehicle for dissemination of scientific findings.
+% Unstructured \ac{pdf} documents remain the main vehicle for dissemination of scientific findings.
 % Those interested in gathering and assimilating data must therefore manually peruse published articles and extract from these the elements of interest.
@@
 % To this end, we present a web-based tool called Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}} that accepts as input an article and provides as output an automatically visually annotated rendering of this article.
-% More generally, Spá provides a framework for visualizing predicted full-text PDF annotations, both at the document and sentence level.
+% More generally, Spá provides a framework for visualizing predicted full-text \ac{pdf} annotations, both at the document and sentence level.
 
 Summarizing the evidence about medical interventions is an immense undertaking.
-In part this is because unstructured PDF documents remain the main vehicle for disseminating the results of clinical trials.
-Clinicians and researchers typically manually extract and synthesise information regarding effectiveness, adverse effects, and trial quality, which are then published as \emph{systematic reviews}.
-We introduce Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}}, a web-based PDF viewer that allows for annotation and summarisation machine learning modules to semi-automate the task of PDF annotation and summarisation.
+In part this is because unstructured \ac{pdf} documents remain the main vehicle for disseminating the results of clinical trials.
+Clinicians and researchers typically manually extract and synthesise information from these \acp{pdf} which is then published as a \emph{systematic review}.
+We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying and which is cognate with the present English word “spy,” continuing Proto-Germanic *spah- and the Proto-Indo-European root *(s)pe\`{k} (to see, to observe)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based \ac{pdf} viewer that allows for annotation and summarisation \acl{ml} modules to semi-automate the task of \ac{pdf} annotation and summarisation.
 To illustrate, we demonstrate the use of Spá to semi-automate the assessment of bias in clinical trials.
-Spá can visualize the output from hybrid models that simultaneously classify PDF documents (e.g., identifying trials as low risk of various biases), and also annotates sentences or words that contribute most to the classification.
-The Spá architecture is modular, and new models may be trivially added, thus the tool made be widely useful in other domains with a PDF-based literature, including law, physics, and biology.
-
+Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low risk of various biases), and also annotates sentences or words that contribute most to the classification.
+The Spá architecture is modular, and new models may be trivially added, thus the tool made be widely useful in other domains with a \ac{pdf}-based literature, including law, physics, and biology.
 \end{abstract}
@@
 \acresetall
+\acused{pdf}
 
@@
 %Finding sentences or words with particular characteristics within a document is an important task in natural language processing and machine learning.
-Imposing structure on full-text documents (e.g., identifying specific sentences of interest) is an important, challenging and practical task in natural language processing and machine learning.
-\emph{Systematic reviews} are fundamental tools in \ac{ebm} \cite{sackett1996}, and aim to answer clinical questions by exhaustively searching the literature for relevant studies.
-Reviewers extract data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases, and synthesise this data to produce a textual and statistical summary.
-As an example, we demonstrate the task of bias assessment.
-Assessing bias is time-consuming.
-Assessing a single trial takes a domain expert around 10 minutes \cite{Hartling2011}.
-A single review may typically include several dozen trials, and due to empirical low rates of reviewer agreement, it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus\cite{Hartling2009}.
+Imposing structure on full-text documents (e.g., identifying specific sentences of interest) is an important and practical task in natural language processing and machine learning.
+For example, \emph{systematic reviews} are fundamental tools in \ac{ebm} \cite{sackett1996}, and aim to answer clinical questions by exhaustively searching the literature for relevant studies.
+During systematic reviewing data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases, is extracted and synthesized to produce a textual and statistical summary.
+As an example, we demonstrate the task of bias assessment in which a reviewer assess, for example, whether the participants and personnel were properly blinded.
+Assessing this is a time-consuming task, a single trial can take a domain expert around ten minutes \cite{Hartling2011}.
+Making matters worse, a single review may typically include several dozen trials, and due to empirical low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus\cite{Hartling2009}.
 
-Machine learning methods provide the machinery to automate such extractions; as they can effectively impose the desired structure onto PDFs.
-For example, we can train a classifier to automatically assess the risk of bias across different domains and simulteanously identify the sentences supporting these assessments.
-We may also train a model that extracts the sample size from a paper describing a clinical trial. 
+\ac{ml} methods provide the machinery to automate such extractions; as they can effectively impose the desired structure onto \acp{pdf}.
+%For example, we can train a classifier to automatically assess the risk of bias across different domains and simulteanously identify the sentences supporting these assessments.
+%We may also train a model that extracts the sample size from a paper describing a clinical trial.
 But if such technologies are to be practically useful, we need tools that visualize these model predictions and annotations.
@@
 
-Spá is an open-source, web-based tool that can incorporate state-of-the-art machine learning predictors to automatically annotate PDF articles.
-As a practical (and useful) demonstration of this technology, we have built a machine learning system that automatically annotates PDFs to facilitate \ac{ebm}. 
-Specifically, this system leverages a multi-task model that simulteanously assesses the risk of biases across several domains, and extracts sample sizes from articles.
+Spá is an open-source, web-based tool that can incorporate state-of-the-art machine learning predictors to automatically annotate \ac{pdf} articles.
+As a practical demonstration of this technology, we have built a machine learning system that automatically annotates \acp{pdf} to facilitate \ac{ebm}.
+Specifically, this system leverages a multi-task model that simulteanously assesses the risk of biases across several domains.
 %Moreover, we have created machine learning systems on describing clinical trials with risk of bias predictions and extracted sample sizes.
-This tool is unique in that it leverages state-of-the-art ML models applied to full-text articles to assist practitioners of \ac{ebm} (and other biomedical researchers).
+This tool is unique in that it leverages state-of-the-art \ac{ml} models applied to full-text articles to assist practitioners of \ac{ebm}.
 
 \begin{figure}[htb]
-	\vspace{-2em}
+\vspace{-1em}
 \centering
-\includegraphics[width=.8\linewidth]{./images/screenshot2.png}
+\includegraphics[width=0.8\linewidth]{./images/screenshot2.png}
 \vspace{-1em}
-\caption{\label{fig:screenshot}Screenshot of a PDF with highlighted risk of bias.
+\caption{\label{fig:screenshot}Screenshot of a \ac{pdf} with highlighted risk of bias.
 Here the risk of bias is assessed to be low, for example, and one of the supporting sentences for this assessment describes the randomization procedure (highlighted in green).}
-\vspace{-2em}
+\vspace{-1em}
 \end{figure}
 
-While our application of interest is \ac{ebm}, we emphasize that the visualization tool can be used for any domain in which one wants to annotate PDFs. 
+While our application of interest is \ac{ebm}, we emphasize that the visualization tool can be used for any domain in which one wants to annotate \acp{pdf}.
 Thus the contribution of this work is two-fold, as we present:
-(1) a practical tool (Spá) that incorporates cutting-edge machine learning to help researchers rapidly assess the risk of biases (and sample sizes) in published biomedical articles, and,
+(1) a practical tool that incorporates machine learning to help researchers rapidly assess the risk of biases in published biomedical articles, and,
 (2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
@@
 
-\subsection{Systematic Reviews}
+% \subsection{Systematic Reviews}
 % %%% sort of redundant with above; may want to re-factor
@@
 % But conducting systematic reviews is complicated by the massive number of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials that were conducted in the last decade \cite{valkenhoef2012}.
-% % While methods and publishing standards are improving, many legacy publications will remain available only as PDF documents.
+% % While methods and publishing standards are improving, many legacy publications will remain available only as \ac{pdf} documents.
 
-% Extracting information of interest from these PDFs is imperative but laborious. 
+% Extracting information of interest from these \acp{pdf} is imperative but laborious.
 % To mitigate this burden, we have constructed machine learning models that automatically extract some characteristics of interest.
@@
 % We also note that we have a a separate model that extracts the study sample size from articles.
-% Spá -- our visualization tool -- provides a framework to upload PDFs and then render these predicted annotations. 
+% Spá -- our visualization tool -- provides a framework to upload \acp{pdf} and then render these predicted annotations.
 % We foresee adding additional predictors to this tool that, for example, may identify different treatment mentions within the text (e.g., drugs).
 
-% % made a web-based tool that allows the visualization of annotations within a PDF documents, and meta-information alongside it.
+% % made a web-based tool that allows the visualization of annotations within a \ac{pdf} documents, and meta-information alongside it.
 
@@
 We briefly describe our model for assessing the study risk of bias (and supporting sentences) across the following domains: random sequence generation, allocation concealment, blinding of participants and personnel, blinding of outcome assessment, incomplete outcome data and selective reporting.
-To train our model, we have leveraged the Cochrane Database of Systematic Reviews (CDSR) in lieu of manually annotated data, which would be expensive to collect. 
-The CDSR contains descriptions and data about clinical trials reported in existing systematic reviews. 
-Briefly, we match (the full-texts of) studies to entries in the CDSR, which contains risk of bias assessments; this provides document level labels. 
-The CDSR also contains sentences that annotators indicated as supporting their assessments. 
-We match these strings to substrings in the PDFs to provide sentence-level supervision. 
+To train our model, we have leveraged the \ac{cdsr} in lieu of manually annotated data, which would be expensive to collect.
+The \ac{cdsr} contains descriptions and data about clinical trials reported in existing systematic reviews.
+Briefly, we match (the full-texts of) studies to entries in the \ac{cdsr}, which contains risk of bias assessments; this provides document level labels.
+The \ac{cdsr} also contains sentences that annotators indicated as supporting their assessments.
+We match these strings to substrings in the \acp{pdf} to provide sentence-level supervision.
 This can thus be viewed as a \emph{distantly supervised} \cite{mintz-09,nguyen-11} approach.
@@
 %%%
-Concerning the risk of bias predictions, we have two tasks for a given article: (1) predict the overall risk of bias for each of the domains of interest, and, (2) extract the sentences that support these assessments.
-In both cases we leverage standard bag-of-words text encoding and linear-kernel support vector machines (SVMs). 
+Concerning the risk of bias predictions, we have two tasks for a given article.
+First, predict the overall risk of bias for each of the domains of interest, and second extract the sentences that support these assessments.
+In both cases we leverage standard bag-of-words text encoding and linear-kernel \acp{svm}.
 Because the risk of bias predictions are correlated (across domains), we take a \emph{multi-task} \cite{evgeniou2004} approach to classification and jointly learn a model for the domains.
@@
 
-With respect to the second task of sentence extraction, we \emph{jointly} assess the risk of bias associated with a given article \emph{and} the sentence(s) that support this judgement. 
+With respect to the second task of sentence extraction, we \emph{jointly} assess the risk of bias associated with a given article \emph{and} the sentences that support this judgment.
 Specifically, we first make sentence level predictions (using one set of trained models), and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier.
@@
 It is therefore possible to extract structured data, and filtered snippets of full text data which describe a single clinical trial.
-Using these identifiers, we were able to obtain full structured citation data for the primary reference of all included studies across the CDSR.
+Using these identifiers, we were able to obtain full structured citation data for the primary reference of all included studies across the \ac{cdsr}.
 
@@
 \section{Spá Architecture Overview}
-\label{section:architecture}
- \vspace{-1em}
-\begin{wrapfigure}{l}{0.5\textwidth}
-%\centering
-\begin{center}
-\includegraphics[scale=.275]{./diagrams/sequence.pdf}
-\end{center}
-\caption{\label{fig:sequence}Sequence diagram of a typical request-response in Spá.}
-\vspace{-2em}
-\end{wrapfigure}
-
 Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
@@
 The user can interactively activate and inspect specific results.
-\vspace{-1em}
+\label{section:architecture}
+\begin{wrapfigure}{R}{0.5\textwidth}
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{./diagrams/sequence.pdf}
+  \end{center}
+  \caption{\label{fig:sequence}Sequence diagram of a typical request-response in Spá.}
+\end{wrapfigure}
 
 \section{Future work}
-We present a web-based tool for interactive visualization of annotations and meta-data on PDF documents.
+We present a web-based tool for interactive visualization of annotations and meta-data on \ac{pdf} documents.
 This allows users to see the results from machine learning predictions for a specific document.
@@
 More generally, we believe the tool to be potentially useful for a much wider range of text mining and machine learning applications.
-To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated PDF annotation.
+To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated \ac{pdf} annotation.
 Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
-The ultimate vision is to have a extensible system for semi-automated (machine assisted) screening, data extraction and data summarization for EBM, and to allow rapid development of similar systems for other domains.
+The ultimate vision is to have an extensible system for semi-automated (machine assisted) screening, data extraction and data summarization for EBM, and to allow rapid development of similar systems for other domains.
 

### 2014-04-24 documentation/paper.tex
Minor revisions to paper

@@
 \usepackage{hyperref}
+\usepackage[multiple]{footmisc}
 \usepackage{microtype}
@@
 Summarizing the evidence about medical interventions is an immense undertaking.
-In part this is because unstructured \ac{pdf} documents remain the main vehicle for disseminating the results of clinical trials.
+In part because unstructured \ac{pdf} documents remain the main vehicle for disseminating the results of clinical trials.
 Clinicians and researchers typically manually extract and synthesise information from these \acp{pdf} which is then published as a \emph{systematic review}.
@@
 Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low risk of various biases), and also annotates sentences or words that contribute most to the classification.
-The Spá architecture is modular, and new models may be trivially added, thus the tool made be widely useful in other domains with a \ac{pdf}-based literature, including law, physics, and biology.
+The Spá architecture is modular and new models may be trivially added, thus the tool made be widely useful in other domains with a \ac{pdf}-based literature, including law, physics, and biology.
 \end{abstract}
@@
 Spá is an open-source, web-based tool that can incorporate state-of-the-art machine learning predictors to automatically annotate \ac{pdf} articles.
-As a practical demonstration of this technology, we have built a machine learning system that automatically annotates \acp{pdf} to facilitate \ac{ebm}.
+As a practical demonstration of this technology, we have built a machine learning system that automatically annotates \acp{pdf} to aid \ac{ebm}.
 Specifically, this system leverages a multi-task model that simulteanously assesses the risk of biases across several domains.
@@
 (2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
-These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}, respectively.
+These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}.
 
@@
 With respect to the second task of sentence extraction, we \emph{jointly} assess the risk of bias associated with a given article \emph{and} the sentences that support this judgment.
-Specifically, we first make sentence level predictions (using one set of trained models), and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier.
-Due to space constraints here, we omit further specifics of our approach, but we provide further details elsewhere \cite{marshall2014}.
+Specifically, we first make sentence level predictions (using one set of trained models), and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier (further details specified in \cite{marshall2014}).
 Figure \ref{fig:screenshot} shows example system output: the overall risk of bias with respect to random sequence generation is judged to be low, and supporting sentence
@@
 We present a web-based tool for interactive visualization of annotations and meta-data on \ac{pdf} documents.
-This allows users to see the results from machine learning predictions for a specific document.
-We have demonstrated the utility of this system within the context of \ac{ebm} by automatically extracting potential risks of bias (and supporting sentences) via state-of-the-art ML methods.
+It allows users to see the results from machine learning predictions for a specific document.
+We have show the use of this system within the context of \ac{ebm} by automatically extracting potential risks of bias (and supporting sentences) via state-of-the-art ML methods.
 
@@
 Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
-The ultimate vision is to have an extensible system for semi-automated (machine assisted) screening, data extraction and data summarization for EBM, and to allow rapid development of similar systems for other domains.
+The vision is to have an extensible system for semi-automated (machine assisted) screening, data extraction and data summarization for EBM, and to allow rapid development of similar systems for other domains.
 

### 2014-04-24 documentation/paper.tex
s/*data is/*data are/ in paper

@@
 For example, \emph{systematic reviews} are fundamental tools in \ac{ebm} \cite{sackett1996}, and aim to answer clinical questions by exhaustively searching the literature for relevant studies.
-During systematic reviewing data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases, is extracted and synthesized to produce a textual and statistical summary.
+During systematic reviewing data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases, are extracted and synthesized to produce a textual and statistical summary.
 As an example, we demonstrate the task of bias assessment in which a reviewer assess, for example, whether the participants and personnel were properly blinded.

### 2014-04-24 documentation/paper.tex
Minor fixes

@@
 The results of the text extraction are processed server-side by a variety of processing topologies, as outlined in figure \ref{fig:sequence}.
-Results, which could come from complicated machine learning systems, are communicated back to the browser and displayed using React components\footnote{\url{http://facebook.github.io/react}}.
+Results are communicated back to the browser and displayed using React components\footnote{\url{http://facebook.github.io/react}}.
 

### 2014-04-24 documentation/paper.tex
Remove redundant latex imports
paper edits
Conflicts:
	documentation/paper.pdf
	documentation/paper.tex
	documentation/revision.tex

@@
 \acrodef{ebm}[EBM]{Evidence-based Medicine}
-\acrodef{ml}[ML]{Machine Learning}
+% I don't think thi sneeds to be capitalized -- bcw
+\acrodef{ml}[ML]{machine learning}
 \acrodef{pdf}[PDF]{Portable Document Format}
@@
 
+%%% BCW -- I t
+
 \maketitle
@@
 
-Summarizing the evidence about medical interventions is an immense undertaking.
-In part because unstructured \ac{pdf} documents remain the main vehicle for disseminating the results of clinical trials.
-Clinicians and researchers typically manually extract and synthesise information from these \acp{pdf} which is then published as a \emph{systematic review}.
-We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying and which is cognate with the present English word “spy,” continuing Proto-Germanic *spah- and the Proto-Indo-European root *(s)pe\`{k} (to see, to observe)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based \ac{pdf} viewer that allows for annotation and summarisation \acl{ml} modules to semi-automate the task of \ac{pdf} annotation and summarisation.
-To illustrate, we demonstrate the use of Spá to semi-automate the assessment of bias in clinical trials.
-Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low risk of various biases), and also annotates sentences or words that contribute most to the classification.
+Summarizing the evidence concerning medical interventions is an immense undertaking, in part because unstructured \ac{pdf} documents remain the main vehicle for disseminating the results of clinical trials.
+Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf}s to be published in \emph{systematic reviews}.
+We introduce Spá,\footnote{From the Old Norse word spá or spæ referring to prophesying and which is cognate with the present English word “spy,” continuing Proto-Germanic *spah- and the Proto-Indo-European root *(s)pe\`{k} (to see, to observe)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}} a web-based viewer that enables automated annotation and summarisation of \ac{pdf}s via \ac{ml}.
+To illustrate its functionalility, here we use Spá to semi-automate the assessment of bias in clinical trials.
+Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low or high risk of various biases), and annotate sentences that support these classifications.
 The Spá architecture is modular and new models may be trivially added, thus the tool made be widely useful in other domains with a \ac{pdf}-based literature, including law, physics, and biology.
+
 \end{abstract}
@@
 
-%Finding sentences or words with particular characteristics within a document is an important task in natural language processing and machine learning.
-Imposing structure on full-text documents (e.g., identifying specific sentences of interest) is an important and practical task in natural language processing and machine learning.
-For example, \emph{systematic reviews} are fundamental tools in \ac{ebm} \cite{sackett1996}, and aim to answer clinical questions by exhaustively searching the literature for relevant studies.
-During systematic reviewing data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases, are extracted and synthesized to produce a textual and statistical summary.
-As an example, we demonstrate the task of bias assessment in which a reviewer assess, for example, whether the participants and personnel were properly blinded.
-Assessing this is a time-consuming task, a single trial can take a domain expert around ten minutes \cite{Hartling2011}.
-Making matters worse, a single review may typically include several dozen trials, and due to empirical low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus\cite{Hartling2009}.
+Imposing structure on full-text documents (e.g., identifying specific sentences of interest) is an important and practical task in natural language processing and machine learning, because doing so manually is laborious and costly.
+\emph{Systematic reviews} are an instructive example.
+Such reviews aim to answer clinical questions by exhaustively identifying and extracting information from all published relevant studies.
+They are fundamental tools in \ac{ebm} \cite{sackett1996}.
+The end product of a systematic review is an exhaustive synthesis (textual and statistical) of the current evidence.
+To produce these, reviewers must manually extract data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases from the free-text of published studies.
+These extraction tasks can be semi-automated using machine learning approaches.
+As an example, here we consider the task of bias assessment, in which a reviewers assess, e.g., whether study participants and personnel were properly blinded.
 
-\ac{ml} methods provide the machinery to automate such extractions; as they can effectively impose the desired structure onto \acp{pdf}.
-%For example, we can train a classifier to automatically assess the risk of bias across different domains and simulteanously identify the sentences supporting these assessments.
-%We may also train a model that extracts the sample size from a paper describing a clinical trial.
+Assessing this is a time-consuming task: a single trial can take a domain expert around ten minutes \cite{Hartling2011}.
+Making matters worse, a single review may typically include several dozen trials, and due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus \cite{Hartling2009}.
+Machine learning methods provide the machinery to automate such extractions; as they can effectively impose the desired structure onto \acp{pdf}. 
 But if such technologies are to be practically useful, we need tools that visualize these model predictions and annotations.
@@
 As a practical demonstration of this technology, we have built a machine learning system that automatically annotates \acp{pdf} to aid \ac{ebm}.
+% maybe?
 Specifically, this system leverages a multi-task model that simulteanously assesses the risk of biases across several domains.
-%Moreover, we have created machine learning systems on describing clinical trials with risk of bias predictions and extracted sample sizes.
 This tool is unique in that it leverages state-of-the-art \ac{ml} models applied to full-text articles to assist practitioners of \ac{ebm}.
@@
 (2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
-These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}.
+These contributions are described further in Sections \ref{section:EBM-ML} and \ref{section:architecture}.
 
@@
 %%%
-Concerning the risk of bias predictions, we have two tasks for a given article.
-First, predict the overall risk of bias for each of the domains of interest, and second extract the sentences that support these assessments.
-In both cases we leverage standard bag-of-words text encoding and linear-kernel \acp{svm}.
+From a \ac{ml} vantage, we have two tasks for a given article: (1) predict the overall risk of bias for each of the domains of interest, and (2) extract the sentences that support these assessments.
+For both tasks we leverage standard bag-of-words text encoding and linear-kernel \acp{svm}.
 Because the risk of bias predictions are correlated (across domains), we take a \emph{multi-task} \cite{evgeniou2004} approach to classification and jointly learn a model for the domains.
 We accomplish this by way of a feature space construction that includes both shared and domain-specific terms (similar to the domain adaptation approach in \cite{daume2007}). 
-
-With respect to the second task of sentence extraction, we \emph{jointly} assess the risk of bias associated with a given article \emph{and} the sentences that support this judgment.
+Furthermore, we take a unified approach to the two tasks by \emph{jointly} assessing the risk of bias associated with a given article \emph{and} extracting the sentences that support this judgment.
 Specifically, we first make sentence level predictions (using one set of trained models), and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier (further details specified in \cite{marshall2014}).
-Figure \ref{fig:screenshot} shows example system output: the overall risk of bias with respect to random sequence generation is judged to be low, and supporting sentence
+Figure \ref{fig:screenshot} shows example system output: in this case the overall risk of bias with respect to random sequence generation is judged to be low, and the supporting sentence for this judgement is highlighted in green.
 %More specifically, the database we leverage contains structured and semi-structured data for each systematic review.
@@
 The results of the text extraction are processed server-side by a variety of processing topologies, as outlined in figure \ref{fig:sequence}.
-Results are communicated back to the browser and displayed using React components\footnote{\url{http://facebook.github.io/react}}.
+Results, which could come from complicated machine learning systems, are communicated back to the browser and displayed using React components.\footnote{\url{http://facebook.github.io/react}}
 
-For each of the annotations the relevant nodes in the document are highlighted and a custom scrollbar, inspired by \href{http://substance.io/}{substance.io}\footnote{\url{http://substance.io/beta/}}, that acts as a mini-map is projected to show where it resides within the document.
+For each of the annotations the relevant nodes in the document are highlighted. 
+A custom scrollbar\footnote{inspired by \href{http://substance.io/}{substance.io}} that acts as a `mini-map' is projected to show where annotations reside within the document.
 The user can interactively activate and inspect specific results.
@@
 \section{Future work}
-We present a web-based tool for interactive visualization of annotations and meta-data on \ac{pdf} documents.
+We have presented a web-based tool for visualization of annotations and summarizations for \ac{pdf} documents.
 It allows users to see the results from machine learning predictions for a specific document.
-We have show the use of this system within the context of \ac{ebm} by automatically extracting potential risks of bias (and supporting sentences) via state-of-the-art ML methods.
+We have demonstrated the use of this system within the context of \ac{ebm} by automatically extracting potential risks of bias (and supporting sentences) via state-of-the-art ML methods.
 
 More generally, we believe the tool to be potentially useful for a much wider range of text mining and machine learning applications.
-To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated \ac{pdf} annotation.
-Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
+To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new ML systems for automated \ac{pdf} annotation.
+Furthermore, we are working to allow users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
 The vision is to have an extensible system for semi-automated (machine assisted) screening, data extraction and data summarization for EBM, and to allow rapid development of similar systems for other domains.
@@
 \subsubsection{Acknowledgments}
-Part of this research was funded by the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement n° 261433. % TODO add seed funds ack (BCW)
+Part of this research was funded by the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement n° 261433.
+% %TODO add seed funds ack (BCW) -- I can do this post-acceptance though
 

### 2014-04-24 documentation/paper.tex
Remove redundant packages
Minor fixes to paper

@@
 \usepackage{textcomp}
-\usepackage{wrapfig}
 \usepackage{marvosym}
@@
 \usepackage[multiple]{footmisc}
-\usepackage{microtype}
 \usepackage{acronym}
@@
 \acrodef{ebm}[EBM]{Evidence-based Medicine}
-% I don't think thi sneeds to be capitalized -- bcw
 \acrodef{ml}[ML]{machine learning}
@@
 These extraction tasks can be semi-automated using machine learning approaches.
-As an example, here we consider the task of bias assessment, in which a reviewers assess, e.g., whether study participants and personnel were properly blinded.
+As an example, here we consider the task of bias assessment, in which reviewers assess, e.g., whether study participants and personnel were properly blinded.
 
@@
 Making matters worse, a single review may typically include several dozen trials, and due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus \cite{Hartling2009}.
-Machine learning methods provide the machinery to automate such extractions; as they can effectively impose the desired structure onto \acp{pdf}. 
+\ac{ml} methods provide the machinery to automate such extractions; as they can effectively impose the desired structure onto \acp{pdf}.
 But if such technologies are to be practically useful, we need tools that visualize these model predictions and annotations.
@@
 
-Spá is an open-source, web-based tool that can incorporate state-of-the-art machine learning predictors to automatically annotate \ac{pdf} articles.
+Spá is an open-source, web-based tool that can incorporate state-of-the-art \acl{ml} predictors to automatically annotate \ac{pdf} articles.
 As a practical demonstration of this technology, we have built a machine learning system that automatically annotates \acp{pdf} to aid \ac{ebm}.
@@
 Specifically, this system leverages a multi-task model that simulteanously assesses the risk of biases across several domains.
-This tool is unique in that it leverages state-of-the-art \ac{ml} models applied to full-text articles to assist practitioners of \ac{ebm}.
+This tool is unique in that it leverages state-of-the-art \acl{ml} models applied to full-text articles to assist practitioners of \ac{ebm}.
 
@@
 (2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
-These contributions are described further in Sections \ref{section:EBM-ML} and \ref{section:architecture}.
+These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}.
 
@@
 It allows users to see the results from machine learning predictions for a specific document.
-We have demonstrated the use of this system within the context of \ac{ebm} by automatically extracting potential risks of bias (and supporting sentences) via state-of-the-art ML methods.
+We have demonstrated the use of this system within the context of \ac{ebm} by automatically extracting potential risks of bias (and supporting sentences) via state-of-the-art \ac{ml} methods.
 
 More generally, we believe the tool to be potentially useful for a much wider range of text mining and machine learning applications.
-To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new ML systems for automated \ac{pdf} annotation.
+To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new \ac{ml} systems for automated \ac{pdf} annotation.
 Furthermore, we are working to allow users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.

### 2014-04-24 pipeline.py
updates
Conflicts:
	documentation/paper.pdf
	documentation/paper.tex
	documentation/revision.tex
	pipeline.py

@@ -30,6 +30,134 @@ pp = pprint.PrettyPrinter(indent=2)
 # bcw -- imports for sample size prediction
 import sample_size_pipeline
 
+<<<<<<< HEAD
+=======
+import subprocess
+# MALLET_PATHS = "/Users/bwallace/dev/eclipse-workspace/mallet/bin/:/Users/bwallace/dev/eclipse-workspace/mallet/lib/mallet-deps.jar"
+# JAVA_PATH = "/usr/bin/java"
+
+MALLET_PATHS = "/Users/iain/Code/java/mallet/class/:/Users/iain/Code/java/mallet/lib/mallet-deps.jar"
+JAVA_PATH = "/usr/bin/java"
+
+
+def load_sample_size_model_and_vect(vect_path, model_path=None):
+    model, vect = None, None
+
+    if not model_path is None:
+        with open(model_path, 'rb') as model_f:
+            model = pickle.load(model_f)
+
+
+    with open(vect_path, 'rb') as vect_f:
+        vect = pickle.load(vect_f)
+
+    return vect, model
+
+class TxPipeline(Pipeline):
+    '''
+    '''
+    pipeline_title = "TX"
+
+    def __init__(self, crf_model_path="models/tx/crf.model.mallet"):
+        #logger.info("%s: loading models" % (self.pipeline_title))
+        self.vectorizer, self.clf = load_sample_size_model_and_vect(
+                                        'models/tx/crf.vectorizer.pickle')
+        self.crf_model_path = crf_model_path
+        logger.info("assuming trained CRF is @ %s" % self.crf_model_path)
+        logger.info("%s: done loading models" % (self.pipeline_title))
+
+        
+
+    def predict(self, full_text):
+        tx_pipeline = sample_size_pipeline.bilearnPipeline(full_text, swap_numbers=False)
+        tx_pipeline.generate_features()
+        features = tx_pipeline.get_features(flatten=True)
+        mallet_str = TxPipeline.to_mallet(self.vectorizer.transform(features))
+        mallet_input_file = "models/tx/crf.tmp.mallet"
+        with open(mallet_input_file, 'wb') as out_f:
+            out_f.write(mallet_str)
+        
+        predictions, errors = TxPipeline.mallet_predict(
+                mallet_input_file, self.crf_model_path)
+        predictions = [int(pred.strip()) for pred in predictions.split("\n") if pred.strip()!='']
+        tx_words = tx_pipeline.get_words(flatten=True)
[…]

### 2014-04-25 documentation/paper.tex
Minor fixes to paper

@@
 
-Summarizing the evidence concerning medical interventions is an immense undertaking, in part because unstructured \ac{pdf} documents remain the main vehicle for disseminating the results of clinical trials.
-Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf}s to be published in \emph{systematic reviews}.
-We introduce Spá,\footnote{From the Old Norse word spá or spæ referring to prophesying and which is cognate with the present English word “spy,” continuing Proto-Germanic *spah- and the Proto-Indo-European root *(s)pe\`{k} (to see, to observe)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}} a web-based viewer that enables automated annotation and summarisation of \ac{pdf}s via \ac{ml}.
+Summarizing the evidence about medical interventions is an immense undertaking, in part because unstructured \ac{pdf} documents remain the main vehicle for disseminating the results of clinical trials.
+Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf} to be published in \emph{systematic reviews}.
+We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying and which is cognate with the present English word “spy,” continuing Proto-Germanic *spah- and the Proto-Indo-European root *(s)pe\`{k} (to see, to observe)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \acl{ml}.
 To illustrate its functionalility, here we use Spá to semi-automate the assessment of bias in clinical trials.
 Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low or high risk of various biases), and annotate sentences that support these classifications.
-The Spá architecture is modular and new models may be trivially added, thus the tool made be widely useful in other domains with a \ac{pdf}-based literature, including law, physics, and biology.
+Spá has a modular architecture and new models may be trivially added, therefore the tool may be widely useful in other domains with a \ac{pdf}-based literature, including law, physics, and biology.
 
@@
 They are fundamental tools in \ac{ebm} \cite{sackett1996}.
-The end product of a systematic review is an exhaustive synthesis (textual and statistical) of the current evidence.
+The end product of a systematic review is an exhaustive textual and statistical synthesis of the current evidence.
 To produce these, reviewers must manually extract data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases from the free-text of published studies.
 These extraction tasks can be semi-automated using machine learning approaches.
-As an example, here we consider the task of bias assessment, in which reviewers assess, e.g., whether study participants and personnel were properly blinded.
+As an example, here we consider the risk of bias assessment, in which reviewers assess, e.g., whether study participants and personnel were properly blinded.
 
-Assessing this is a time-consuming task: a single trial can take a domain expert around ten minutes \cite{Hartling2011}.
-Making matters worse, a single review may typically include several dozen trials, and due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus \cite{Hartling2009}.
-\ac{ml} methods provide the machinery to automate such extractions; as they can effectively impose the desired structure onto \acp{pdf}.
+Assessing this is a time-consuming task.
+A single trial may typically take a domain expert ten minutes \cite{Hartling2011}, and a single review may typically include several dozen trials.
+Making matters worse, due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus \cite{Hartling2009}.
+
+Machine learning methods provide the machinery to automate such extractions; as they can effectively impose structure onto \acp{pdf}.
+
 But if such technologies are to be practically useful, we need tools that visualize these model predictions and annotations.
@@
 
-Spá is an open-source, web-based tool that can incorporate state-of-the-art \acl{ml} predictors to automatically annotate \ac{pdf} articles.
+Spá is an open-source, web-based tool that can incorporate state-of-the-art machine learning to automatically annotate \ac{pdf} articles.
 As a practical demonstration of this technology, we have built a machine learning system that automatically annotates \acp{pdf} to aid \ac{ebm}.
@@
 The results of the text extraction are processed server-side by a variety of processing topologies, as outlined in figure \ref{fig:sequence}.
-Results, which could come from complicated machine learning systems, are communicated back to the browser and displayed using React components.\footnote{\url{http://facebook.github.io/react}}
+Results are communicated back to the browser and displayed using React components.\footnote{\url{http://facebook.github.io/react}}
 
-For each of the annotations the relevant nodes in the document are highlighted.
+For each of the annotations the relevant text nodes in the document are highlighted.
 A custom scrollbar\footnote{inspired by \href{http://substance.io/}{substance.io}} that acts as a `mini-map' is projected to show where annotations reside within the document.

### 2014-04-28 pipeline.py
Fix missed merge conflict

@@ -30,135 +30,6 @@ pp = pprint.PrettyPrinter(indent=2)
 # bcw -- imports for sample size prediction
 import sample_size_pipeline
 
-<<<<<<< HEAD
-=======
-import subprocess
-# MALLET_PATHS = "/Users/bwallace/dev/eclipse-workspace/mallet/bin/:/Users/bwallace/dev/eclipse-workspace/mallet/lib/mallet-deps.jar"
-# JAVA_PATH = "/usr/bin/java"
-
-MALLET_PATHS = "/Users/iain/Code/java/mallet/class/:/Users/iain/Code/java/mallet/lib/mallet-deps.jar"
-JAVA_PATH = "/usr/bin/java"
-
-
-def load_sample_size_model_and_vect(vect_path, model_path=None):
-    model, vect = None, None
-
-    if not model_path is None:
-        with open(model_path, 'rb') as model_f:
-            model = pickle.load(model_f)
-
-
-    with open(vect_path, 'rb') as vect_f:
-        vect = pickle.load(vect_f)
-
-    return vect, model
-
-class TxPipeline(Pipeline):
-    '''
-    '''
-    pipeline_title = "TX"
-
-    def __init__(self, crf_model_path="models/tx/crf.model.mallet"):
-        #logger.info("%s: loading models" % (self.pipeline_title))
-        self.vectorizer, self.clf = load_sample_size_model_and_vect(
-                                        'models/tx/crf.vectorizer.pickle')
-        self.crf_model_path = crf_model_path
-        logger.info("assuming trained CRF is @ %s" % self.crf_model_path)
-        logger.info("%s: done loading models" % (self.pipeline_title))
-
-        
-
-    def predict(self, full_text):
-        tx_pipeline = sample_size_pipeline.bilearnPipeline(full_text, swap_numbers=False)
-        tx_pipeline.generate_features()
-        features = tx_pipeline.get_features(flatten=True)
-        mallet_str = TxPipeline.to_mallet(self.vectorizer.transform(features))
-        mallet_input_file = "models/tx/crf.tmp.mallet"
-        with open(mallet_input_file, 'wb') as out_f:
-            out_f.write(mallet_str)
-        
-        predictions, errors = TxPipeline.mallet_predict(
-                mallet_input_file, self.crf_model_path)
-        predictions = [int(pred.strip()) for pred in predictions.split("\n") if pred.strip()!='']
-        tx_words = tx_pipeline.get_words(flatten=True)
[…]

### 2014-04-28 abstract_pipeline.py
Project clean-slate
* Clojure stub
* Directory tree structure
* Removed all python server code

@@ -1,141 +1,0 @@
-from abc import ABCMeta, abstractmethod
-import logging
-from functools import wraps
-import time
-
-log = logging.getLogger(__name__)
-
-def timethis(func):
-    '''
-    Decorator that reports the execution time.
-    '''
-    @wraps(func)
-    def wrapper(*args, **kwargs):
-        start = time.time()
-        result = func(*args, **kwargs)
-        end = time.time()
-        log.debug("call to {} took {}".format(func.__name__, end-start))
-        return result
-    return wrapper
-
-class OverlappingIntervals():
-    """
-    maintains a list of start, end tuples
-    and calculates overlaps
-    """
-    def __init__(self, intervals):
-        """
-        takes intervals = list of (start, end) tuples and sorts them
-        """
-        self.intervals = sorted(intervals)
-
-    def _is_overlapping(self, i1, i2):
-        return i2[0] < i1[1] and i1[0] < i2[1]
-
-    def overlap(self, bounds):
-        """
-        bounds = (start, end) tuple
-        returns all overlapping bounds
-        """
-        return [interval for interval in self.intervals if self._is_overlapping(interval, bounds)]
-
-    def overlap_indices(self, bounds):
-        """
-        return the 0 indexed positions and bounds of overlapping bounds
-        """
-        return [{"index": index, "interval": interval} for index, interval in enumerate(self.intervals) if self._is_overlapping(interval, bounds)]
-
-class Pipeline(object):
-    __metaclass__ = ABCMeta
-
-    pipeline_title = ""
-
-    def __preprocess(self, pages):
-        # we need to do two things, create a single string for each page
-        # and establish a method to figure out the original nodes
-        parsed = []
-
-        for idx, page in enumerate(pages):
-            if page is not None:
-                textNodes = [node["str"].encode("utf8") for node in page["items"]]
-
-                total = 0
-                ranges = []
-                for txt in textNodes:
-
-                    start = total
-                    total += len(txt)
-                    ranges.append((start, total))
-
-                    total += 1
-                    # note that this +=1 aligns both for spaces added later between nodes *and* pages
-                    # (since the ' '.join(nodes) does not leave a trailing space, but we add one anyway)
-
-                intervals = OverlappingIntervals(ranges)
-                page_str = " ".join(textNodes)
-
-                parsed.append({"str": page_str,
-                               "length": total,
-                               "intervals": intervals})
-            else:
[…]

### 2014-04-28 pipeline.py

@@ -1,184 +1,0 @@
-#
-#   pipeline.py
-#
-#   N.B. predictive modelling requires a trained model in pickle form:
-#   - get `quality_models.pck` from `Dropbox/cochranetech/quality-prediction-results/models`
-#   - put in the `models/` directory
-#
-
-from abstract_pipeline import Pipeline
-import pdb
-from indexnumbers import swap_num
-
-# custom tokenizers based on NLTK
-from tokenizers import word_tokenizer, sent_tokenizer
-
-import collections
-
-import cPickle as pickle
-
-import quality3
-import sklearn
-
-import logging
-logger = logging.getLogger(__name__)
-
-import pprint
-pp = pprint.PrettyPrinter(indent=2)
-
-####
-# bcw -- imports for sample size prediction
-import sample_size_pipeline
-
-class SampleSizePipeline(Pipeline):
-    """
-    @TODO
-    """
-    pipeline_title = "Sample Size"
-    def __init__(self):
-        logger.info("%s: loading models" % (self.pipeline_title))
-        self.vectorizer, self.clf = self.load_sample_size_model_and_vect(
-                                    'models/sample_size/sample_size_vectorizer_ft.pickle',
-                                    'models/sample_size/sample_size_predictor_ft.pickle')
-        logger.info("%s: done loading models" % (self.pipeline_title))
-
-
-    def load_sample_size_model_and_vect(self, vect_path, model_path):
-        model, vect = None, None
-        with open(model_path, 'rb') as model_f:
-            model = pickle.load(model_f)
-
-        with open(vect_path, 'rb') as vect_f:
-            vect = pickle.load(vect_f)
-
-        return vect, model
-
-    @staticmethod
-    def integer_filter(w):
-        return w['num'] == True
-
-    def predict(self, full_text):
-        ss_pipeline = sample_size_pipeline.bilearnPipeline(full_text)
-        ss_pipeline.generate_features()
-        features = ss_pipeline.get_features(filter=SampleSizePipeline.integer_filter, flatten=True)
-        X = self.vectorizer.transform(features)
-        preds = self.clf.decision_function(X)
-        sl_words = ss_pipeline.get_words(filter=SampleSizePipeline.integer_filter, flatten=True)
-        predicted_i = preds.argmax()
-        predicted = sl_words[predicted_i]
-        print "predicted sample size: %s" % predicted
-
-        '''
-        So this is kind of hacky. The deal is that we need to
-        get the spans for the predicted sample size. To this
[…]

### 2014-04-28 resources/build.js

@@ -1,5 +1,5 @@
 ({
-    appDir: "./static",
+    appDir: "./public",
     baseUrl: "./scripts",
     dir: "./build",
     optimize: "uglify2",
@@ -8,7 +8,7 @@
     // call with `node r.js -o build.js`
     // add `optimize=none` to skip script optimization (useful during debugging).
 
-    mainConfigFile: "./static/scripts/main.js",
+    mainConfigFile: "./public/scripts/main.js",
     onBuildWrite: function (moduleName, path, singleContents) {
         return singleContents.replace(/jsx!/g, '');
     },

### 2014-04-28 server.py

@@ -1,32 +1,0 @@
-import pdb
-
-from flask import Flask, request, jsonify
-from pipeline import RiskOfBiasPipeline, SampleSizePipeline
-import json
-import logging
-
-DEBUG_MODE = True
-
-logging.basicConfig(level=(logging.DEBUG if DEBUG_MODE else logging.INFO))
-logger = logging.getLogger(__name__)
-
-app = Flask(__name__)
-pipelines = [RiskOfBiasPipeline(), SampleSizePipeline()]
-
-@app.route('/')
-def root():
-    return app.send_static_file('index.html')
-
-@app.route('/annotate', methods=['POST'])
-def annotate():
-    payload = json.loads(request.data)
-
-    results = [p.run(payload["pages"]) for p in pipelines]
-    result = reduce(lambda memo, r: memo + r["result"], results, [])
-
-    response = {}
-    response["result"] = result
-    return jsonify(response)
-
-if __name__ == "__main__":
-    app.run(debug=DEBUG_MODE)

### 2014-04-28 tokenizers.py

@@ -1,78 +1,0 @@
-#
-#	tokenizers.py
-#
-#	custom adaptations of the nltk tokenizers to suit scientific article parsing
-#
-
-from nltk.tokenize.punkt import *
-from functools import wraps
-from itertools import izip
-
-class CochraneNLPLanguageVars(PunktLanguageVars):
-    _re_non_word_chars   = r"(?:[?!)\";}\]\*:@\'\({\[=\.])" # added =
-    """Characters that cannot appear within words"""
-
-    _re_word_start    = r"[^\(\"\`{\[:;&\#\*@\)}\]\-,=]" # added =
-    """Excludes some characters from starting word tokens"""
-
-class newPunktWordTokenizer(TokenizerI):
-    """
-    taken from new version of NLTK 3.0 alpha
-    to allow for span tokenization of words (current
-    full version does not allow this)
-    """
-    def __init__(self, lang_vars=CochraneNLPLanguageVars()):
-        self._lang_vars = lang_vars
-        
-
-    def tokenize(self, text):
-        return self._lang_vars.word_tokenize(text)
-
-    def span_tokenize(self, text):
-        """
-        Given a text, returns a list of the (start, end) spans of words
-        in the text.
-        """
-        return [(sl.start, sl.stop) for sl in self._slices_from_text(text)]
-
-     
-    def _slices_from_text(self, text):
-        last_break = 0
-        contains_no_words = True
-        for match in self._lang_vars._word_tokenizer_re().finditer(text):
-            contains_no_words = False
-            context = match.group()
-            yield slice(match.start(), match.end())
-        if contains_no_words:
-            yield slice(0, 0) # matches PunktSentenceTokenizer's functionality
-
-word_tokenizer = newPunktWordTokenizer()
-sent_tokenizer = PunktSentenceTokenizer()
-
-def filters(func):
-    """
-    used as decorator
-    allows pipeline functions to return helpful
-    views/permetations of output data - flattened lists
-    and filters based on the base (hidden) features
-    """
-    @wraps(func)
-    def wrapper(self, *args, **kwargs):
-        
-        flatten = kwargs.pop("flatten", False)
-        filter = kwargs.pop("filter", None)
-
-        raw_output = func(self, *args, **kwargs)
-        if filter:
-            filtered_output = [[raw_word for raw_word, base_word in izip(raw_sent, base_sent) if filter(base_word)]
-                                for raw_sent, base_sent in izip(raw_output, self.functions)]
-        else:
[…]

### 2014-04-29 services/gen-java/spa/services/services/Echo.java
Add generated code
thrift -r --gen py:utf8strings,dynamic services.thrift
thrift -r --gen java:hashcode services.thrift

@@ -1,0 +1,972 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.services;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class Echo {
+
+  public interface Iface {
+
+    public String echo(String input) throws org.apache.thrift.TException;
+
+  }
+
+  public interface AsyncIface {
+
+    public void echo(String input, org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
+
+  }
+
+  public static class Client extends org.apache.thrift.TServiceClient implements Iface {
+    public static class Factory implements org.apache.thrift.TServiceClientFactory<Client> {
+      public Factory() {}
+      public Client getClient(org.apache.thrift.protocol.TProtocol prot) {
+        return new Client(prot);
+      }
+      public Client getClient(org.apache.thrift.protocol.TProtocol iprot, org.apache.thrift.protocol.TProtocol oprot) {
+        return new Client(iprot, oprot);
+      }
+    }
+
+    public Client(org.apache.thrift.protocol.TProtocol prot)
+    {
+      super(prot, prot);
+    }
+
[…]

### 2014-04-29 services/gen-java/spa/services/services/Filter.java

@@ -1,0 +1,2062 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.services;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class Filter {
+
+  public interface Iface {
+
+    public void ping() throws org.apache.thrift.TException;
+
+    public spa.services.structs.Document run(spa.services.structs.Document document) throws ProcessException, org.apache.thrift.TException;
+
+    public void shutdown() throws org.apache.thrift.TException;
+
+  }
+
+  public interface AsyncIface {
+
+    public void ping(org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
+
+    public void run(spa.services.structs.Document document, org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
+
+    public void shutdown(org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
+
+  }
+
+  public static class Client extends org.apache.thrift.TServiceClient implements Iface {
+    public static class Factory implements org.apache.thrift.TServiceClientFactory<Client> {
+      public Factory() {}
+      public Client getClient(org.apache.thrift.protocol.TProtocol prot) {
+        return new Client(prot);
+      }
[…]

### 2014-04-29 services/gen-java/spa/services/services/PDFParser.java

@@ -1,0 +1,1937 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.services;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class PDFParser {
+
+  public interface Iface {
+
+    public void ping() throws org.apache.thrift.TException;
+
+    public spa.services.structs.Document parse(String file) throws org.apache.thrift.TException;
+
+    public void shutdown() throws org.apache.thrift.TException;
+
+  }
+
+  public interface AsyncIface {
+
+    public void ping(org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
+
+    public void parse(String file, org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
+
+    public void shutdown(org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
+
+  }
+
+  public static class Client extends org.apache.thrift.TServiceClient implements Iface {
+    public static class Factory implements org.apache.thrift.TServiceClientFactory<Client> {
+      public Factory() {}
+      public Client getClient(org.apache.thrift.protocol.TProtocol prot) {
[…]

### 2014-04-29 services/gen-java/spa/services/services/ProcessException.java

@@ -1,0 +1,607 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.services;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class ProcessException extends TException implements org.apache.thrift.TBase<ProcessException, ProcessException._Fields>, java.io.Serializable, Cloneable, Comparable<ProcessException> {
+  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("ProcessException");
+
+  private static final org.apache.thrift.protocol.TField TIMESTAMP_FIELD_DESC = new org.apache.thrift.protocol.TField("timestamp", org.apache.thrift.protocol.TType.I32, (short)1);
+  private static final org.apache.thrift.protocol.TField WHAT_FIELD_DESC = new org.apache.thrift.protocol.TField("what", org.apache.thrift.protocol.TType.STRING, (short)2);
+  private static final org.apache.thrift.protocol.TField WHY_FIELD_DESC = new org.apache.thrift.protocol.TField("why", org.apache.thrift.protocol.TType.STRING, (short)3);
+
+  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
+  static {
[…]

### 2014-04-29 services/gen-java/spa/services/structs/Annotation.java

@@ -1,0 +1,609 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.structs;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class Annotation implements org.apache.thrift.TBase<Annotation, Annotation._Fields>, java.io.Serializable, Cloneable, Comparable<Annotation> {
+  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Annotation");
+
+  private static final org.apache.thrift.protocol.TField UUID_FIELD_DESC = new org.apache.thrift.protocol.TField("uuid", org.apache.thrift.protocol.TType.STRING, (short)1);
+  private static final org.apache.thrift.protocol.TField LABEL_FIELD_DESC = new org.apache.thrift.protocol.TField("label", org.apache.thrift.protocol.TType.I32, (short)2);
+  private static final org.apache.thrift.protocol.TField __META_FIELD_DESC = new org.apache.thrift.protocol.TField("__meta", org.apache.thrift.protocol.TType.STRUCT, (short)3);
+
[…]

### 2014-04-29 services/gen-java/spa/services/structs/Document.java

@@ -1,0 +1,887 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.structs;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class Document implements org.apache.thrift.TBase<Document, Document._Fields>, java.io.Serializable, Cloneable, Comparable<Document> {
+  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Document");
+
+  private static final org.apache.thrift.protocol.TField TEXT_FIELD_DESC = new org.apache.thrift.protocol.TField("text", org.apache.thrift.protocol.TType.STRING, (short)1);
+  private static final org.apache.thrift.protocol.TField MARGINALIA_FIELD_DESC = new org.apache.thrift.protocol.TField("marginalia", org.apache.thrift.protocol.TType.LIST, (short)2);
+  private static final org.apache.thrift.protocol.TField __META_FIELD_DESC = new org.apache.thrift.protocol.TField("__meta", org.apache.thrift.protocol.TType.MAP, (short)3);
[…]

### 2014-04-29 services/gen-java/spa/services/structs/Interval.java

@@ -1,0 +1,484 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.structs;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class Interval implements org.apache.thrift.TBase<Interval, Interval._Fields>, java.io.Serializable, Cloneable, Comparable<Interval> {
+  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Interval");
+
+  private static final org.apache.thrift.protocol.TField UPPER_FIELD_DESC = new org.apache.thrift.protocol.TField("upper", org.apache.thrift.protocol.TType.I32, (short)1);
+  private static final org.apache.thrift.protocol.TField LOWER_FIELD_DESC = new org.apache.thrift.protocol.TField("lower", org.apache.thrift.protocol.TType.I32, (short)2);
+
+  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
+  static {
+    schemes.put(StandardScheme.class, new IntervalStandardSchemeFactory());
+    schemes.put(TupleScheme.class, new IntervalTupleSchemeFactory());
+  }
+
+  public int upper; // required
+  public int lower; // required
+
[…]

### 2014-04-29 services/gen-java/spa/services/structs/Mapping.java

@@ -1,0 +1,604 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.structs;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class Mapping implements org.apache.thrift.TBase<Mapping, Mapping._Fields>, java.io.Serializable, Cloneable, Comparable<Mapping> {
+  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Mapping");
+
+  private static final org.apache.thrift.protocol.TField TEXT_NODES_FIELD_DESC = new org.apache.thrift.protocol.TField("textNodes", org.apache.thrift.protocol.TType.LIST, (short)1);
+  private static final org.apache.thrift.protocol.TField RANGES_FIELD_DESC = new org.apache.thrift.protocol.TField("ranges", org.apache.thrift.protocol.TType.LIST, (short)2);
+
+  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
+  static {
+    schemes.put(StandardScheme.class, new MappingStandardSchemeFactory());
[…]

### 2014-04-29 services/gen-java/spa/services/structs/Marginalis.java

@@ -1,0 +1,765 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.structs;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class Marginalis implements org.apache.thrift.TBase<Marginalis, Marginalis._Fields>, java.io.Serializable, Cloneable, Comparable<Marginalis> {
+  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Marginalis");
+
+  private static final org.apache.thrift.protocol.TField ID_FIELD_DESC = new org.apache.thrift.protocol.TField("id", org.apache.thrift.protocol.TType.STRING, (short)1);
+  private static final org.apache.thrift.protocol.TField TITLE_FIELD_DESC = new org.apache.thrift.protocol.TField("title", org.apache.thrift.protocol.TType.STRING, (short)2);
+  private static final org.apache.thrift.protocol.TField DESCRIPTION_FIELD_DESC = new org.apache.thrift.protocol.TField("description", org.apache.thrift.protocol.TType.STRING, (short)3);
[…]

### 2014-04-29 services/gen-java/spa/services/structs/MetaReference.java

@@ -1,0 +1,499 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.structs;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class MetaReference implements org.apache.thrift.TBase<MetaReference, MetaReference._Fields>, java.io.Serializable, Cloneable, Comparable<MetaReference> {
+  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("MetaReference");
+
+  private static final org.apache.thrift.protocol.TField FIELD_FIELD_DESC = new org.apache.thrift.protocol.TField("field", org.apache.thrift.protocol.TType.STRING, (short)1);
+  private static final org.apache.thrift.protocol.TField IDX_FIELD_DESC = new org.apache.thrift.protocol.TField("idx", org.apache.thrift.protocol.TType.I32, (short)2);
+
+  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
+  static {
+    schemes.put(StandardScheme.class, new MetaReferenceStandardSchemeFactory());
[…]

### 2014-04-29 services/gen-java/spa/services/structs/TextNode.java

@@ -1,0 +1,504 @@
+/**
+ * Autogenerated by Thrift Compiler (0.9.1)
+ *
+ * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+ *  @generated
+ */
+package spa.services.structs;
+
+import org.apache.commons.lang3.builder.HashCodeBuilder;
+import org.apache.thrift.scheme.IScheme;
+import org.apache.thrift.scheme.SchemeFactory;
+import org.apache.thrift.scheme.StandardScheme;
+
+import org.apache.thrift.scheme.TupleScheme;
+import org.apache.thrift.protocol.TTupleProtocol;
+import org.apache.thrift.protocol.TProtocolException;
+import org.apache.thrift.EncodingUtils;
+import org.apache.thrift.TException;
+import org.apache.thrift.async.AsyncMethodCallback;
+import org.apache.thrift.server.AbstractNonblockingServer.*;
+import java.util.List;
+import java.util.ArrayList;
+import java.util.Map;
+import java.util.HashMap;
+import java.util.EnumMap;
+import java.util.Set;
+import java.util.HashSet;
+import java.util.EnumSet;
+import java.util.Collections;
+import java.util.BitSet;
+import java.nio.ByteBuffer;
+import java.util.Arrays;
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+
+public class TextNode implements org.apache.thrift.TBase<TextNode, TextNode._Fields>, java.io.Serializable, Cloneable, Comparable<TextNode> {
+  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("TextNode");
+
+  private static final org.apache.thrift.protocol.TField PAGE_INDEX_FIELD_DESC = new org.apache.thrift.protocol.TField("pageIndex", org.apache.thrift.protocol.TType.I32, (short)1);
+  private static final org.apache.thrift.protocol.TField INTERVAL_FIELD_DESC = new org.apache.thrift.protocol.TField("interval", org.apache.thrift.protocol.TType.STRUCT, (short)2);
+
+  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
+  static {
+    schemes.put(StandardScheme.class, new TextNodeStandardSchemeFactory());
[…]

### 2014-04-29 services/gen-py/services/Echo.py

@@ -1,0 +1,144 @@
+#
+# Autogenerated by Thrift Compiler (0.9.1)
+#
+# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+#
+#  options string: py:utf8strings,dynamic
+#
+
+from thrift.Thrift import TType, TMessageType, TException, TApplicationException
+from ttypes import *
+from thrift.Thrift import TProcessor
+from thrift.protocol.TBase import TBase, TExceptionBase
+
+
+class Iface(object):
+  def echo(self, input):
+    """
+    Parameters:
+     - input
+    """
+    pass
+
+
+class Client(Iface):
+  def __init__(self, iprot, oprot=None):
+    self._iprot = self._oprot = iprot
+    if oprot is not None:
+      self._oprot = oprot
+    self._seqid = 0
+
+  def echo(self, input):
+    """
+    Parameters:
+     - input
+    """
+    self.send_echo(input)
+    return self.recv_echo()
+
+  def send_echo(self, input):
+    self._oprot.writeMessageBegin('echo', TMessageType.CALL, self._seqid)
+    args = echo_args()
+    args.input = input
+    args.write(self._oprot)
+    self._oprot.writeMessageEnd()
+    self._oprot.trans.flush()
+
+  def recv_echo(self):
+    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
+    if mtype == TMessageType.EXCEPTION:
+      x = TApplicationException()
+      x.read(self._iprot)
+      self._iprot.readMessageEnd()
+      raise x
+    result = echo_result()
+    result.read(self._iprot)
+    self._iprot.readMessageEnd()
+    if result.success is not None:
+      return result.success
+    raise TApplicationException(TApplicationException.MISSING_RESULT, "echo failed: unknown result");
+
+
+class Processor(Iface, TProcessor):
+  def __init__(self, handler):
+    self._handler = handler
+    self._processMap = {}
+    self._processMap["echo"] = Processor.process_echo
+
+  def process(self, iprot, oprot):
+    (name, type, seqid) = iprot.readMessageBegin()
+    if name not in self._processMap:
+      iprot.skip(TType.STRUCT)
+      iprot.readMessageEnd()
+      x = TApplicationException(TApplicationException.UNKNOWN_METHOD, 'Unknown function %s' % (name))
[…]

### 2014-04-29 services/gen-py/services/Filter.py

@@ -1,0 +1,258 @@
+#
+# Autogenerated by Thrift Compiler (0.9.1)
+#
+# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+#
+#  options string: py:utf8strings,dynamic
+#
+
+from thrift.Thrift import TType, TMessageType, TException, TApplicationException
+from ttypes import *
+from thrift.Thrift import TProcessor
+from thrift.protocol.TBase import TBase, TExceptionBase
+
+
+class Iface(object):
+  def ping(self):
+    pass
+
+  def run(self, document):
+    """
+    Parameters:
+     - document
+    """
+    pass
+
+  def shutdown(self):
+    pass
+
+
+class Client(Iface):
+  def __init__(self, iprot, oprot=None):
+    self._iprot = self._oprot = iprot
+    if oprot is not None:
+      self._oprot = oprot
+    self._seqid = 0
+
+  def ping(self):
+    self.send_ping()
+    self.recv_ping()
+
+  def send_ping(self):
+    self._oprot.writeMessageBegin('ping', TMessageType.CALL, self._seqid)
+    args = ping_args()
+    args.write(self._oprot)
+    self._oprot.writeMessageEnd()
+    self._oprot.trans.flush()
+
+  def recv_ping(self):
+    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
+    if mtype == TMessageType.EXCEPTION:
+      x = TApplicationException()
+      x.read(self._iprot)
+      self._iprot.readMessageEnd()
+      raise x
+    result = ping_result()
+    result.read(self._iprot)
+    self._iprot.readMessageEnd()
+    return
+
+  def run(self, document):
+    """
+    Parameters:
+     - document
+    """
+    self.send_run(document)
+    return self.recv_run()
+
+  def send_run(self, document):
+    self._oprot.writeMessageBegin('run', TMessageType.CALL, self._seqid)
+    args = run_args()
+    args.document = document
+    args.write(self._oprot)
+    self._oprot.writeMessageEnd()
+    self._oprot.trans.flush()
+
+  def recv_run(self):
+    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
+    if mtype == TMessageType.EXCEPTION:
+      x = TApplicationException()
+      x.read(self._iprot)
+      self._iprot.readMessageEnd()
+      raise x
+    result = run_result()
+    result.read(self._iprot)
[…]

### 2014-04-29 services/gen-py/services/PDFParser.py

@@ -1,0 +1,250 @@
+#
+# Autogenerated by Thrift Compiler (0.9.1)
+#
+# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+#
+#  options string: py:utf8strings,dynamic
+#
+
+from thrift.Thrift import TType, TMessageType, TException, TApplicationException
+from ttypes import *
+from thrift.Thrift import TProcessor
+from thrift.protocol.TBase import TBase, TExceptionBase
+
+
+class Iface(object):
+  def ping(self):
+    pass
+
+  def parse(self, file):
+    """
+    Parameters:
+     - file
+    """
+    pass
+
+  def shutdown(self):
+    pass
+
+
+class Client(Iface):
+  def __init__(self, iprot, oprot=None):
+    self._iprot = self._oprot = iprot
+    if oprot is not None:
+      self._oprot = oprot
+    self._seqid = 0
+
+  def ping(self):
+    self.send_ping()
+    self.recv_ping()
+
+  def send_ping(self):
+    self._oprot.writeMessageBegin('ping', TMessageType.CALL, self._seqid)
+    args = ping_args()
+    args.write(self._oprot)
+    self._oprot.writeMessageEnd()
+    self._oprot.trans.flush()
+
+  def recv_ping(self):
+    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
+    if mtype == TMessageType.EXCEPTION:
+      x = TApplicationException()
+      x.read(self._iprot)
+      self._iprot.readMessageEnd()
+      raise x
+    result = ping_result()
+    result.read(self._iprot)
+    self._iprot.readMessageEnd()
+    return
+
+  def parse(self, file):
+    """
+    Parameters:
+     - file
+    """
+    self.send_parse(file)
+    return self.recv_parse()
+
+  def send_parse(self, file):
+    self._oprot.writeMessageBegin('parse', TMessageType.CALL, self._seqid)
+    args = parse_args()
+    args.file = file
+    args.write(self._oprot)
+    self._oprot.writeMessageEnd()
+    self._oprot.trans.flush()
+
+  def recv_parse(self):
+    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
+    if mtype == TMessageType.EXCEPTION:
+      x = TApplicationException()
+      x.read(self._iprot)
+      self._iprot.readMessageEnd()
+      raise x
+    result = parse_result()
+    result.read(self._iprot)
[…]

### 2014-04-29 services/gen-py/services/__init__.py

@@ -1,0 +1,1 @@
+__all__ = ['ttypes', 'constants', 'PDFParser', 'Filter', 'Echo']

### 2014-04-29 services/gen-py/services/ttypes.py

@@ -1,0 +1,49 @@
+#
+# Autogenerated by Thrift Compiler (0.9.1)
+#
+# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+#
+#  options string: py:utf8strings,dynamic
+#
+
+from thrift.Thrift import TType, TMessageType, TException, TApplicationException
+import structs.ttypes
+
+
+from thrift.protocol.TBase import TBase, TExceptionBase
+
+
+
+class ProcessException(TExceptionBase):
+  """
+  Attributes:
+   - timestamp
+   - what
+   - why
+  """
+
+  thrift_spec = (
+    None, # 0
+    (1, TType.I32, 'timestamp', None, None, ), # 1
+    (2, TType.STRING, 'what', None, None, ), # 2
+    (3, TType.STRING, 'why', None, None, ), # 3
+  )
+
+  def __init__(self, timestamp=None, what=None, why=None,):
+    self.timestamp = timestamp
+    self.what = what
+    self.why = why
+
+  def __str__(self):
+    return repr(self)
+
+  def __repr__(self):
+    L = ['%s=%r' % (key, value)
+      for key, value in self.__dict__.iteritems()]
+    return '%s(%s)' % (self.__class__.__name__, ', '.join(L))
+
+  def __eq__(self, other):
+    return isinstance(other, self.__class__) and self.__dict__ == other.__dict__
+
+  def __ne__(self, other):
+    return not (self == other)

### 2014-04-29 services/gen-py/structs/constants.py

@@ -1,0 +1,11 @@
+#
+# Autogenerated by Thrift Compiler (0.9.1)
+#
+# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+#
+#  options string: py:utf8strings,dynamic
+#
+
+from thrift.Thrift import TType, TMessageType, TException, TApplicationException
+from ttypes import *
+

### 2014-04-29 services/gen-py/structs/ttypes.py

@@ -1,0 +1,224 @@
+#
+# Autogenerated by Thrift Compiler (0.9.1)
+#
+# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
+#
+#  options string: py:utf8strings,dynamic
+#
+
+from thrift.Thrift import TType, TMessageType, TException, TApplicationException
+
+from thrift.protocol.TBase import TBase, TExceptionBase
+
+
+
+class Interval(TBase):
+  """
+  Attributes:
+   - upper
+   - lower
+  """
+
+  thrift_spec = (
+    None, # 0
+    (1, TType.I32, 'upper', None, None, ), # 1
+    (2, TType.I32, 'lower', None, None, ), # 2
+  )
+
+  def __init__(self, upper=None, lower=None,):
+    self.upper = upper
+    self.lower = lower
+
+  def __repr__(self):
+    L = ['%s=%r' % (key, value)
+      for key, value in self.__dict__.iteritems()]
+    return '%s(%s)' % (self.__class__.__name__, ', '.join(L))
+
+  def __eq__(self, other):
+    return isinstance(other, self.__class__) and self.__dict__ == other.__dict__
+
+  def __ne__(self, other):
+    return not (self == other)
+
+class TextNode(TBase):
+  """
+  Attributes:
+   - pageIndex
+   - interval
+  """
+
+  thrift_spec = (
+    None, # 0
+    (1, TType.I32, 'pageIndex', None, None, ), # 1
+    (2, TType.STRUCT, 'interval', (Interval, Interval.thrift_spec), None, ), # 2
+  )
+
+  def __init__(self, pageIndex=None, interval=None,):
+    self.pageIndex = pageIndex
+    self.interval = interval
+
+  def __repr__(self):
+    L = ['%s=%r' % (key, value)
+      for key, value in self.__dict__.iteritems()]
+    return '%s(%s)' % (self.__class__.__name__, ', '.join(L))
+
+  def __eq__(self, other):
+    return isinstance(other, self.__class__) and self.__dict__ == other.__dict__
+
+  def __ne__(self, other):
+    return not (self == other)
+
+class MetaReference(TBase):
+  """
+  Attributes:
+   - field
+   - idx
+  """
+
+  thrift_spec = (
+    None, # 0
+    (1, TType.STRING, 'field', None, None, ), # 1
+    (2, TType.I32, 'idx', None, None, ), # 2
+  )
+
+  def __init__(self, field=None, idx=None,):
[…]

### 2014-04-29 services/gen-java/spa/services/services/Echo.java
Remove Echo service

@@ -1,972 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.services;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class Echo {
-
-  public interface Iface {
-
-    public String echo(String input) throws org.apache.thrift.TException;
-
-  }
-
-  public interface AsyncIface {
-
-    public void echo(String input, org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
-
-  }
-
-  public static class Client extends org.apache.thrift.TServiceClient implements Iface {
-    public static class Factory implements org.apache.thrift.TServiceClientFactory<Client> {
-      public Factory() {}
-      public Client getClient(org.apache.thrift.protocol.TProtocol prot) {
-        return new Client(prot);
-      }
-      public Client getClient(org.apache.thrift.protocol.TProtocol iprot, org.apache.thrift.protocol.TProtocol oprot) {
-        return new Client(iprot, oprot);
-      }
-    }
-
-    public Client(org.apache.thrift.protocol.TProtocol prot)
-    {
-      super(prot, prot);
-    }
-
[…]

### 2014-04-29 services/gen-py/services/Echo.py

@@ -1,144 +1,0 @@
-#
-# Autogenerated by Thrift Compiler (0.9.1)
-#
-# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
-#
-#  options string: py:utf8strings,dynamic
-#
-
-from thrift.Thrift import TType, TMessageType, TException, TApplicationException
-from ttypes import *
-from thrift.Thrift import TProcessor
-from thrift.protocol.TBase import TBase, TExceptionBase
-
-
-class Iface(object):
-  def echo(self, input):
-    """
-    Parameters:
-     - input
-    """
-    pass
-
-
-class Client(Iface):
-  def __init__(self, iprot, oprot=None):
-    self._iprot = self._oprot = iprot
-    if oprot is not None:
-      self._oprot = oprot
-    self._seqid = 0
-
-  def echo(self, input):
-    """
-    Parameters:
-     - input
-    """
-    self.send_echo(input)
-    return self.recv_echo()
-
-  def send_echo(self, input):
-    self._oprot.writeMessageBegin('echo', TMessageType.CALL, self._seqid)
-    args = echo_args()
-    args.input = input
-    args.write(self._oprot)
-    self._oprot.writeMessageEnd()
-    self._oprot.trans.flush()
-
-  def recv_echo(self):
-    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
-    if mtype == TMessageType.EXCEPTION:
-      x = TApplicationException()
-      x.read(self._iprot)
-      self._iprot.readMessageEnd()
-      raise x
-    result = echo_result()
-    result.read(self._iprot)
-    self._iprot.readMessageEnd()
-    if result.success is not None:
-      return result.success
-    raise TApplicationException(TApplicationException.MISSING_RESULT, "echo failed: unknown result");
-
-
-class Processor(Iface, TProcessor):
-  def __init__(self, handler):
-    self._handler = handler
-    self._processMap = {}
-    self._processMap["echo"] = Processor.process_echo
-
-  def process(self, iprot, oprot):
-    (name, type, seqid) = iprot.readMessageBegin()
-    if name not in self._processMap:
-      iprot.skip(TType.STRUCT)
-      iprot.readMessageEnd()
-      x = TApplicationException(TApplicationException.UNKNOWN_METHOD, 'Unknown function %s' % (name))
[…]

### 2014-04-29 services/gen-py/services/__init__.py

@@ -1,1 +1,1 @@
-__all__ = ['ttypes', 'constants', 'PDFParser', 'Filter', 'Echo']
+__all__ = ['ttypes', 'constants', 'PDFParser', 'Filter']

### 2014-04-29 services/gen-java/spa/services/structs/Annotation.java
Clojure does not accept underscores in fields

@@ -38,7 +38,7 @@ public class Annotation implements org.apache.thrift.TBase<Annotation, Annotatio
 
   private static final org.apache.thrift.protocol.TField UUID_FIELD_DESC = new org.apache.thrift.protocol.TField("uuid", org.apache.thrift.protocol.TType.STRING, (short)1);
   private static final org.apache.thrift.protocol.TField LABEL_FIELD_DESC = new org.apache.thrift.protocol.TField("label", org.apache.thrift.protocol.TType.I32, (short)2);
-  private static final org.apache.thrift.protocol.TField __META_FIELD_DESC = new org.apache.thrift.protocol.TField("__meta", org.apache.thrift.protocol.TType.STRUCT, (short)3);
+  private static final org.apache.thrift.protocol.TField META_FIELD_DESC = new org.apache.thrift.protocol.TField("meta", org.apache.thrift.protocol.TType.STRUCT, (short)3);
 
   private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
   static {
@@ -48,13 +48,13 @@ public class Annotation implements org.apache.thrift.TBase<Annotation, Annotatio
 
   public String uuid; // required
   public int label; // required
-  public MetaReference __meta; // required
+  public MetaReference meta; // required
 
   /** The set of fields this struct contains, along with convenience methods for finding and manipulating them. */
   public enum _Fields implements org.apache.thrift.TFieldIdEnum {
     UUID((short)1, "uuid"),
     LABEL((short)2, "label"),
-    __META((short)3, "__meta");
+    META((short)3, "meta");
 
     private static final Map<String, _Fields> byName = new HashMap<String, _Fields>();
 
@@ -73,8 +73,8 @@ public class Annotation implements org.apache.thrift.TBase<Annotation, Annotatio
           return UUID;
         case 2: // LABEL
           return LABEL;
-        case 3: // __META
-          return __META;
+        case 3: // META
+          return META;
         default:
           return null;
       }
@@ -124,7 +124,7 @@ public class Annotation implements org.apache.thrift.TBase<Annotation, Annotatio
         new org.apache.thrift.meta_data.FieldValueMetaData(org.apache.thrift.protocol.TType.STRING)));
[…]

### 2014-04-29 services/gen-java/spa/services/structs/Document.java

@@ -38,8 +38,8 @@ public class Document implements org.apache.thrift.TBase<Document, Document._Fie
 
   private static final org.apache.thrift.protocol.TField TEXT_FIELD_DESC = new org.apache.thrift.protocol.TField("text", org.apache.thrift.protocol.TType.STRING, (short)1);
   private static final org.apache.thrift.protocol.TField MARGINALIA_FIELD_DESC = new org.apache.thrift.protocol.TField("marginalia", org.apache.thrift.protocol.TType.LIST, (short)2);
-  private static final org.apache.thrift.protocol.TField __META_FIELD_DESC = new org.apache.thrift.protocol.TField("__meta", org.apache.thrift.protocol.TType.MAP, (short)3);
-  private static final org.apache.thrift.protocol.TField __TEXT_NODES_FIELD_DESC = new org.apache.thrift.protocol.TField("__textNodes", org.apache.thrift.protocol.TType.LIST, (short)4);
+  private static final org.apache.thrift.protocol.TField META_FIELD_DESC = new org.apache.thrift.protocol.TField("meta", org.apache.thrift.protocol.TType.MAP, (short)3);
+  private static final org.apache.thrift.protocol.TField TEXT_NODES_FIELD_DESC = new org.apache.thrift.protocol.TField("textNodes", org.apache.thrift.protocol.TType.LIST, (short)4);
 
   private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
   static {
@@ -49,15 +49,15 @@ public class Document implements org.apache.thrift.TBase<Document, Document._Fie
 
   public String text; // required
   public List<Marginalis> marginalia; // optional
-  public Map<String,Mapping> __meta; // optional
-  public List<TextNode> __textNodes; // optional
+  public Map<String,Mapping> meta; // optional
+  public List<TextNode> textNodes; // optional
 
   /** The set of fields this struct contains, along with convenience methods for finding and manipulating them. */
   public enum _Fields implements org.apache.thrift.TFieldIdEnum {
     TEXT((short)1, "text"),
     MARGINALIA((short)2, "marginalia"),
-    __META((short)3, "__meta"),
-    __TEXT_NODES((short)4, "__textNodes");
+    META((short)3, "meta"),
+    TEXT_NODES((short)4, "textNodes");
 
     private static final Map<String, _Fields> byName = new HashMap<String, _Fields>();
 
[…]

### 2014-04-29 services/gen-py/structs/ttypes.py

@@ -101,20 +101,20 @@ class Annotation(TBase):
   Attributes:
    - uuid
    - label
-   - __meta
+   - meta
   """
 
   thrift_spec = (
     None, # 0
     (1, TType.STRING, 'uuid', None, None, ), # 1
     (2, TType.I32, 'label', None, None, ), # 2
-    (3, TType.STRUCT, '__meta', (MetaReference, MetaReference.thrift_spec), None, ), # 3
+    (3, TType.STRUCT, 'meta', (MetaReference, MetaReference.thrift_spec), None, ), # 3
   )
 
-  def __init__(self, uuid=None, label=None, __meta=None,):
+  def __init__(self, uuid=None, label=None, meta=None,):
     self.uuid = uuid
     self.label = label
-    self.__meta = __meta
+    self.meta = meta
 
   def __repr__(self):
     L = ['%s=%r' % (key, value)
@@ -194,23 +194,23 @@ class Document(TBase):
   Attributes:
    - text
    - marginalia
-   - __meta
-   - __textNodes
+   - meta
+   - textNodes
   """
 
   thrift_spec = (
     None, # 0
     (1, TType.STRING, 'text', None, None, ), # 1
     (2, TType.LIST, 'marginalia', (TType.STRUCT,(Marginalis, Marginalis.thrift_spec)), None, ), # 2
-    (3, TType.MAP, '__meta', (TType.STRING,None,TType.STRUCT,(Mapping, Mapping.thrift_spec)), None, ), # 3
-    (4, TType.LIST, '__textNodes', (TType.STRUCT,(TextNode, TextNode.thrift_spec)), None, ), # 4
+    (3, TType.MAP, 'meta', (TType.STRING,None,TType.STRUCT,(Mapping, Mapping.thrift_spec)), None, ), # 3
+    (4, TType.LIST, 'textNodes', (TType.STRUCT,(TextNode, TextNode.thrift_spec)), None, ), # 4
   )
 
-  def __init__(self, text=None, marginalia=None, __meta=None, __textNodes=None,):
+  def __init__(self, text=None, marginalia=None, meta=None, textNodes=None,):
     self.text = text
     self.marginalia = marginalia
-    self.__meta = __meta
-    self.__textNodes = __textNodes
+    self.meta = meta
+    self.textNodes = textNodes
 
   def __repr__(self):
     L = ['%s=%r' % (key, value)

### 2014-04-30 services/FilterServer.py
Minor fixes to Python wrapper

@@ -9,7 +9,8 @@ from thrift.protocol import TBinaryProtocol
 from thrift.server import TServer
 
 DEBUG_MODE = True
-logging.basicConfig(level=(logging.DEBUG if DEBUG_MODE else logging.INFO), format='[%(levelname)s] %(name)s %(asctime)s: %(message)s')
+LOG_LEVEL = (logging.DEBUG if DEBUG_MODE else logging.INFO)
+logging.basicConfig(level=LOG_LEVEL, format='[%(levelname)s] %(name)s %(asctime)s: %(message)s')
 log = logging.getLogger(__name__)
 
 class FilterHandler:
@@ -26,6 +27,6 @@ transport = TSocket.TServerSocket(port=9090)
 tfactory = TTransport.TBufferedTransportFactory()
 pfactory = TBinaryProtocol.TBinaryProtocolFactory()
 
-server = TServer.TSimpleServer(processor, transport, tfactory, pfactory)
+server = TServer.TThreadPoolServer(processor, transport, tfactory, pfactory)
 
 server.serve()

### 2014-04-30 documentation/paper.tex
Merge documentation from tx_branch

@@
 \acrodef{ebm}[EBM]{Evidence-based Medicine}
+% I don't think thi sneeds to be capitalized -- bcw
 \acrodef{ml}[ML]{machine learning}
@@
 
-%%% BCW -- I t
+%%% BCW --
 
@@
 
-Summarizing the evidence about medical interventions is an immense undertaking, in part because unstructured \ac{pdf} documents remain the main vehicle for disseminating the results of clinical trials.
+Summarizing the evidence about medical interventions is an immense undertaking, in part because unstructured \ac{pdf} documents remain the main vehicle for disseminating scientific findings.
 Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf} to be published in \emph{systematic reviews}.
-We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying and which is cognate with the present English word “spy,” continuing Proto-Germanic *spah- and the Proto-Indo-European root *(s)pe\`{k} (to see, to observe)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \acl{ml}.
+We introduce Spá,\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}} a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \ac{ml}.
 To illustrate its functionalility, here we use Spá to semi-automate the assessment of bias in clinical trials.
-Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low or high risk of various biases), and annotate sentences that support these classifications.
-Spá has a modular architecture and new models may be trivially added, therefore the tool may be widely useful in other domains with a \ac{pdf}-based literature, including law, physics, and biology.
+%Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low or high risk of various biases), and annotate sentences that support these classifications.
+Spá has a modular architecture, therefore the tool may be widely useful in other domains with a \ac{pdf}-based literature, including law, physics, and biology.
 
@@
 
-Imposing structure on full-text documents (e.g., identifying specific sentences of interest) is an important and practical task in natural language processing and machine learning, because doing so manually is laborious and costly.
+Imposing structure on full-text documents is an important and practical task in natural language processing and machine learning.
 \emph{Systematic reviews} are an instructive example.
-Such reviews aim to answer clinical questions by exhaustively identifying and extracting information from all published relevant studies.
+Such reviews aim to answer clinical questions by providing an exhaustive synthesis (textual and statistical) of the current evidence in all published literature.
 They are fundamental tools in \ac{ebm} \cite{sackett1996}.
-The end product of a systematic review is an exhaustive textual and statistical synthesis of the current evidence.
-To produce these, reviewers must manually extract data on trial design and conduct, intervention effectiveness, adverse effects, and potential biases from the free-text of published studies.
-These extraction tasks can be semi-automated using machine learning approaches.
-As an example, here we consider the risk of bias assessment, in which reviewers assess, e.g., whether study participants and personnel were properly blinded.
+To produce these reviews data, like potential biases, must be manually extracted from the literature.
+These extraction tasks are extremely labourous, but could potentially be (semi-)automated using machine learning approaches.
 
-Assessing this is a time-consuming task.
+As an example, we consider the risk of bias assessment, in which reviewers assess, e.g., whether study participants and personnel were properly blinded.
+Assessing risk of bias is a time-consuming task.
 A single trial may typically take a domain expert ten minutes \cite{Hartling2011}, and a single review may typically include several dozen trials.
-Making matters worse, due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus \cite{Hartling2009}.
+Making matters worse, due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus.\cite{Hartling2009}
 
-Machine learning methods provide the machinery to automate such extractions; as they can effectively impose structure onto \acp{pdf}.
-
+Machine learning methods could provide the machinery to automate such extractions; as they can effectively impose the desired structure onto \acp{pdf}.
 But if such technologies are to be practically useful, we need tools that visualize these model predictions and annotations.
@@
 
-Spá is an open-source, web-based tool that can incorporate state-of-the-art machine learning to automatically annotate \ac{pdf} articles.
+Spá is an open-source, web-based tool that can incorporate machine learning to automatically annotate \ac{pdf} articles.
 As a practical demonstration of this technology, we have built a machine learning system that automatically annotates \acp{pdf} to aid \ac{ebm}.
-% maybe?
-Specifically, this system leverages a multi-task model that simulteanously assesses the risk of biases across several domains.
-This tool is unique in that it leverages state-of-the-art \acl{ml} models applied to full-text articles to assist practitioners of \ac{ebm}.
+This tool is unique in that it leverages state-of-the-art \ac{ml} models applied to full-text articles to assist practitioners of \ac{ebm}.
 
@@
 \subsection{Machine Learning Approaches}
-
-We briefly describe our model for assessing the study risk of bias (and supporting sentences) across the following domains: random sequence generation, allocation concealment, blinding of participants and personnel, blinding of outcome assessment, incomplete outcome data and selective reporting.
-To train our model, we have leveraged the \ac{cdsr} in lieu of manually annotated data, which would be expensive to collect.
+To automatically assess the study risk of bias, we have leveraged the \ac{cdsr} in lieu of manually annotated data, which would be expensive to collect.
 The \ac{cdsr} contains descriptions and data about clinical trials reported in existing systematic reviews.
-Briefly, we match (the full-texts of) studies to entries in the \ac{cdsr}, which contains risk of bias assessments; this provides document level labels.
-The \ac{cdsr} also contains sentences that annotators indicated as supporting their assessments.
+We match the full-texts of studies to entries in the \ac{cdsr}, which contains risk of bias assessment; providing  document level labels.
+The \ac{cdsr} also contains quotations that reviewers indicated as supporting their assessments.
 We match these strings to substrings in the \acp{pdf} to provide sentence-level supervision.
-This can thus be viewed as a \emph{distantly supervised} \cite{mintz-09,nguyen-11} approach.
+This can be viewed as a \emph{distantly supervised} \cite{mintz-09,nguyen-11} approach.
 
@@
 We accomplish this by way of a feature space construction that includes both shared and domain-specific terms (similar to the domain adaptation approach in \cite{daume2007}).
-Furthermore, we take a unified approach to the two tasks by \emph{jointly} assessing the risk of bias associated with a given article \emph{and} extracting the sentences that support this judgment.
+%Furthermore, we take a unified approach to the two tasks by \emph{jointly} assessing the risk of bias associated with a given article \emph{and} extracting the sentences that support this judgment.
 Specifically, we first make sentence level predictions (using one set of trained models), and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier (further details specified in \cite{marshall2014}).
-Figure \ref{fig:screenshot} shows example system output: in this case the overall risk of bias with respect to random sequence generation is judged to be low, and the supporting sentence for this judgement is highlighted in green.
+Figure \ref{fig:screenshot} shows the system in use.
 %More specifically, the database we leverage contains structured and semi-structured data for each systematic review.
@@
 
-%\vspace{-2em}
 \section{Spá Architecture Overview}
+
+\label{section:architecture}
+\begin{wrapfigure}{}{0.5\textwidth}
+  \vspace{-1em}
+  \includegraphics[width=0.48\textwidth]{./diagrams/sequence.pdf}
+  \caption{\label{fig:sequence}Sequence diagram of a typical request-response in Spá.}
+  \vspace{-1em}
+\end{wrapfigure}
+
 Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
@@
 
-For each of the annotations the relevant text nodes in the document are highlighted.
+For each of the annotations the relevant nodes in the document are highlighted.
 A custom scrollbar\footnote{inspired by \href{http://substance.io/}{substance.io}} that acts as a `mini-map' is projected to show where annotations reside within the document.
 The user can interactively activate and inspect specific results.
-\label{section:architecture}
-\begin{wrapfigure}{R}{0.5\textwidth}
-  \begin{center}
-    \includegraphics[width=0.48\textwidth]{./diagrams/sequence.pdf}
-  \end{center}
-  \caption{\label{fig:sequence}Sequence diagram of a typical request-response in Spá.}
-\end{wrapfigure}
 
 \section{Future work}
-We have presented a web-based tool for visualization of annotations and summarizations for \ac{pdf} documents.
-It allows users to see the results from machine learning predictions for a specific document.
-We have demonstrated the use of this system within the context of \ac{ebm} by automatically extracting potential risks of bias (and supporting sentences) via state-of-the-art \ac{ml} methods.
+We have presented a web-based tool for visualization of annotations and marginalia for \ac{pdf} documents.
+Furthermore, we have demonstrated the use of this system within the context of \ac{ebm} by automatically extracting potential risks of bias.
 
-More generally, we believe the tool to be potentially useful for a much wider range of text mining and machine learning applications.
-To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new \ac{ml} systems for automated \ac{pdf} annotation.
+More generally, we believe the tool to be potentially useful for a much wider range of text mining and \acl{ml} applications.
+To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated \ac{pdf} annotation.
 Furthermore, we are working to allow users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
@@
 \bibliographystyle{splncs}
+
 \bibliography{references}

### 2014-04-30 doc/paper.tex

--- 2014-04-30 documentation/paper.tex
@@
 We match these strings to substrings in the \acp{pdf} to provide sentence-level supervision.
-This can be viewed as a \emph{distantly supervised} \cite{mintz-09,nguyen-11} approach.
+This can be viewed as a \emph{distantly supervised} \cite{mintz-09} approach.
 

### 2014-04-30 documentation/paper.tex
Minor documentation fixes

@@
 Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf} to be published in \emph{systematic reviews}.
-We introduce Spá,\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}} a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \ac{ml}.
+We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \ac{ml}.
 To illustrate its functionalility, here we use Spá to semi-automate the assessment of bias in clinical trials.
@@
 A single trial may typically take a domain expert ten minutes \cite{Hartling2011}, and a single review may typically include several dozen trials.
-Making matters worse, due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus.\cite{Hartling2009}
+Making matters worse, due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus \cite{Hartling2009}.
 
@@
 (2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
-These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}.
+%These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}.
 
@@
 From a \ac{ml} vantage, we have two tasks for a given article: (1) predict the overall risk of bias for each of the domains of interest, and (2) extract the sentences that support these assessments.
-For both tasks we leverage standard bag-of-words text encoding and linear-kernel \acp{svm}.
+For both tasks we leverage standard bag-of-words text encoding and linear-kernel \aclp{svm}.
 Because the risk of bias predictions are correlated (across domains), we take a \emph{multi-task} \cite{evgeniou2004} approach to classification and jointly learn a model for the domains.
-We accomplish this by way of a feature space construction that includes both shared and domain-specific terms (similar to the domain adaptation approach in \cite{daume2007}).
+We accomplish this by way of a feature space construction that includes both shared and domain-specific terms, similar to the domain adaptation approach in \cite{daume2007}.
 %Furthermore, we take a unified approach to the two tasks by \emph{jointly} assessing the risk of bias associated with a given article \emph{and} extracting the sentences that support this judgment.
-Specifically, we first make sentence level predictions (using one set of trained models), and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier (further details specified in \cite{marshall2014}).
+Specifically, we first make sentence level prediction, and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier (further details specified in \cite{marshall2014}).
 Figure \ref{fig:screenshot} shows the system in use.
@@
 We have presented a web-based tool for visualization of annotations and marginalia for \ac{pdf} documents.
-Furthermore, we have demonstrated the use of this system within the context of \ac{ebm} by automatically extracting potential risks of bias.
+Furthermore, we have demonstrated the use of this system within the context of \acl{ebm} by automatically extracting potential risks of bias.
 

### 2014-05-01 documentation/paper.tex
Squeeze some extra space out of the paper

@@
 Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf} to be published in \emph{systematic reviews}.
-We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \ac{ml}.
-To illustrate its functionalility, here we use Spá to semi-automate the assessment of bias in clinical trials.
+We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{Kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \ac{ml}.
+To illustrate its functionalility, we use Spá to semi-automate the assessment of bias in clinical trials.
 %Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low or high risk of various biases), and annotate sentences that support these classifications.
@@
 \emph{Systematic reviews} are an instructive example.
-Such reviews aim to answer clinical questions by providing an exhaustive synthesis (textual and statistical) of the current evidence in all published literature.
-They are fundamental tools in \ac{ebm} \cite{sackett1996}.
-To produce these reviews data, like potential biases, must be manually extracted from the literature.
+Such reviews aim to answer clinical questions by providing an exhaustive synthesis of all the current evidence in published literature.
+They are fundamental tools in \ac{ebm} \cite{Sackett1996,Valkenhoef2012}.
+To produce these reviews data must be manually extracted from the literature.
 These extraction tasks are extremely labourous, but could potentially be (semi-)automated using machine learning approaches.
 
-As an example, we consider the risk of bias assessment, in which reviewers assess, e.g., whether study participants and personnel were properly blinded.
+As an example we consider risk of bias assessment, here reviewers assess, e.g., whether study participants and personnel were properly blinded \cite{Higgins2011}.
 Assessing risk of bias is a time-consuming task.
@@
 \begin{figure}[htb]
-\vspace{-1em}
+\vspace{-2em}
 \centering
@@
 Here the risk of bias is assessed to be low, for example, and one of the supporting sentences for this assessment describes the randomization procedure (highlighted in green).}
-\vspace{-1em}
+\vspace{-1.5em}
 \end{figure}
@@
 We match these strings to substrings in the \acp{pdf} to provide sentence-level supervision.
-This can be viewed as a \emph{distantly supervised} \cite{mintz-09,nguyen-11} approach.
+This can be viewed as a \emph{distantly supervised} \cite{Mintz09,Nguyen11} approach.
 
@@
 %%%
-From a \ac{ml} vantage, we have two tasks for a given article: (1) predict the overall risk of bias for each of the domains of interest, and (2) extract the sentences that support these assessments.
+From a \ac{ml} vantage, we have two tasks for a given article: (1) predict the overall risk of bias for each of the domains, and (2) extract the sentences that support these assessments.
 For both tasks we leverage standard bag-of-words text encoding and linear-kernel \aclp{svm}.
-Because the risk of bias predictions are correlated (across domains), we take a \emph{multi-task} \cite{evgeniou2004} approach to classification and jointly learn a model for the domains.
-We accomplish this by way of a feature space construction that includes both shared and domain-specific terms, similar to the domain adaptation approach in \cite{daume2007}.
+Because the risk of bias predictions are correlated across domains, we take a \emph{multi-task} \cite{Evgeniou2004} approach to classification and jointly learn a model for the domains.
+We accomplish this by way of a feature space construction that includes both shared and domain-specific terms, similar to the domain adaptation approach in \cite{Daume2007}.
 %Furthermore, we take a unified approach to the two tasks by \emph{jointly} assessing the risk of bias associated with a given article \emph{and} extracting the sentences that support this judgment.
-Specifically, we first make sentence level prediction, and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier (further details specified in \cite{marshall2014}).
+Specifically, we first make sentence level prediction, and then insert features representing the tokens in the predicted sentences for exploitation by the document level classifier (see for details \cite{Marshall2014}).
 Figure \ref{fig:screenshot} shows the system in use.
@@
 \begin{wrapfigure}{}{0.5\textwidth}
+  \vspace{-2em}
+  \includegraphics[width=0.48\textwidth]{./diagrams/sequence.pdf}
   \vspace{-1em}
-  \includegraphics[width=0.48\textwidth]{./diagrams/sequence.pdf}
   \caption{\label{fig:sequence}Sequence diagram of a typical request-response in Spá.}
-  \vspace{-1em}
+  \vspace{-1.5em}
 \end{wrapfigure}
@@
 For each of the annotations the relevant nodes in the document are highlighted.
-A custom scrollbar\footnote{inspired by \href{http://substance.io/}{substance.io}} that acts as a `mini-map' is projected to show where annotations reside within the document.
+A custom scrollbar, inspired by \href{http://substance.io/}{substance.io} that acts as a `mini-map' is projected to show where annotations reside within the document.
 The user can interactively activate and inspect specific results.
@@
 
-More generally, we believe the tool to be potentially useful for a much wider range of text mining and \acl{ml} applications.
+More generally, we believe the tool to be potentially useful for a much wider range of \acl{ml} applications.
 To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated \ac{pdf} annotation.
 Furthermore, we are working to allow users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
-The vision is to have an extensible system for semi-automated (machine assisted) screening, data extraction and data summarization for EBM, and to allow rapid development of similar systems for other domains.
+The vision is to have an extensible system for machine assisted data extraction and data summarization.
 
@@
 \bibliographystyle{splncs}
-
 \bibliography{references}
-
 \end{document}

### 2014-05-01 documentation/paper.tex
Address some comments on the paper

@@
 \usepackage{graphicx}
+\usepackage[english]{babel}
 \usepackage{float}
@@
 Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf} to be published in \emph{systematic reviews}.
-We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{Kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \ac{ml}.
-To illustrate its functionalility, we use Spá to semi-automate the assessment of bias in clinical trials.
+We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{Kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \acl{ml}.
+To illustrate its functionality, we use Spá to semi-automate the assessment of bias in clinical trials.
 %Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low or high risk of various biases), and annotate sentences that support these classifications.
@@
 They are fundamental tools in \ac{ebm} \cite{Sackett1996,Valkenhoef2012}.
-To produce these reviews data must be manually extracted from the literature.
-These extraction tasks are extremely labourous, but could potentially be (semi-)automated using machine learning approaches.
+Data must be manually extracted from the literature to produce the systematic reviews.
+These extraction tasks are extremely laborious, but could potentially be assisted by machine learning approaches.
 
-As an example we consider risk of bias assessment, here reviewers assess, e.g., whether study participants and personnel were properly blinded \cite{Higgins2011}.
+As an example we consider risk of bias assessment.
+Here reviewers assess, e.g., whether study participants and personnel were properly blinded \cite{Higgins2011}.
 Assessing risk of bias is a time-consuming task.
@@
 
-While our application of interest is \ac{ebm}, we emphasize that the visualization tool can be used for any domain in which one wants to annotate \acp{pdf}.
+While our application of interest is \ac{ebm}, we emphasize that the visualization tool can be used for any domain in which one wants to annotate \acp{pdf}, e.g.
+genome-wide association studies or jurisprudence.
 Thus the contribution of this work is two-fold, as we present:
@@
 
-\section{Automating \acl{ebm}}
+\section{Case study: Risk of Bias in \acl{ebm}}
 \label{section:EBM-ML}
@@
 For each of the annotations the relevant nodes in the document are highlighted.
-A custom scrollbar, inspired by \href{http://substance.io/}{substance.io} that acts as a `mini-map' is projected to show where annotations reside within the document.
+A custom scrollbar, inspired by \href{http://substance.io/}{substance.io}, that acts as a `mini-map' is projected to show where annotations reside within the document.
 The user can interactively activate and inspect specific results.
@@
 
-More generally, we believe the tool to be potentially useful for a much wider range of \acl{ml} applications.
-To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated \ac{pdf} annotation.
-Furthermore, we are working to allow users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
-The vision is to have an extensible system for machine assisted data extraction and data summarization.
+We believe the tool to be potentially useful for a much wider range of \acl{ml} applications.
+Currently we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated \ac{pdf} annotation.
+Furthermore, we are working to allow users to persist annotations and marginalia, possibly embedded within the document itself, for sharing and off-line use.
+The vision is to have an extensible system for machine assisted data extraction that will greatly increase both the quality and the reproducibility (i.e. data provenance) of current \acl{ebm}.
 

### 2014-05-05 services/FilterServer.py
Remove Apache Thrift
Switching to ZeroMQ + JSON (or protobuf)

@@ -1,32 +1,0 @@
-import sys, logging
-sys.path.append('gen-py')
-
-from services import Filter
-
-from thrift.transport import TSocket
-from thrift.transport import TTransport
-from thrift.protocol import TBinaryProtocol
-from thrift.server import TServer
-
-DEBUG_MODE = True
-LOG_LEVEL = (logging.DEBUG if DEBUG_MODE else logging.INFO)
-logging.basicConfig(level=LOG_LEVEL, format='[%(levelname)s] %(name)s %(asctime)s: %(message)s')
-log = logging.getLogger(__name__)
-
-class FilterHandler:
-    def __init__(self):
-        log.info("Started server")
-
-    def ping(self):
-        log.info("PONG")
-
-
-handler = FilterHandler()
-processor = Filter.Processor(handler)
-transport = TSocket.TServerSocket(port=9090)
-tfactory = TTransport.TBufferedTransportFactory()
-pfactory = TBinaryProtocol.TBinaryProtocolFactory()
-
-server = TServer.TThreadPoolServer(processor, transport, tfactory, pfactory)
-
-server.serve()

### 2014-05-05 services/gen-java/spa/services/services/Filter.java

@@ -1,2062 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.services;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class Filter {
-
-  public interface Iface {
-
-    public void ping() throws org.apache.thrift.TException;
-
-    public spa.services.structs.Document run(spa.services.structs.Document document) throws ProcessException, org.apache.thrift.TException;
-
-    public void shutdown() throws org.apache.thrift.TException;
-
-  }
-
-  public interface AsyncIface {
-
-    public void ping(org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
-
-    public void run(spa.services.structs.Document document, org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
-
-    public void shutdown(org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
-
-  }
-
-  public static class Client extends org.apache.thrift.TServiceClient implements Iface {
-    public static class Factory implements org.apache.thrift.TServiceClientFactory<Client> {
-      public Factory() {}
-      public Client getClient(org.apache.thrift.protocol.TProtocol prot) {
-        return new Client(prot);
-      }
[…]

### 2014-05-05 services/gen-java/spa/services/services/PDFParser.java

@@ -1,1937 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.services;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class PDFParser {
-
-  public interface Iface {
-
-    public void ping() throws org.apache.thrift.TException;
-
-    public spa.services.structs.Document parse(String file) throws org.apache.thrift.TException;
-
-    public void shutdown() throws org.apache.thrift.TException;
-
-  }
-
-  public interface AsyncIface {
-
-    public void ping(org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
-
-    public void parse(String file, org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
-
-    public void shutdown(org.apache.thrift.async.AsyncMethodCallback resultHandler) throws org.apache.thrift.TException;
-
-  }
-
-  public static class Client extends org.apache.thrift.TServiceClient implements Iface {
-    public static class Factory implements org.apache.thrift.TServiceClientFactory<Client> {
-      public Factory() {}
-      public Client getClient(org.apache.thrift.protocol.TProtocol prot) {
-        return new Client(prot);
[…]

### 2014-05-05 services/gen-java/spa/services/services/ProcessException.java

@@ -1,607 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.services;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class ProcessException extends TException implements org.apache.thrift.TBase<ProcessException, ProcessException._Fields>, java.io.Serializable, Cloneable, Comparable<ProcessException> {
-  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("ProcessException");
-
-  private static final org.apache.thrift.protocol.TField TIMESTAMP_FIELD_DESC = new org.apache.thrift.protocol.TField("timestamp", org.apache.thrift.protocol.TType.I32, (short)1);
-  private static final org.apache.thrift.protocol.TField WHAT_FIELD_DESC = new org.apache.thrift.protocol.TField("what", org.apache.thrift.protocol.TType.STRING, (short)2);
-  private static final org.apache.thrift.protocol.TField WHY_FIELD_DESC = new org.apache.thrift.protocol.TField("why", org.apache.thrift.protocol.TType.STRING, (short)3);
-
-  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
-  static {
[…]

### 2014-05-05 services/gen-java/spa/services/structs/Annotation.java

@@ -1,609 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.structs;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class Annotation implements org.apache.thrift.TBase<Annotation, Annotation._Fields>, java.io.Serializable, Cloneable, Comparable<Annotation> {
-  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Annotation");
-
-  private static final org.apache.thrift.protocol.TField UUID_FIELD_DESC = new org.apache.thrift.protocol.TField("uuid", org.apache.thrift.protocol.TType.STRING, (short)1);
-  private static final org.apache.thrift.protocol.TField LABEL_FIELD_DESC = new org.apache.thrift.protocol.TField("label", org.apache.thrift.protocol.TType.I32, (short)2);
-  private static final org.apache.thrift.protocol.TField META_FIELD_DESC = new org.apache.thrift.protocol.TField("meta", org.apache.thrift.protocol.TType.STRUCT, (short)3);
-
[…]

### 2014-05-05 services/gen-java/spa/services/structs/Document.java

@@ -1,881 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.structs;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class Document implements org.apache.thrift.TBase<Document, Document._Fields>, java.io.Serializable, Cloneable, Comparable<Document> {
-  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Document");
-
-  private static final org.apache.thrift.protocol.TField TEXT_FIELD_DESC = new org.apache.thrift.protocol.TField("text", org.apache.thrift.protocol.TType.STRING, (short)1);
-  private static final org.apache.thrift.protocol.TField TEXT_NODES_FIELD_DESC = new org.apache.thrift.protocol.TField("textNodes", org.apache.thrift.protocol.TType.LIST, (short)2);
-  private static final org.apache.thrift.protocol.TField MARGINALIA_FIELD_DESC = new org.apache.thrift.protocol.TField("marginalia", org.apache.thrift.protocol.TType.LIST, (short)3);
-  private static final org.apache.thrift.protocol.TField META_FIELD_DESC = new org.apache.thrift.protocol.TField("meta", org.apache.thrift.protocol.TType.MAP, (short)4);
-
[…]

### 2014-05-05 services/gen-java/spa/services/structs/Interval.java

@@ -1,484 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.structs;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class Interval implements org.apache.thrift.TBase<Interval, Interval._Fields>, java.io.Serializable, Cloneable, Comparable<Interval> {
-  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Interval");
-
-  private static final org.apache.thrift.protocol.TField UPPER_FIELD_DESC = new org.apache.thrift.protocol.TField("upper", org.apache.thrift.protocol.TType.I32, (short)1);
-  private static final org.apache.thrift.protocol.TField LOWER_FIELD_DESC = new org.apache.thrift.protocol.TField("lower", org.apache.thrift.protocol.TType.I32, (short)2);
-
-  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
-  static {
-    schemes.put(StandardScheme.class, new IntervalStandardSchemeFactory());
-    schemes.put(TupleScheme.class, new IntervalTupleSchemeFactory());
-  }
-
-  public int upper; // required
-  public int lower; // required
-
[…]

### 2014-05-05 services/gen-java/spa/services/structs/Mapping.java

@@ -1,604 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.structs;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class Mapping implements org.apache.thrift.TBase<Mapping, Mapping._Fields>, java.io.Serializable, Cloneable, Comparable<Mapping> {
-  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Mapping");
-
-  private static final org.apache.thrift.protocol.TField TEXT_NODES_FIELD_DESC = new org.apache.thrift.protocol.TField("textNodes", org.apache.thrift.protocol.TType.LIST, (short)1);
-  private static final org.apache.thrift.protocol.TField RANGES_FIELD_DESC = new org.apache.thrift.protocol.TField("ranges", org.apache.thrift.protocol.TType.LIST, (short)2);
-
-  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
-  static {
-    schemes.put(StandardScheme.class, new MappingStandardSchemeFactory());
-    schemes.put(TupleScheme.class, new MappingTupleSchemeFactory());
[…]

### 2014-05-05 services/gen-java/spa/services/structs/Marginalis.java

@@ -1,765 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.structs;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class Marginalis implements org.apache.thrift.TBase<Marginalis, Marginalis._Fields>, java.io.Serializable, Cloneable, Comparable<Marginalis> {
-  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("Marginalis");
-
-  private static final org.apache.thrift.protocol.TField ID_FIELD_DESC = new org.apache.thrift.protocol.TField("id", org.apache.thrift.protocol.TType.STRING, (short)1);
-  private static final org.apache.thrift.protocol.TField TITLE_FIELD_DESC = new org.apache.thrift.protocol.TField("title", org.apache.thrift.protocol.TType.STRING, (short)2);
-  private static final org.apache.thrift.protocol.TField DESCRIPTION_FIELD_DESC = new org.apache.thrift.protocol.TField("description", org.apache.thrift.protocol.TType.STRING, (short)3);
[…]

### 2014-05-05 services/gen-java/spa/services/structs/MetaReference.java

@@ -1,499 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.structs;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class MetaReference implements org.apache.thrift.TBase<MetaReference, MetaReference._Fields>, java.io.Serializable, Cloneable, Comparable<MetaReference> {
-  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("MetaReference");
-
-  private static final org.apache.thrift.protocol.TField FIELD_FIELD_DESC = new org.apache.thrift.protocol.TField("field", org.apache.thrift.protocol.TType.STRING, (short)1);
-  private static final org.apache.thrift.protocol.TField IDX_FIELD_DESC = new org.apache.thrift.protocol.TField("idx", org.apache.thrift.protocol.TType.I32, (short)2);
-
-  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
-  static {
-    schemes.put(StandardScheme.class, new MetaReferenceStandardSchemeFactory());
[…]

### 2014-05-05 services/gen-java/spa/services/structs/TextNode.java

@@ -1,504 +1,0 @@
-/**
- * Autogenerated by Thrift Compiler (0.9.1)
- *
- * DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
- *  @generated
- */
-package spa.services.structs;
-
-import org.apache.commons.lang3.builder.HashCodeBuilder;
-import org.apache.thrift.scheme.IScheme;
-import org.apache.thrift.scheme.SchemeFactory;
-import org.apache.thrift.scheme.StandardScheme;
-
-import org.apache.thrift.scheme.TupleScheme;
-import org.apache.thrift.protocol.TTupleProtocol;
-import org.apache.thrift.protocol.TProtocolException;
-import org.apache.thrift.EncodingUtils;
-import org.apache.thrift.TException;
-import org.apache.thrift.async.AsyncMethodCallback;
-import org.apache.thrift.server.AbstractNonblockingServer.*;
-import java.util.List;
-import java.util.ArrayList;
-import java.util.Map;
-import java.util.HashMap;
-import java.util.EnumMap;
-import java.util.Set;
-import java.util.HashSet;
-import java.util.EnumSet;
-import java.util.Collections;
-import java.util.BitSet;
-import java.nio.ByteBuffer;
-import java.util.Arrays;
-import org.slf4j.Logger;
-import org.slf4j.LoggerFactory;
-
-public class TextNode implements org.apache.thrift.TBase<TextNode, TextNode._Fields>, java.io.Serializable, Cloneable, Comparable<TextNode> {
-  private static final org.apache.thrift.protocol.TStruct STRUCT_DESC = new org.apache.thrift.protocol.TStruct("TextNode");
-
-  private static final org.apache.thrift.protocol.TField PAGE_INDEX_FIELD_DESC = new org.apache.thrift.protocol.TField("pageIndex", org.apache.thrift.protocol.TType.I32, (short)1);
-  private static final org.apache.thrift.protocol.TField INTERVAL_FIELD_DESC = new org.apache.thrift.protocol.TField("interval", org.apache.thrift.protocol.TType.STRUCT, (short)2);
-
-  private static final Map<Class<? extends IScheme>, SchemeFactory> schemes = new HashMap<Class<? extends IScheme>, SchemeFactory>();
-  static {
-    schemes.put(StandardScheme.class, new TextNodeStandardSchemeFactory());
[…]

### 2014-05-05 services/gen-py/services/Filter.py

@@ -1,258 +1,0 @@
-#
-# Autogenerated by Thrift Compiler (0.9.1)
-#
-# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
-#
-#  options string: py:utf8strings,dynamic
-#
-
-from thrift.Thrift import TType, TMessageType, TException, TApplicationException
-from ttypes import *
-from thrift.Thrift import TProcessor
-from thrift.protocol.TBase import TBase, TExceptionBase
-
-
-class Iface(object):
-  def ping(self):
-    pass
-
-  def run(self, document):
-    """
-    Parameters:
-     - document
-    """
-    pass
-
-  def shutdown(self):
-    pass
-
-
-class Client(Iface):
-  def __init__(self, iprot, oprot=None):
-    self._iprot = self._oprot = iprot
-    if oprot is not None:
-      self._oprot = oprot
-    self._seqid = 0
-
-  def ping(self):
-    self.send_ping()
-    self.recv_ping()
-
-  def send_ping(self):
-    self._oprot.writeMessageBegin('ping', TMessageType.CALL, self._seqid)
-    args = ping_args()
-    args.write(self._oprot)
-    self._oprot.writeMessageEnd()
-    self._oprot.trans.flush()
-
-  def recv_ping(self):
-    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
-    if mtype == TMessageType.EXCEPTION:
-      x = TApplicationException()
-      x.read(self._iprot)
-      self._iprot.readMessageEnd()
-      raise x
-    result = ping_result()
-    result.read(self._iprot)
-    self._iprot.readMessageEnd()
-    return
-
-  def run(self, document):
-    """
-    Parameters:
-     - document
-    """
-    self.send_run(document)
-    return self.recv_run()
-
-  def send_run(self, document):
-    self._oprot.writeMessageBegin('run', TMessageType.CALL, self._seqid)
-    args = run_args()
-    args.document = document
-    args.write(self._oprot)
-    self._oprot.writeMessageEnd()
-    self._oprot.trans.flush()
-
-  def recv_run(self):
-    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
-    if mtype == TMessageType.EXCEPTION:
-      x = TApplicationException()
-      x.read(self._iprot)
-      self._iprot.readMessageEnd()
-      raise x
-    result = run_result()
-    result.read(self._iprot)
[…]

### 2014-05-05 services/gen-py/services/PDFParser.py

@@ -1,250 +1,0 @@
-#
-# Autogenerated by Thrift Compiler (0.9.1)
-#
-# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
-#
-#  options string: py:utf8strings,dynamic
-#
-
-from thrift.Thrift import TType, TMessageType, TException, TApplicationException
-from ttypes import *
-from thrift.Thrift import TProcessor
-from thrift.protocol.TBase import TBase, TExceptionBase
-
-
-class Iface(object):
-  def ping(self):
-    pass
-
-  def parse(self, file):
-    """
-    Parameters:
-     - file
-    """
-    pass
-
-  def shutdown(self):
-    pass
-
-
-class Client(Iface):
-  def __init__(self, iprot, oprot=None):
-    self._iprot = self._oprot = iprot
-    if oprot is not None:
-      self._oprot = oprot
-    self._seqid = 0
-
-  def ping(self):
-    self.send_ping()
-    self.recv_ping()
-
-  def send_ping(self):
-    self._oprot.writeMessageBegin('ping', TMessageType.CALL, self._seqid)
-    args = ping_args()
-    args.write(self._oprot)
-    self._oprot.writeMessageEnd()
-    self._oprot.trans.flush()
-
-  def recv_ping(self):
-    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
-    if mtype == TMessageType.EXCEPTION:
-      x = TApplicationException()
-      x.read(self._iprot)
-      self._iprot.readMessageEnd()
-      raise x
-    result = ping_result()
-    result.read(self._iprot)
-    self._iprot.readMessageEnd()
-    return
-
-  def parse(self, file):
-    """
-    Parameters:
-     - file
-    """
-    self.send_parse(file)
-    return self.recv_parse()
-
-  def send_parse(self, file):
-    self._oprot.writeMessageBegin('parse', TMessageType.CALL, self._seqid)
-    args = parse_args()
-    args.file = file
-    args.write(self._oprot)
-    self._oprot.writeMessageEnd()
-    self._oprot.trans.flush()
-
-  def recv_parse(self):
-    (fname, mtype, rseqid) = self._iprot.readMessageBegin()
-    if mtype == TMessageType.EXCEPTION:
-      x = TApplicationException()
-      x.read(self._iprot)
-      self._iprot.readMessageEnd()
-      raise x
-    result = parse_result()
-    result.read(self._iprot)
[…]

### 2014-05-05 services/gen-py/services/__init__.py

@@ -1,1 +1,0 @@
-__all__ = ['ttypes', 'constants', 'PDFParser', 'Filter']

### 2014-05-05 services/gen-py/services/constants.py

@@ -1,11 +1,0 @@
-#
-# Autogenerated by Thrift Compiler (0.9.1)
-#
-# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
-#
-#  options string: py:utf8strings,dynamic
-#
-
-from thrift.Thrift import TType, TMessageType, TException, TApplicationException
-from ttypes import *
-

### 2014-05-05 services/gen-py/services/ttypes.py

@@ -1,49 +1,0 @@
-#
-# Autogenerated by Thrift Compiler (0.9.1)
-#
-# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
-#
-#  options string: py:utf8strings,dynamic
-#
-
-from thrift.Thrift import TType, TMessageType, TException, TApplicationException
-import structs.ttypes
-
-
-from thrift.protocol.TBase import TBase, TExceptionBase
-
-
-
-class ProcessException(TExceptionBase):
-  """
-  Attributes:
-   - timestamp
-   - what
-   - why
-  """
-
-  thrift_spec = (
-    None, # 0
-    (1, TType.I32, 'timestamp', None, None, ), # 1
-    (2, TType.STRING, 'what', None, None, ), # 2
-    (3, TType.STRING, 'why', None, None, ), # 3
-  )
-
-  def __init__(self, timestamp=None, what=None, why=None,):
-    self.timestamp = timestamp
-    self.what = what
-    self.why = why
-
-  def __str__(self):
-    return repr(self)
-
-  def __repr__(self):
-    L = ['%s=%r' % (key, value)
-      for key, value in self.__dict__.iteritems()]
-    return '%s(%s)' % (self.__class__.__name__, ', '.join(L))
-
-  def __eq__(self, other):
-    return isinstance(other, self.__class__) and self.__dict__ == other.__dict__
-
-  def __ne__(self, other):
-    return not (self == other)

### 2014-05-05 services/gen-py/structs/ttypes.py

@@ -1,224 +1,0 @@
-#
-# Autogenerated by Thrift Compiler (0.9.1)
-#
-# DO NOT EDIT UNLESS YOU ARE SURE THAT YOU KNOW WHAT YOU ARE DOING
-#
-#  options string: py:utf8strings,dynamic
-#
-
-from thrift.Thrift import TType, TMessageType, TException, TApplicationException
-
-from thrift.protocol.TBase import TBase, TExceptionBase
-
-
-
-class Interval(TBase):
-  """
-  Attributes:
-   - upper
-   - lower
-  """
-
-  thrift_spec = (
-    None, # 0
-    (1, TType.I32, 'upper', None, None, ), # 1
-    (2, TType.I32, 'lower', None, None, ), # 2
-  )
-
-  def __init__(self, upper=None, lower=None,):
-    self.upper = upper
-    self.lower = lower
-
-  def __repr__(self):
-    L = ['%s=%r' % (key, value)
-      for key, value in self.__dict__.iteritems()]
-    return '%s(%s)' % (self.__class__.__name__, ', '.join(L))
-
-  def __eq__(self, other):
-    return isinstance(other, self.__class__) and self.__dict__ == other.__dict__
-
-  def __ne__(self, other):
-    return not (self == other)
-
-class TextNode(TBase):
-  """
-  Attributes:
-   - pageIndex
-   - interval
-  """
-
-  thrift_spec = (
-    None, # 0
-    (1, TType.I32, 'pageIndex', None, None, ), # 1
-    (2, TType.STRUCT, 'interval', (Interval, Interval.thrift_spec), None, ), # 2
-  )
-
-  def __init__(self, pageIndex=None, interval=None,):
-    self.pageIndex = pageIndex
-    self.interval = interval
-
-  def __repr__(self):
-    L = ['%s=%r' % (key, value)
-      for key, value in self.__dict__.iteritems()]
-    return '%s(%s)' % (self.__class__.__name__, ', '.join(L))
-
-  def __eq__(self, other):
-    return isinstance(other, self.__class__) and self.__dict__ == other.__dict__
-
-  def __ne__(self, other):
-    return not (self == other)
-
-class MetaReference(TBase):
-  """
-  Attributes:
-   - field
-   - idx
-  """
-
-  thrift_spec = (
-    None, # 0
-    (1, TType.STRING, 'field', None, None, ), # 1
-    (2, TType.I32, 'idx', None, None, ), # 2
-  )
-
-  def __init__(self, field=None, idx=None,):
[…]

### 2014-05-05 resources/topologies/JSONFilterServer.py
[WIP] Run Python service from Clojure

@@ -1,0 +1,17 @@
+import os, logging, optparse
+
+DEBUG_MODE = True
+LOG_LEVEL = (logging.DEBUG if DEBUG_MODE else logging.INFO)
+logging.basicConfig(level=LOG_LEVEL, format='[%(levelname)s] %(name)s %(asctime)s: %(message)s')
+log = logging.getLogger(__name__)
+
+def main():
+    p = optparse.OptionParser(description="Runs the file as a worker process on the specified socket",
+                              version="Spa %s" % (os.environ['SPA_VERSION']))
+    p.add_option('--file', '-f')
+    p.add_option('--socket', '-s')
+    options, arguments = p.parse_args()
+    log.debug('Hello %s' % options.file)
+
+if __name__ == '__main__':
+    main()

### 2014-05-05 resources/topologies/JSONFilterServer.py
Handle SIGINT and SIGTERM in Python

@@ -1,17 +1,43 @@
-import os, logging, optparse
+import os, logging, optparse, time, signal
+import zmq
+
+context = zmq.Context()
 
 DEBUG_MODE = True
 LOG_LEVEL = (logging.DEBUG if DEBUG_MODE else logging.INFO)
 logging.basicConfig(level=LOG_LEVEL, format='[%(levelname)s] %(name)s %(asctime)s: %(message)s')
 log = logging.getLogger(__name__)
 
+def destroy(signum, frame):
+    log.warn("received %s shutting down..." % (signum))
+    # context.destroy depends on pyzmq >= 2.1.10
+    context.destroy(0)
+
+signal.signal(signal.SIGINT, destroy)
+signal.signal(signal.SIGTERM, destroy)
+
+def run_server(socket_addr):
+    log.info("Starting server on %s" % (socket_addr))
+    socket = context.socket(zmq.REP)
+    socket.bind(socket_addr)
+    try:
+        # Wait for next request from client
+        while True:
+            message = socket.recv()
+            log.debug("Received request: %s" % (message))
+            time.sleep(1)
+            socket.send("World from %s" % socket_addr)
+    except zmq.ZMQError as e:
+        log.info("recv failed with: %s" % e)
+
 def main():
-    p = optparse.OptionParser(description="Runs the file as a worker process on the specified socket",
-                              version="Spa %s" % (os.environ['SPA_VERSION']))
+    p = optparse.OptionParser(
+        description="Runs the file as a worker process on the specified socket",
+        version="Spa %s" % (os.environ['SPA_VERSION']))
     p.add_option('--file', '-f')
     p.add_option('--socket', '-s')
     options, arguments = p.parse_args()
-    log.debug('Hello %s' % options.file)
+    run_server(options.socket)
 
 if __name__ == '__main__':
     main()

### 2014-05-05 resources/topologies/JSONFilterServer.py
Simple REQ-REP between Python & Clojure

@@ -25,7 +25,6 @@ def run_server(socket_addr):
         while True:
             message = socket.recv()
             log.debug("Received request: %s" % (message))
-            time.sleep(1)
             socket.send("World from %s" % socket_addr)
     except zmq.ZMQError as e:
         log.info("recv failed with: %s" % e)

### 2014-05-06 resources/multilang/python/AbstractFilter.py
Dynamically load python modules by name

@@ -1,0 +1,8 @@
+from abc import ABCMeta, abstractmethod
+
+class AbstractFilter(object):
+    __metaclass__ = ABCMeta
+
+    @abstractmethod
+    def run(self, payload):
+        pass

### 2014-05-06 resources/multilang/python/JSONFilterServer.py

@@ -1,43 +1,58 @@
-import os, logging, optparse, time, signal
+import os, logging, optparse, time, signal, sys
 import zmq
+import json
+
+
+def str2bool(v):
+  return v.lower() in ("yes", "true", "t", "1")
 
 context = zmq.Context()
 
-DEBUG_MODE = os.environ("DEBUG")
-VERSION = os.environ("VERSION")
+DEBUG_MODE = str2bool(os.environ.get("DEBUG", "true"))
+VERSION = os.environ.get("SPA_VERSION", "<I HAVE NO MASTER>")
 LOG_LEVEL = (logging.DEBUG if DEBUG_MODE else logging.INFO)
 logging.basicConfig(level=LOG_LEVEL, format='[%(levelname)s] %(name)s %(asctime)s: %(message)s')
 log = logging.getLogger(__name__)
 
 def destroy(signum, frame):
     log.warn("received %s shutting down..." % (signum))
-    # context.destroy depends on pyzmq >= 2.1.10
     context.destroy(0)
 
 signal.signal(signal.SIGINT, destroy)
 signal.signal(signal.SIGTERM, destroy)
 
-def run_server(socket_addr):
-    log.info("Hail to the king Spa %s on %s" % (VERSION, socket_addr))
+def run_server(socket_addr, handler):
+    log.info("Hail to the king %s on %s" % (VERSION, socket_addr))
     socket = context.socket(zmq.REP)
     socket.bind(socket_addr)
     try:
         # Wait for next request from client
         while True:
-            message = socket.recv()
-            log.debug("Received request: %s" % (message))
-            socket.send("World from %s" % socket_addr)
+            try:
+                message = json.loads(socket.recv())
+                response = handler.run(message)
+                socket.send(json.dumps(response, ensure_ascii=False))
+            except Exception as e:
+                socket.send(json.dumps({"cause": str(e)}))
     except zmq.ZMQError as e:
         log.info("recv failed with: %s" % e)
 
 def main():
     p = optparse.OptionParser(
-        description="Runs the file (subclass of AbstractFilter) as a worker process on the specified socket",
-        version="Spa %s" % (VERSION))
-    p.add_option('--file', '-f')
+        description="Runs the filter (subclass of AbstractFilter) from the module as a worker process on the specified socket",
+        version="%s" % (VERSION))
+    p.add_option('--module', '-m')
     p.add_option('--socket', '-s')
[…]

### 2014-05-06 resources/topologies/ebm/sentence_tokenizer.py

@@ -1,0 +1,19 @@
+import sys, glob
+sys.path.append('../../multilang/python')
+
+import logging
+logger = logging.getLogger(__name__)
+
+from AbstractFilter import AbstractFilter
+
+class Filter(AbstractFilter):
+    title = "Sentence Tokenizer"
+
+    def __init__(self):
+        logger.info("constructing %s" % (self.title))
+
+    def run(self, payload):
+        return {"response": "Gotcha %s" % (payload)}
+
+if __name__ == '__main__':
+    Filter().run("")

### 2014-05-07 resources/topologies/ebm/sentence_tokenizer.py
Make topologies callable

@@ -13,7 +13,7 @@ class Filter(AbstractFilter):
         logger.info("constructing %s" % (self.title))
 
     def run(self, payload):
-        return {"response": "Gotcha %s" % (payload)}
+        return {"echo": payload} # Some modified payload
 
 if __name__ == '__main__':
     Filter().run("")

### 2014-05-07 resources/topologies/ebm/word_tokenizer.py

@@ -1,0 +1,19 @@
+import sys, glob
+sys.path.append('../../multilang/python')
+
+import logging
+logger = logging.getLogger(__name__)
+
+from AbstractFilter import AbstractFilter
+
+class Filter(AbstractFilter):
+    title = "Word Tokenizer"
+
+    def __init__(self):
+        logger.info("constructing %s" % (self.title))
+
+    def run(self, payload):
+        return {} # Some modified payload
+
+if __name__ == '__main__':
+    Filter().run("")

### 2014-05-07 resources/topologies/ebm/word_tokenizer.py
Be able to call topologies over HTTP with RPCs

@@ -13,7 +13,7 @@ class Filter(AbstractFilter):
         logger.info("constructing %s" % (self.title))
 
     def run(self, payload):
-        return {} # Some modified payload
+        return {"count": len(payload)} # Some result
 
 if __name__ == '__main__':
     Filter().run("")

### 2014-05-07 resources/multilang/python/JSONFilterServer.py
Actually exit Python process

@@ -17,6 +17,7 @@ log = logging.getLogger(__name__)
 def destroy(signum, frame):
     log.warn("received %s shutting down..." % (signum))
     context.destroy(0)
+    sys.exit(0)
 
 signal.signal(signal.SIGINT, destroy)
 signal.signal(signal.SIGTERM, destroy)

### 2014-05-12 resources/multilang/nodejs/worker.js
Fixes to NodeJS RPC
- May receive a promise now as result value
- Added rudimentary PDF-to-Text (based on BWC work)

@@ -45,7 +45,7 @@ Worker.prototype.connectToBroker = function () {
   }
   self.socket = zmq.socket('dealer');
   self.socket.identity = self.name;
-  self.socket.setsockopt('linger', 1);
+  self.socket.setsockopt('linger', 0);
 
   self.socket.on('message', function () {
     self.onMsg.call(self, arguments);
@@ -59,7 +59,7 @@ Worker.prototype.connectToBroker = function () {
   self.hbTimer = setInterval(function () {
     self.sendHeartbeat();
     self.liveness--;
-    if (! self.liveness) {
+    if (!self.liveness) {
       clearInterval(self.hbTimer);
       console.log('Disconnected from broker - retrying in %s sec(s)...', (self.reconnect / 1000));
       setTimeout(function () {
@@ -79,7 +79,7 @@ Worker.prototype.onMsg = function (msg) {
   self.liveness = HEARTBEAT_LIVENESS;
 
   if (header !== MDP.WORKER) {
-    self.emitErr('(onMsg) Invalid message header \'' + header + '\'');
+    self.emitErr('Invalid message header \'' + header + '\'');
     // send error
     return;
   }

### 2014-05-12 resources/topologies/ebm/document_filter.py

@@ -2,7 +2,7 @@ import json
 
 import sys
 sys.path.append('../../multilang/python')
-import logging, copy
+import logging
 log = logging.getLogger(__name__)
 
 
@@ -19,7 +19,7 @@ class DocumentFilter(AbstractFilter):
             result = self.filter(document)
             return json.dumps(result, ensure_ascii=True)
         except Exception as e:
-            return json.dumps({"cause": str(e)})
+            return json.dumps({"cause": str(e)}, ensure_ascii=True)
 
     @abstractmethod
     def filter(self, document):

### 2014-05-12 resources/topologies/ebm/document_parser.js

@@ -1,7 +1,48 @@
+var program = require('commander');
+var fs = require('fs');
+var atob = require('atob');
+var _ = require('underscore');
+var Q = require('q');
+
+// let PDF.js be loaded not as a module in global space.
+global.window = global;
+global.navigator = { userAgent: "node" };
+global.PDFJS = {};
+global.DOMParser = require('./pdfjs/domparsermock.js').DOMParserMock;
+
+require('./pdfjs/pdf.combined.js');
+
 function handler(payload) {
-  var data = JSON.parse(payload);
-  data.text = "foobar";
-  return JSON.stringify(data);
+  return PDFJS.getDocument(payload).then(function (pdf) {
+    var pages = _.map(_.range(1, pdf.numPages + 1), function(pageNr) {
+      return pdf.getPage(pageNr);
+    });
+
+    return Q.all(_.invoke(pages, "then", function(page) {
+      return page.getTextContent().then(function(content) {
+        return content;
+      });
+    }));
+  });
+};
+
+if(require.main === module) {
+  program
+    .option('-i, --input [input]', 'path to PDF to parse')
+    .option('-o, --output [output]', 'path to output file')
+    .parse(process.argv);
+
+  var pdf = new Uint8Array(fs.readFileSync(program.input));
+  var out = program.output;
+  var resultPromise = handler(pdf);
+  resultPromise.then(function(result) {
+    result = JSON.stringify(result);
+    if(out) {
+      fs.writeFile(out, result);
+    } else {
+      console.log(result);
+    }
+  });
 }
 
 module.exports = handler;

### 2014-05-13 doc/paper.tex
Remove reference to KDD submission
- Minor fixes

@@
 Summarizing the evidence about medical interventions is an immense undertaking, in part because unstructured \ac{pdf} documents remain the main vehicle for disseminating scientific findings.
-Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf} to be published in \emph{systematic reviews}.
-We introduce Spá,\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://spa.clinici.co/}} a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \ac{ml}.
-To illustrate its functionalility, here we use Spá to semi-automate the assessment of bias in clinical trials.
+Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf}.
+We introduce Spá,\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{Kuiper2014}; demo available at \url{http://spa.clinici.co/}} a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \acl{ml}.
+To illustrate its functionality, we use Spá to semi-automate the assessment of bias in clinical trials.
 %Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low or high risk of various biases), and annotate sentences that support these classifications.
@@
 \emph{Systematic reviews} are an instructive example.
-Such reviews aim to answer clinical questions by providing an exhaustive synthesis (textual and statistical) of the current evidence in all published literature.
-They are fundamental tools in \ac{ebm} \cite{sackett1996}.
-To produce these reviews data, like potential biases, must be manually extracted from the literature.
-These extraction tasks are extremely labourous, but could potentially be (semi-)automated using machine learning approaches.
+Such reviews aim to answer clinical questions by providing an exhaustive synthesis of all the current evidence in published literature.
+They are fundamental tools in \ac{ebm} \cite{Sackett1996,Valkenhoef2012}.
+Data must be manually extracted from the literature to produce the systematic reviews.
+These extraction tasks are extremely laborious, but could potentially be assisted by machine learning approaches.
 
-As an example, we consider the risk of bias assessment, in which reviewers assess, e.g., whether study participants and personnel were properly blinded.
+As an example we consider risk of bias assessment.
+Here reviewers assess, e.g., whether study participants and personnel were properly blinded \cite{Higgins2011}.
 Assessing risk of bias is a time-consuming task.
-A single trial may typically take a domain expert ten minutes \cite{Hartling2011}, and a single review may typically include several dozen trials.
-Making matters worse, due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus.\cite{Hartling2009}
+A single trial typically takes a domain expert ten minutes \cite{Hartling2011}, and a single review typically includes several dozen trials.
+Making matters worse, due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus \cite{Hartling2009}.
 
@@
 Here the risk of bias is assessed to be low, for example, and one of the supporting sentences for this assessment describes the randomization procedure (highlighted in green).}
-\vspace{-1em}
+\vspace{-1.5em}
 \end{figure}
 
-While our application of interest is \ac{ebm}, we emphasize that the visualization tool can be used for any domain in which one wants to annotate \acp{pdf}.
+While our application of interest is \ac{ebm}, we emphasize that the visualization tool can be used for any domain in which one wants to annotate \acp{pdf}, e.g.
+genome-wide association studies or jurisprudence.
 Thus the contribution of this work is two-fold, as we present:
 (1) a practical tool that incorporates machine learning to help researchers rapidly assess the risk of biases in published biomedical articles, and,
-(2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
-These contributions are described further in Sections \ref{section:EBM-ML} and \ref{section:architecture}.
+(2) a general open-source system for visualizing the predictions of trained models from full-text articles on the web.
+%These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}.
 
-\section{Automating \acl{ebm}}
+\section{Case study: Risk of Bias in \acl{ebm}}
 \label{section:EBM-ML}
@@
 We match these strings to substrings in the \acp{pdf} to provide sentence-level supervision.
-This can be viewed as a \emph{distantly supervised} \cite{mintz-09} approach.
+This can be viewed as a \emph{distantly supervised} \cite{Mintz09,Nguyen11} approach.
 
@@
 %%%
-From a \ac{ml} vantage, we have two tasks for a given article: (1) predict the overall risk of bias for each of the domains of interest, and (2) extract the sentences that support these assessments.
-For both tasks we leverage standard bag-of-words text encoding and linear-kernel \acp{svm}.
-Because the risk of bias predictions are correlated (across domains), we take a \emph{multi-task} \cite{evgeniou2004} approach to classification and jointly learn a model for the domains.
-We accomplish this by way of a feature space construction that includes both shared and domain-specific terms (similar to the domain adaptation approach in \cite{daume2007}).
+From a \ac{ml} vantage, we have two tasks for a given article: (1) predict the overall risk of bias for each of the domains, and (2) extract the sentences that support these assessments.
+For both tasks we leverage standard bag-of-words text encoding and linear-kernel \aclp{svm}.
+Because the risk of bias predictions are correlated across domains, we take a \emph{multi-task} \cite{Evgeniou2004} approach to classification and jointly learn a model for the domains.
+We accomplish this by way of a feature space construction that includes both shared and domain-specific terms, similar to the domain adaptation approach in \cite{Daume2007}.
 %Furthermore, we take a unified approach to the two tasks by \emph{jointly} assessing the risk of bias associated with a given article \emph{and} extracting the sentences that support this judgment.
-Specifically, we first make sentence level predictions (using one set of trained models), and then insert features representing the tokens (words) in the predicted sentences for exploitation by the document level classifier (further details specified in \cite{marshall2014}).
+Specifically, we first make sentence level prediction, and then insert features representing the tokens in the predicted sentences for exploitation by the document level classifier.
 Figure \ref{fig:screenshot} shows the system in use.
@@
 For each of the annotations the relevant nodes in the document are highlighted.
-A custom scrollbar\footnote{inspired by \href{http://substance.io/}{substance.io}} that acts as a `mini-map' is projected to show where annotations reside within the document.
+A custom scrollbar, inspired by \href{http://substance.io/}{substance.io}, that acts as a `mini-map' is projected to show where annotations reside within the document.
 The user can interactively activate and inspect specific results.
@@
 We have presented a web-based tool for visualization of annotations and marginalia for \ac{pdf} documents.
-Furthermore, we have demonstrated the use of this system within the context of \ac{ebm} by automatically extracting potential risks of bias.
+Furthermore, we have demonstrated the use of this system within the context of \acl{ebm} by automatically extracting potential risks of bias.
 
-More generally, we believe the tool to be potentially useful for a much wider range of text mining and \acl{ml} applications.
-To increase the generality of the tool we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated \ac{pdf} annotation.
-Furthermore, we are working to allow users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
-The vision is to have an extensible system for semi-automated (machine assisted) screening, data extraction and data summarization for EBM, and to allow rapid development of similar systems for other domains.
+We believe the tool to be potentially useful for a much wider range of \acl{ml} applications.
+Currently we are developing a pluggable system for processing topologies, allowing developers to quickly plug in new systems for automated \ac{pdf} annotation.
+Furthermore, we are working to allow users to persist annotations and marginalia, possibly embedded within the document itself, for sharing and off-line use.
+The vision is to have an extensible system for machine assisted data extraction that will greatly increase both the quality and the reproducibility (i.e. data provenance) of current \acl{ebm}.
 

### 2014-05-13 doc/paper.tex
Remove reference to KDD submission

@@
 Clinicians and researchers must therefore manually extract and synthesise information from these \acp{pdf}.
-We introduce Spá,\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{Kuiper2014}; demo available at \url{http://spa.clinici.co/}} a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \acl{ml}.
+We introduce Spá\footnote{From the Old Norse word spá or spæ referring to prophesying (prophecy)}\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{Kuiper2014}; demo available at \url{http://spa.clinici.co/}}, a web-based viewer that enables automated annotation and summarisation of \acp{pdf} via \acl{ml}.
 To illustrate its functionality, we use Spá to semi-automate the assessment of bias in clinical trials.
@@
 Assessing risk of bias is a time-consuming task.
-A single trial typically takes a domain expert ten minutes \cite{Hartling2011}, and a single review typically includes several dozen trials.
+A single trial may typically take a domain expert ten minutes \cite{Hartling2011}, and a single review may typically include several dozen trials.
 Making matters worse, due to low rates of reviewer agreement it is regarded as best practice to have each study assessed twice by independent reviewers who later come to a consensus \cite{Hartling2009}.
@@
 (1) a practical tool that incorporates machine learning to help researchers rapidly assess the risk of biases in published biomedical articles, and,
-(2) a general open-source system for visualizing the predictions of trained models from full-text articles on the web.
+(2) a general open-source web tool for visualizing the predictions of trained models from full-text articles.
 %These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}.

### 2014-05-13 resources/pdfjs/src/core/evaluator.js
Add PDFjs as submodule

@@ -1,0 +1,2239 @@
+/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
+/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
+/* Copyright 2012 Mozilla Foundation
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+/* globals assert, ColorSpace, DecodeStream, Dict, Encodings,
+           error, ErrorFont, Font, FONT_IDENTITY_MATRIX, fontCharsToUnicode,
+           FontFlags, ImageKind, info, isArray, isCmd, isDict, isEOF, isName,
+           isNum, isStream, isString, JpegStream, Lexer, Metrics,
+           MurmurHash3_64, Name, Parser, Pattern, PDFImage, PDFJS, serifFonts,
+           stdFontMap, symbolsFonts, getTilingPatternIR, warn, Util, Promise,
+           RefSetCache, isRef, TextRenderingMode, CMapFactory, OPS,
+           UNSUPPORTED_FEATURES, UnsupportedManager, NormalizedUnicodes,
+           IDENTITY_MATRIX, reverseIfRtl */
+
+'use strict';
+
+var PartialEvaluator = (function PartialEvaluatorClosure() {
+  function PartialEvaluator(pdfManager, xref, handler, pageIndex,
+                            uniquePrefix, idCounters, fontCache) {
+    this.pdfManager = pdfManager;
+    this.xref = xref;
+    this.handler = handler;
+    this.pageIndex = pageIndex;
+    this.uniquePrefix = uniquePrefix;
+    this.idCounters = idCounters;
+    this.fontCache = fontCache;
+  }
+
+  var TILING_PATTERN = 1, SHADING_PATTERN = 2;
+
+  PartialEvaluator.prototype = {
+    hasBlendModes: function PartialEvaluator_hasBlendModes(resources) {
+      if (!isDict(resources)) {
+        return false;
+      }
+
[…]

### 2014-05-13 resources/pdfjs/src/display/api.js

@@ -1,0 +1,1367 @@
+/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
+/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
+/* Copyright 2012 Mozilla Foundation
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+/* globals CanvasGraphics, combineUrl, createScratchCanvas, error,
+           FontLoader, globalScope, info, isArrayBuffer, loadJpegStream,
+           MessageHandler, PDFJS, Promise, StatTimer, warn,
+           PasswordResponses, Util, loadScript, createPromiseCapability,
+           FontFace */
+
+'use strict';
+
+/**
+ * The maximum allowed image size in total pixels e.g. width * height. Images
+ * above this value will not be drawn. Use -1 for no limit.
+ * @var {number}
+ */
+PDFJS.maxImageSize = (PDFJS.maxImageSize === undefined ?
+                      -1 : PDFJS.maxImageSize);
+
+/**
+ * The url of where the predefined Adobe CMaps are located. Include trailing
+ * slash.
+ * @var {string}
+ */
+PDFJS.cMapUrl = (PDFJS.cMapUrl === undefined ? null : PDFJS.cMapUrl);
+
+/**
+ * Specifies if CMaps are binary packed.
+ * @var {boolean}
+ */
+PDFJS.cMapPacked = PDFJS.cMapPacked === undefined ? false : PDFJS.cMapPacked;
+
+/*
+ * By default fonts are converted to OpenType fonts and loaded via font face
+ * rules. If disabled, the font will be rendered using a built in font renderer
+ * that constructs the glyphs with primitive path commands.
+ * @var {boolean}
+ */
+PDFJS.disableFontFace = (PDFJS.disableFontFace === undefined ?
+                         false : PDFJS.disableFontFace);
+
+/**
[…]

### 2014-05-13 resources/pdfjs/src/display/canvas.js

@@ -1,0 +1,2191 @@
+/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
+/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
+/* Copyright 2012 Mozilla Foundation
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+/* globals ColorSpace, DeviceCmykCS, DeviceGrayCS, DeviceRgbCS, error, PDFJS,
+           FONT_IDENTITY_MATRIX, Uint32ArrayView, IDENTITY_MATRIX, ImageData,
+           ImageKind, isArray, isNum, TilingPattern, OPS, Promise, Util, warn,
+           assert, info, shadow, TextRenderingMode, getShadingPatternFromIR,
+           WebGLUtils */
+
+'use strict';
+
+// <canvas> contexts store most of the state we need natively.
+// However, PDF needs a bit more state, which we store here.
+
+// Minimal font size that would be used during canvas fillText operations.
+var MIN_FONT_SIZE = 16;
+var MAX_GROUP_SIZE = 4096;
+
+var COMPILE_TYPE3_GLYPHS = true;
+
+function createScratchCanvas(width, height) {
+  var canvas = document.createElement('canvas');
+  canvas.width = width;
+  canvas.height = height;
+  return canvas;
+}
+
+function addContextCurrentTransform(ctx) {
+  // If the context doesn't expose a `mozCurrentTransform`, add a JS based on.
+  if (!ctx.mozCurrentTransform) {
+    // Store the original context
+    ctx._scaleX = ctx._scaleX || 1.0;
+    ctx._scaleY = ctx._scaleY || 1.0;
+    ctx._originalSave = ctx.save;
+    ctx._originalRestore = ctx.restore;
+    ctx._originalRotate = ctx.rotate;
[…]

### 2014-05-13 resources/pdfjs/src/shared/annotation.js

@@ -1,0 +1,825 @@
+/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
+/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
+/* Copyright 2012 Mozilla Foundation
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+/* globals Util, isDict, isName, stringToPDFString, warn, Dict, Stream,
+           stringToBytes, PDFJS, isWorker, assert, NotImplementedException,
+           Promise, isArray, ObjectLoader, isValidUrl, OperatorList, OPS,
+           createPromiseCapability */
+
+'use strict';
+
+var DEFAULT_ICON_SIZE = 22; // px
+var HIGHLIGHT_OFFSET = 4; // px
+var SUPPORTED_TYPES = ['Link', 'Text', 'Widget'];
+
+var Annotation = (function AnnotationClosure() {
+  // 12.5.5: Algorithm: Appearance streams
+  function getTransformMatrix(rect, bbox, matrix) {
+    var bounds = Util.getAxialAlignedBoundingBox(bbox, matrix);
+    var minX = bounds[0];
+    var minY = bounds[1];
+    var maxX = bounds[2];
+    var maxY = bounds[3];
+
+    if (minX === maxX || minY === maxY) {
+      // From real-life file, bbox was [0, 0, 0, 0]. In this case,
+      // just apply the transform for rect
+      return [1, 0, 0, 1, rect[0], rect[1]];
+    }
+
+    var xRatio = (rect[2] - rect[0]) / (maxX - minX);
+    var yRatio = (rect[3] - rect[1]) / (maxY - minY);
+    return [
+      xRatio,
+      0,
+      0,
+      yRatio,
+      rect[0] - minX * xRatio,
+      rect[1] - minY * yRatio
+    ];
+  }
+
+  function getDefaultAppearance(dict) {
[…]

### 2014-05-13 resources/pdfjs/src/shared/util.js

@@ -1,0 +1,1509 @@
+/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
+/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
+/* Copyright 2012 Mozilla Foundation
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+/* globals Cmd, ColorSpace, Dict, MozBlobBuilder, Name, PDFJS, Ref, URL,
+           Promise */
+
+'use strict';
+
+var globalScope = (typeof window === 'undefined') ? this : window;
+
+var isWorker = (typeof window == 'undefined');
+
+var FONT_IDENTITY_MATRIX = [0.001, 0, 0, 0.001, 0, 0];
+
+var TextRenderingMode = {
+  FILL: 0,
+  STROKE: 1,
+  FILL_STROKE: 2,
+  INVISIBLE: 3,
+  FILL_ADD_TO_PATH: 4,
+  STROKE_ADD_TO_PATH: 5,
+  FILL_STROKE_ADD_TO_PATH: 6,
+  ADD_TO_PATH: 7,
+  FILL_STROKE_MASK: 3,
+  ADD_TO_PATH_FLAG: 4
+};
+
+var ImageKind = {
+  GRAYSCALE_1BPP: 1,
+  RGB_24BPP: 2,
+  RGBA_32BPP: 3
+};
+
+// The global PDFJS object exposes the API
+// In production, it will be declared outside a global wrapper
+// In development, it will be declared here
+if (!globalScope.PDFJS) {
+  globalScope.PDFJS = {};
+}
+
+globalScope.PDFJS.pdfBug = false;
+
+PDFJS.VERBOSITY_LEVELS = {
+  errors: 0,
+  warnings: 1,
+  infos: 5
+};
+
+// All the possible operations for an operator list.
+var OPS = PDFJS.OPS = {
[…]

### 2014-05-13 resources/pdfjs/src/worker_loader.js

@@ -1,0 +1,82 @@
+/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
+/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
+/* Copyright 2012 Mozilla Foundation
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+ /* globals PDFJS, Util */
+
+'use strict';
+
+// List of shared files to include;
+var sharedFiles = [
+  'shared/util.js',
+  'shared/colorspace.js',
+  'shared/function.js',
+  'shared/annotation.js'
+];
+
+// List of other files to include;
+var otherFiles = [
+  'core/network.js',
+  'core/chunked_stream.js',
+  'core/pdf_manager.js',
+  'core/core.js',
+  'core/obj.js',
+  'core/charsets.js',
+  'core/cidmaps.js',
+  'core/crypto.js',
+  'core/pattern.js',
+  'core/evaluator.js',
+  'core/cmap.js',
+  'core/fonts.js',
+  'core/font_renderer.js',
+  'core/glyphlist.js',
+  'core/image.js',
+  'core/metrics.js',
+  'core/parser.js',
+  'core/ps_parser.js',
+  'core/stream.js',
+  'core/worker.js',
+  'core/arithmetic_decoder.js',
+  'core/jpg.js',
+  'core/jpx.js',
+  'core/jbig2.js',
+  'core/bidi.js',
+  'core/murmurhash3.js'
+];
+
+function loadInOrder(index, path, files) {
+  if (index >= files.length) {
+    PDFJS.fakeWorkerFilesLoadedCapability.resolve();
+    return;
+  }
+  PDFJS.Util.loadScript(path + files[index],
+                  loadInOrder.bind(null, ++index, path, files));
+}
+
+// Load all the files.
+if (typeof PDFJS === 'undefined' || !PDFJS.fakeWorkerFilesLoadedCapability) {
[…]

### 2014-05-13 resources/pdfjs/test/unit/evaluator_spec.js

@@ -1,0 +1,181 @@
+/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
+/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
+/* globals expect, it, describe, PartialEvaluator, StringStream, OPS */
+
+'use strict';
+
+describe('evaluator', function() {
+  function XrefMock(queue) {
+    this.queue = queue;
+  }
+  XrefMock.prototype = {
+    fetchIfRef: function() {
+      return this.queue.shift();
+    }
+  };
+  function HandlerMock() {
+    this.inputs = [];
+  }
+  HandlerMock.prototype = {
+    send: function(name, data) {
+      this.inputs({name: name, data: data});
+    }
+  };
+  function ResourcesMock() { }
+  ResourcesMock.prototype = {
+    get: function(name) {
+      return this[name];
+    }
+  };
+
+  function PdfManagerMock() { }
+
+  describe('splitCombinedOperations', function() {
+    it('should reject unknown operations', function() {
+      var evaluator = new PartialEvaluator(new PdfManagerMock(),
+                                           new XrefMock(), new HandlerMock(),
+                                           'prefix');
+      var stream = new StringStream('fTT');
+      var result = evaluator.getOperatorList(stream, new ResourcesMock());
+      expect(!!result.fnArray && !!result.argsArray).toEqual(true);
+      expect(result.fnArray.length).toEqual(1);
+      expect(result.fnArray[0]).toEqual(OPS.fill);
+      expect(result.argsArray[0].length).toEqual(0);
+    });
+
+    it('should handle one operations', function() {
+      var evaluator = new PartialEvaluator(new PdfManagerMock(),
+                                           new XrefMock(), new HandlerMock(),
+                                           'prefix');
+      var stream = new StringStream('Q');
+      var result = evaluator.getOperatorList(stream, new ResourcesMock());
+      expect(!!result.fnArray && !!result.argsArray).toEqual(true);
+      expect(result.fnArray.length).toEqual(1);
+      expect(result.fnArray[0]).toEqual(OPS.restore);
+    });
+
+    it('should handle two glued operations', function() {
+      var evaluator = new PartialEvaluator(new PdfManagerMock(),
+                                           new XrefMock(), new HandlerMock(),
+                                           'prefix');
+      var resources = new ResourcesMock();
+      resources.Res1 = {};
[…]

### 2014-05-13 resources/pdfjs/web/viewer.js

@@ -1,0 +1,2429 @@
+/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
+/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
+/* Copyright 2012 Mozilla Foundation
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+/* globals PDFJS, PDFBug, FirefoxCom, Stats, Cache, PDFFindBar, CustomStyle,
+           PDFFindController, ProgressBar, TextLayerBuilder, DownloadManager,
+           getFileName, scrollIntoView, getPDFFileNameFromURL, PDFHistory,
+           Preferences, SidebarView, ViewHistory, PageView, ThumbnailView, URL,
+           noContextMenuHandler, SecondaryToolbar, PasswordPrompt,
+           PresentationMode, HandTool, Promise, DocumentProperties,
+           DocumentOutlineView, DocumentAttachmentsView */
+
+'use strict';
+
+var DEFAULT_URL = 'compressed.tracemonkey-pldi-09.pdf';
+var DEFAULT_SCALE = 'auto';
+var DEFAULT_SCALE_DELTA = 1.1;
+var UNKNOWN_SCALE = 0;
+var CACHE_SIZE = 20;
+var CSS_UNITS = 96.0 / 72.0;
+var SCROLLBAR_PADDING = 40;
+var VERTICAL_PADDING = 5;
+var MAX_AUTO_SCALE = 1.25;
+var MIN_SCALE = 0.25;
+var MAX_SCALE = 4.0;
+var VIEW_HISTORY_MEMORY = 20;
+var SCALE_SELECT_CONTAINER_PADDING = 8;
+var SCALE_SELECT_PADDING = 22;
[…]

### 2014-05-13 resources/public/scripts/main.js

@@ -25,7 +25,7 @@ require.config({
       exports: "Backbone" },
     'PDFJS': {
       exports: 'PDFJS',
-      deps: ['vendor/pdfjs/compatibility', 'vendor/pdfjs/ui_utils'] }
+      deps: ['vendor/pdfjs/generic/web/compatibility', 'vendor/ui_utils'] }
   }
 });
 

### 2014-05-13 resources/public/scripts/models/appState.js

@@ -2,7 +2,7 @@
 define(['backbone', 'PDFJS'], function(Backbone, PDFJS) {
   'use strict';
   PDFJS.workerSrc = 'static/scripts/vendor/pdfjs/pdf.worker.js';
-  PDFJS.cMapUrl = 'static/scripts/vendor/pdfjs/cmaps/';
+  PDFJS.cMapUrl = 'static/scripts/vendor/pdfjs/generic/web/cmaps/';
   PDFJS.cMapPacked = true;
   PDFJS.disableWebGL = false;
 

### 2014-05-13 resources/topologies/ebm/document_parser.js

@@ -8,9 +8,9 @@ var Q = require('q');
 global.window = global;
 global.navigator = { userAgent: "node" };
 global.PDFJS = {};
-global.DOMParser = require('./pdfjs/domparsermock.js').DOMParserMock;
+global.DOMParser = require('./domparsermock.js').DOMParserMock;
 
-require('./pdfjs/pdf.combined.js');
+require('./pdfjs/singlefile/build/pdf.combined.js');
 
 function handler(payload) {
   return PDFJS.getDocument(payload).then(function (pdf) {

### 2014-05-13 resources/pdfjs/src/core/evaluator.js
Reattempt to add pdfjs as submodule

@@ -1,2239 +1,0 @@
-/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
-/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
-/* Copyright 2012 Mozilla Foundation
- *
- * Licensed under the Apache License, Version 2.0 (the "License");
- * you may not use this file except in compliance with the License.
- * You may obtain a copy of the License at
- *
- *     http://www.apache.org/licenses/LICENSE-2.0
- *
- * Unless required by applicable law or agreed to in writing, software
- * distributed under the License is distributed on an "AS IS" BASIS,
- * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
- * See the License for the specific language governing permissions and
- * limitations under the License.
- */
-/* globals assert, ColorSpace, DecodeStream, Dict, Encodings,
-           error, ErrorFont, Font, FONT_IDENTITY_MATRIX, fontCharsToUnicode,
-           FontFlags, ImageKind, info, isArray, isCmd, isDict, isEOF, isName,
-           isNum, isStream, isString, JpegStream, Lexer, Metrics,
-           MurmurHash3_64, Name, Parser, Pattern, PDFImage, PDFJS, serifFonts,
-           stdFontMap, symbolsFonts, getTilingPatternIR, warn, Util, Promise,
-           RefSetCache, isRef, TextRenderingMode, CMapFactory, OPS,
-           UNSUPPORTED_FEATURES, UnsupportedManager, NormalizedUnicodes,
-           IDENTITY_MATRIX, reverseIfRtl */
-
-'use strict';
-
-var PartialEvaluator = (function PartialEvaluatorClosure() {
-  function PartialEvaluator(pdfManager, xref, handler, pageIndex,
-                            uniquePrefix, idCounters, fontCache) {
-    this.pdfManager = pdfManager;
-    this.xref = xref;
-    this.handler = handler;
-    this.pageIndex = pageIndex;
-    this.uniquePrefix = uniquePrefix;
-    this.idCounters = idCounters;
-    this.fontCache = fontCache;
-  }
-
-  var TILING_PATTERN = 1, SHADING_PATTERN = 2;
-
-  PartialEvaluator.prototype = {
-    hasBlendModes: function PartialEvaluator_hasBlendModes(resources) {
-      if (!isDict(resources)) {
-        return false;
-      }
-
-      var processed = Object.create(null);
[…]

### 2014-05-13 resources/pdfjs/src/display/api.js

@@ -1,1367 +1,0 @@
-/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
-/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
-/* Copyright 2012 Mozilla Foundation
- *
- * Licensed under the Apache License, Version 2.0 (the "License");
- * you may not use this file except in compliance with the License.
- * You may obtain a copy of the License at
- *
- *     http://www.apache.org/licenses/LICENSE-2.0
- *
- * Unless required by applicable law or agreed to in writing, software
- * distributed under the License is distributed on an "AS IS" BASIS,
- * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
- * See the License for the specific language governing permissions and
- * limitations under the License.
- */
-/* globals CanvasGraphics, combineUrl, createScratchCanvas, error,
-           FontLoader, globalScope, info, isArrayBuffer, loadJpegStream,
-           MessageHandler, PDFJS, Promise, StatTimer, warn,
-           PasswordResponses, Util, loadScript, createPromiseCapability,
-           FontFace */
-
-'use strict';
-
-/**
- * The maximum allowed image size in total pixels e.g. width * height. Images
- * above this value will not be drawn. Use -1 for no limit.
- * @var {number}
- */
-PDFJS.maxImageSize = (PDFJS.maxImageSize === undefined ?
-                      -1 : PDFJS.maxImageSize);
-
-/**
- * The url of where the predefined Adobe CMaps are located. Include trailing
- * slash.
- * @var {string}
- */
-PDFJS.cMapUrl = (PDFJS.cMapUrl === undefined ? null : PDFJS.cMapUrl);
-
-/**
- * Specifies if CMaps are binary packed.
- * @var {boolean}
- */
-PDFJS.cMapPacked = PDFJS.cMapPacked === undefined ? false : PDFJS.cMapPacked;
-
-/*
- * By default fonts are converted to OpenType fonts and loaded via font face
- * rules. If disabled, the font will be rendered using a built in font renderer
- * that constructs the glyphs with primitive path commands.
- * @var {boolean}
- */
-PDFJS.disableFontFace = (PDFJS.disableFontFace === undefined ?
-                         false : PDFJS.disableFontFace);
-
-/**
- * Path for image resources, mainly for annotation icons. Include trailing
- * slash.
[…]

### 2014-05-13 resources/pdfjs/src/display/canvas.js

@@ -1,2191 +1,0 @@
-/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
-/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
-/* Copyright 2012 Mozilla Foundation
- *
- * Licensed under the Apache License, Version 2.0 (the "License");
- * you may not use this file except in compliance with the License.
- * You may obtain a copy of the License at
- *
- *     http://www.apache.org/licenses/LICENSE-2.0
- *
- * Unless required by applicable law or agreed to in writing, software
- * distributed under the License is distributed on an "AS IS" BASIS,
- * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
- * See the License for the specific language governing permissions and
- * limitations under the License.
- */
-/* globals ColorSpace, DeviceCmykCS, DeviceGrayCS, DeviceRgbCS, error, PDFJS,
-           FONT_IDENTITY_MATRIX, Uint32ArrayView, IDENTITY_MATRIX, ImageData,
-           ImageKind, isArray, isNum, TilingPattern, OPS, Promise, Util, warn,
-           assert, info, shadow, TextRenderingMode, getShadingPatternFromIR,
-           WebGLUtils */
-
-'use strict';
-
-// <canvas> contexts store most of the state we need natively.
-// However, PDF needs a bit more state, which we store here.
-
-// Minimal font size that would be used during canvas fillText operations.
-var MIN_FONT_SIZE = 16;
-var MAX_GROUP_SIZE = 4096;
-
-var COMPILE_TYPE3_GLYPHS = true;
-
-function createScratchCanvas(width, height) {
-  var canvas = document.createElement('canvas');
-  canvas.width = width;
-  canvas.height = height;
-  return canvas;
-}
-
-function addContextCurrentTransform(ctx) {
-  // If the context doesn't expose a `mozCurrentTransform`, add a JS based on.
-  if (!ctx.mozCurrentTransform) {
-    // Store the original context
-    ctx._scaleX = ctx._scaleX || 1.0;
-    ctx._scaleY = ctx._scaleY || 1.0;
-    ctx._originalSave = ctx.save;
-    ctx._originalRestore = ctx.restore;
-    ctx._originalRotate = ctx.rotate;
[…]

### 2014-05-13 resources/pdfjs/src/shared/annotation.js

@@ -1,825 +1,0 @@
-/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
-/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
-/* Copyright 2012 Mozilla Foundation
- *
- * Licensed under the Apache License, Version 2.0 (the "License");
- * you may not use this file except in compliance with the License.
- * You may obtain a copy of the License at
- *
- *     http://www.apache.org/licenses/LICENSE-2.0
- *
- * Unless required by applicable law or agreed to in writing, software
- * distributed under the License is distributed on an "AS IS" BASIS,
- * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
- * See the License for the specific language governing permissions and
- * limitations under the License.
- */
-/* globals Util, isDict, isName, stringToPDFString, warn, Dict, Stream,
-           stringToBytes, PDFJS, isWorker, assert, NotImplementedException,
-           Promise, isArray, ObjectLoader, isValidUrl, OperatorList, OPS,
-           createPromiseCapability */
-
-'use strict';
-
-var DEFAULT_ICON_SIZE = 22; // px
-var HIGHLIGHT_OFFSET = 4; // px
-var SUPPORTED_TYPES = ['Link', 'Text', 'Widget'];
-
-var Annotation = (function AnnotationClosure() {
-  // 12.5.5: Algorithm: Appearance streams
-  function getTransformMatrix(rect, bbox, matrix) {
-    var bounds = Util.getAxialAlignedBoundingBox(bbox, matrix);
-    var minX = bounds[0];
-    var minY = bounds[1];
-    var maxX = bounds[2];
-    var maxY = bounds[3];
-
-    if (minX === maxX || minY === maxY) {
-      // From real-life file, bbox was [0, 0, 0, 0]. In this case,
-      // just apply the transform for rect
-      return [1, 0, 0, 1, rect[0], rect[1]];
-    }
-
-    var xRatio = (rect[2] - rect[0]) / (maxX - minX);
-    var yRatio = (rect[3] - rect[1]) / (maxY - minY);
-    return [
-      xRatio,
-      0,
-      0,
-      yRatio,
-      rect[0] - minX * xRatio,
-      rect[1] - minY * yRatio
-    ];
-  }
-
-  function getDefaultAppearance(dict) {
-    var appearanceState = dict.get('AP');
[…]

### 2014-05-13 resources/pdfjs/src/shared/util.js

@@ -1,1509 +1,0 @@
-/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
-/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
-/* Copyright 2012 Mozilla Foundation
- *
- * Licensed under the Apache License, Version 2.0 (the "License");
- * you may not use this file except in compliance with the License.
- * You may obtain a copy of the License at
- *
- *     http://www.apache.org/licenses/LICENSE-2.0
- *
- * Unless required by applicable law or agreed to in writing, software
- * distributed under the License is distributed on an "AS IS" BASIS,
- * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
- * See the License for the specific language governing permissions and
- * limitations under the License.
- */
-/* globals Cmd, ColorSpace, Dict, MozBlobBuilder, Name, PDFJS, Ref, URL,
-           Promise */
-
-'use strict';
-
-var globalScope = (typeof window === 'undefined') ? this : window;
-
-var isWorker = (typeof window == 'undefined');
-
-var FONT_IDENTITY_MATRIX = [0.001, 0, 0, 0.001, 0, 0];
-
-var TextRenderingMode = {
-  FILL: 0,
-  STROKE: 1,
-  FILL_STROKE: 2,
-  INVISIBLE: 3,
-  FILL_ADD_TO_PATH: 4,
-  STROKE_ADD_TO_PATH: 5,
-  FILL_STROKE_ADD_TO_PATH: 6,
-  ADD_TO_PATH: 7,
-  FILL_STROKE_MASK: 3,
-  ADD_TO_PATH_FLAG: 4
-};
-
-var ImageKind = {
-  GRAYSCALE_1BPP: 1,
-  RGB_24BPP: 2,
-  RGBA_32BPP: 3
-};
-
-// The global PDFJS object exposes the API
-// In production, it will be declared outside a global wrapper
-// In development, it will be declared here
-if (!globalScope.PDFJS) {
-  globalScope.PDFJS = {};
-}
-
-globalScope.PDFJS.pdfBug = false;
-
-PDFJS.VERBOSITY_LEVELS = {
-  errors: 0,
-  warnings: 1,
-  infos: 5
-};
-
-// All the possible operations for an operator list.
-var OPS = PDFJS.OPS = {
[…]

### 2014-05-13 resources/pdfjs/test/unit/evaluator_spec.js

@@ -1,181 +1,0 @@
-/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
-/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
-/* globals expect, it, describe, PartialEvaluator, StringStream, OPS */
-
-'use strict';
-
-describe('evaluator', function() {
-  function XrefMock(queue) {
-    this.queue = queue;
-  }
-  XrefMock.prototype = {
-    fetchIfRef: function() {
-      return this.queue.shift();
-    }
-  };
-  function HandlerMock() {
-    this.inputs = [];
-  }
-  HandlerMock.prototype = {
-    send: function(name, data) {
-      this.inputs({name: name, data: data});
-    }
-  };
-  function ResourcesMock() { }
-  ResourcesMock.prototype = {
-    get: function(name) {
-      return this[name];
-    }
-  };
-
-  function PdfManagerMock() { }
-
-  describe('splitCombinedOperations', function() {
-    it('should reject unknown operations', function() {
-      var evaluator = new PartialEvaluator(new PdfManagerMock(),
-                                           new XrefMock(), new HandlerMock(),
-                                           'prefix');
-      var stream = new StringStream('fTT');
-      var result = evaluator.getOperatorList(stream, new ResourcesMock());
-      expect(!!result.fnArray && !!result.argsArray).toEqual(true);
-      expect(result.fnArray.length).toEqual(1);
-      expect(result.fnArray[0]).toEqual(OPS.fill);
-      expect(result.argsArray[0].length).toEqual(0);
-    });
-
-    it('should handle one operations', function() {
-      var evaluator = new PartialEvaluator(new PdfManagerMock(),
-                                           new XrefMock(), new HandlerMock(),
-                                           'prefix');
-      var stream = new StringStream('Q');
-      var result = evaluator.getOperatorList(stream, new ResourcesMock());
-      expect(!!result.fnArray && !!result.argsArray).toEqual(true);
-      expect(result.fnArray.length).toEqual(1);
-      expect(result.fnArray[0]).toEqual(OPS.restore);
-    });
-
-    it('should handle two glued operations', function() {
-      var evaluator = new PartialEvaluator(new PdfManagerMock(),
-                                           new XrefMock(), new HandlerMock(),
-                                           'prefix');
-      var resources = new ResourcesMock();
-      resources.Res1 = {};
[…]

### 2014-05-13 resources/pdfjs/web/viewer.js

@@ -1,2429 +1,0 @@
-/* -*- Mode: Java; tab-width: 2; indent-tabs-mode: nil; c-basic-offset: 2 -*- */
-/* vim: set shiftwidth=2 tabstop=2 autoindent cindent expandtab: */
-/* Copyright 2012 Mozilla Foundation
- *
- * Licensed under the Apache License, Version 2.0 (the "License");
- * you may not use this file except in compliance with the License.
- * You may obtain a copy of the License at
- *
- *     http://www.apache.org/licenses/LICENSE-2.0
- *
- * Unless required by applicable law or agreed to in writing, software
- * distributed under the License is distributed on an "AS IS" BASIS,
- * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
- * See the License for the specific language governing permissions and
- * limitations under the License.
- */
-/* globals PDFJS, PDFBug, FirefoxCom, Stats, Cache, PDFFindBar, CustomStyle,
-           PDFFindController, ProgressBar, TextLayerBuilder, DownloadManager,
-           getFileName, scrollIntoView, getPDFFileNameFromURL, PDFHistory,
-           Preferences, SidebarView, ViewHistory, PageView, ThumbnailView, URL,
-           noContextMenuHandler, SecondaryToolbar, PasswordPrompt,
-           PresentationMode, HandTool, Promise, DocumentProperties,
-           DocumentOutlineView, DocumentAttachmentsView */
-
-'use strict';
-
-var DEFAULT_URL = 'compressed.tracemonkey-pldi-09.pdf';
-var DEFAULT_SCALE = 'auto';
-var DEFAULT_SCALE_DELTA = 1.1;
-var UNKNOWN_SCALE = 0;
-var CACHE_SIZE = 20;
-var CSS_UNITS = 96.0 / 72.0;
-var SCROLLBAR_PADDING = 40;
-var VERTICAL_PADDING = 5;
-var MAX_AUTO_SCALE = 1.25;
-var MIN_SCALE = 0.25;
-var MAX_SCALE = 4.0;
-var VIEW_HISTORY_MEMORY = 20;
-var SCALE_SELECT_CONTAINER_PADDING = 8;
-var SCALE_SELECT_PADDING = 22;
[…]

### 2014-06-20 doc/paper.tex
updating my affiliation
Remove sequence diagram in documentation

--- 2014-05-13 doc/paper.tex
@@
-% Created 2014-04-14 Mon 18:10
-\documentclass[runningheads,a4paper]{llncs}
+\documentclass{llncs}
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-\usepackage[protrusion=true,expansion=true]{microtype}
-\usepackage{fixltx2e}
+\usepackage{makeidx}  % allows for indexgeneration
 \usepackage{graphicx}
@@
 \usepackage{wrapfig}
-\usepackage{amsmath}
 \usepackage{textcomp}
-\usepackage{marvosym}
-\usepackage{wasysym}
-\usepackage{amssymb}
 \usepackage{hyperref}
@@
 \tolerance=1000
-\usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{listings}
 
@@
 \urldef{\mailsb}\path|iain.marshall@kcl.ac.uk|
-\urldef{\mailsc}\path|byron_wallace@brown.edu|
+\urldef{\mailsc}\path|byron.wallace@utexas.edu|
 
 \acrodef{ebm}[EBM]{Evidence-based Medicine}
-% I don't think thi sneeds to be capitalized -- bcw
 \acrodef{ml}[ML]{machine learning}
@@
   \and King's College London, London SE1 3QD, UK \\ \mailsb
-  \and Brown University, Providence, RI 02906, USA \\ \mailsc}
+  \and University of Texas at Austin, Austin, TX 78712, USA \\ \mailsc}
 
@@
 \setcounter{tocdepth}{3}
-\newcommand{\highlight}[1]{\colorbox{yellow}{#1}}
 
-\input{revision}
+%\input{revision}
 \author{Kuiper, J\inst{1}. \and Marshall, I.J.\inst{2} \and Wallace, B.C.\inst{3} \and Swertz, M.A.\inst{1}}
-\date{\texttt{revision: \revision, date: \revisiondate}}
+%\date{\texttt{revision: \revision, date: \revisiondate}}
 \title{Spá: a web-based viewer for text mining in Evidence Based Medicine}
-
-%%% BCW --
 
@@
 \begin{abstract}
-% Unstructured \ac{pdf} documents remain the main vehicle for dissemination of scientific findings.
-% Those interested in gathering and assimilating data must therefore manually peruse published articles and extract from these the elements of interest.
-% \acl{ebm} provides a compelling illustration of this: many person-hours are spent each year extracting summary information from articles that describe clinical trials.
-% This represents an enormous burden, especially in light of the expotentially increasing volume of published biomedical articles.
-% Machine learning provides a potential means of mitigating this burden by automating extraction.
-% But for automated approaches to be useful to end-users, we need tools that allow domain experts to interact with, and benefit from, model predictions.
-% To this end, we present a web-based tool called Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}} that accepts as input an article and provides as output an automatically visually annotated rendering of this article.
-% More generally, Spá provides a framework for visualizing predicted full-text \ac{pdf} annotations, both at the document and sentence level.
-
 Summarizing the evidence about medical interventions is an immense undertaking, in part because unstructured \ac{pdf} documents remain the main vehicle for disseminating scientific findings.
@@
 To illustrate its functionality, we use Spá to semi-automate the assessment of bias in clinical trials.
-%Spá can visualize the output from hybrid models that simultaneously classify documents (e.g., identifying trials as low or high risk of various biases), and annotate sentences that support these classifications.
 Spá has a modular architecture, therefore the tool may be widely useful in other domains with a \ac{pdf}-based literature, including law, physics, and biology.
@@
 (2) a general open-source system for visualizing the predictions of trained models from full-text articles on the web.
-%These contributions are described further in sections \ref{section:EBM-ML} and \ref{section:architecture}.
 
@@
 \label{section:EBM-ML}
-
-% \subsection{Systematic Reviews}
-% %%% sort of redundant with above; may want to re-factor
-% The process of pooling and summarizing clinical trials is called \emph{systematic reviewing}, and forms the corner-stone of current \ac{ebm}.
-% Systematic reviewing consists of specifying a precise clinical question and accompanying study inclusion criteria, and then exhaustively searching the literature to identify eligible studies.
-% Identified eligible studies are subsequently analyzed (i.e., synthesized), resulting in a summary of all of the published evidence that pertains to the clinical question of interest.
-% Systematic reviews thus represent a rigorous, data-driven approach to answering clinical questions.
-% But conducting systematic reviews is complicated by the massive number of trials that are conducted: for example, the Cochrane Library alone indexes 286,418 trials that were conducted in the last decade \cite{valkenhoef2012}.
-% % While methods and publishing standards are improving, many legacy publications will remain available only as \ac{pdf} documents.
-
-% Extracting information of interest from these \acp{pdf} is imperative but laborious.
-% To mitigate this burden, we have constructed machine learning models that automatically extract some characteristics of interest.
-% Specifically, our model predicts {\it risk of biases} across different domains as a function of the texts comprising articles.
-% It simultaneously extracts sentences supporting these predictions.
-% We briefly outline our approach to achieving this below.
-% We also note that we have a a separate model that extracts the study sample size from articles.
-% Spá -- our visualization tool -- provides a framework to upload \acp{pdf} and then render these predicted annotations.
-% We foresee adding additional predictors to this tool that, for example, may identify different treatment mentions within the text (e.g., drugs).
-
-% % made a web-based tool that allows the visualization of annotations within a \ac{pdf} documents, and meta-information alongside it.
 
@@
 
-%%%
-% note that this is a little misleading right now -- we don't technically have this multi-task joint extraction thing going yet!!!
-%%%
 From a \ac{ml} vantage, we have two tasks for a given article: (1) predict the overall risk of bias for each of the domains, and (2) extract the sentences that support these assessments.
@@
 We accomplish this by way of a feature space construction that includes both shared and domain-specific terms, similar to the domain adaptation approach in \cite{Daume2007}.
-%Furthermore, we take a unified approach to the two tasks by \emph{jointly} assessing the risk of bias associated with a given article \emph{and} extracting the sentences that support this judgment.
 Specifically, we first make sentence level prediction, and then insert features representing the tokens in the predicted sentences for exploitation by the document level classifier.
 Figure \ref{fig:screenshot} shows the system in use.
-%More specifically, the database we leverage contains structured and semi-structured data for each systematic review.
-Internally, the Cochrane Collaboration stores working versions of their reviews as XML.
-Each review contains a wealth of (structured) data about the clinical trials that met the review inclusion criteria.
-There are usually multiple clinical trials described in a single review.
-Cochrane reviews use basic clinical trial identifiers which are unique per review (based on the first author surname and year of publication) throughout these files.
-It is therefore possible to extract structured data, and filtered snippets of full text data which describe a single clinical trial.
-Using these identifiers, we were able to obtain full structured citation data for the primary reference of all included studies across the \ac{cdsr}.
-
-% \begin{itemize}
-% \item Basically show that we're using state of the art
-% \item Briefly talk about cochrane DB / distant supervision
-% \item KDD stuff (briefly)
-% \item Multi-task stuff!
-% \end{itemize}
 
@@
 
-\label{section:architecture}
-\begin{wrapfigure}{}{0.5\textwidth}
-  \vspace{-2em}
-  \includegraphics[width=0.48\textwidth]{./diagrams/sequence.pdf}
-  \vspace{-1em}
-  \caption{\label{fig:sequence}Sequence diagram of a typical request-response in Spá.}
-  \vspace{-1.5em}
-\end{wrapfigure}
+%label{section:architecture}
+%begin{wrapfigure}{}{0.5\textwidth}
+% \vspace{-2em}
+% \includegraphics[width=0.6\textwidth]{./diagrams/sequence.pdf}
+% \vspace{-1em}
+% \caption{\label{fig:sequence}Sequence diagram of a typical request-response in Spá.}
+% \vspace{-1.0em}
+%end{wrapfigure}
 
 Spá relies on Mozilla pdf.js\footnote{\url{http://mozilla.github.io/pdf.js}} for visualization of the document and text extraction.
-The results of the text extraction are processed server-side by a variety of processing topologies, as outlined in figure \ref{fig:sequence}.
+The results of the text extraction are processed server-side by a variety of processing topologies.
 Results are communicated back to the browser and displayed using React components.\footnote{\url{http://facebook.github.io/react}}
@@
 Part of this research was funded by the European Union Seventh Framework Programme (FP7/2007-2013) under grant agreement n° 261433.
-% %TODO add seed funds ack (BCW) -- I can do this post-acceptance though
 
